### 2021-10-20 thesis.tex
Initial thesis

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{todonotes}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Thesis paper in Seminar Business Processes and the Internet of Things on Conformance Checking Using Activity and Trace Embeddings.}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jan Kruska}
%
%\authorrunning{Pegoraro et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
%\institute{Chair of Process and Data Science\\Department of Computer Science, RWTH Aachen, Aachen, Germany
%	\email{\{pegoraro,wvdaalst\}@pads.rwth-aachen.de}\\
%	\url{http://www.pads.rwth-aachen.de/}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\todo{Abstract}
%\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Planned structure}
The following list shall give a short overview of both the intended general structure of the seminar paper. In each section the main questions that should be answered by it are listed.
\begin{enumerate}
	\item Abstract
	\item Introduction
	\item Background
	\begin{enumerate}
		\item What is conformance checking, how is it useful and why would you do it, which methods are there, what are advantages and disadvantages of said methods.
		\item What is NLP (briefly), what are embeddings generally and word embeddings specifically, what are word2vec and doc2vec and how do they approach the NLP problems.
		\item What parallels are there between NLP and conformance checking
		\item If there are these parallels, how could such NLP mechanism be adapted (theoretically not practically) for conformance checking, what could the advantages be of such an approach, what could be disadvantages and/or problems that will need addressing.
	\end{enumerate}
	\item Method
	\begin{enumerate}
		\item How were word2vec and doc2vec adapted to conformance checking in the paper (I.e. practical adaption)
	\end{enumerate}
	\item Results
	\begin{enumerate}
		\item What are the results given in the paper
		\item What metrics were used to evaluate the performance of the approach presented in the paper, are they appropriate, are there other possible metrics, if so why was this one choses, what advantages or disadvantages do different metrics have.
		\item What are the results when using their code and reproducing the results (ideally the same)
	\end{enumerate}
	\item Outlook
	\begin{enumerate}
		\item What future work do the authors suggest
		\item What problems were encountered when trying to reproduce the results from the paper. Could they be reproduced completely, just in part or not at all. If so are there suggestions on how could these problems be mitigated.
	\end{enumerate}
\end{enumerate}
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{bibliography}
%
\end{document}

### 2021-10-21 template/samplepaper.tex
Moved template to subdir

--- 2021-10-20 thesis.tex
@@
 \usepackage{graphicx}
-\usepackage{todonotes}
 % Used for displaying a sample figure. If possible, figure files should
@@
 %
-\title{Thesis paper in Seminar Business Processes and the Internet of Things on Conformance Checking Using Activity and Trace Embeddings.}
+\title{Contribution Title\thanks{Supported by organization x.}}
 %
@@
 %
-\author{Jan Kruska}
+\author{Marco Pegoraro\orcidID{0000-0002-8997-7517} \and
+	Wil M.P. van der Aalst\orcidID{0000-0002-0955-6940}}
 %
-%\authorrunning{Pegoraro et al.}
+\authorrunning{Pegoraro et al.}
 % First names are abbreviated in the running head.
@@
 %
-%\institute{Chair of Process and Data Science\\Department of Computer Science, RWTH Aachen, Aachen, Germany
-%	\email{\{pegoraro,wvdaalst\}@pads.rwth-aachen.de}\\
-%	\url{http://www.pads.rwth-aachen.de/}}
+\institute{Chair of Process and Data Science\\Department of Computer Science, RWTH Aachen, Aachen, Germany
+	\email{\{pegoraro,wvdaalst\}@pads.rwth-aachen.de}\\
+	\url{http://www.pads.rwth-aachen.de/}}
 %
@@
 \begin{abstract}
-\todo{Abstract}
-%\keywords{First keyword  \and Second keyword \and Another keyword.}
+The abstract should briefly summarize the contents of the paper in
+150--250 words.
+
+\keywords{First keyword  \and Second keyword \and Another keyword.}
 \end{abstract}
@@
 %
-\section{Planned structure}
-The following list shall give a short overview of both the intended general structure of the seminar paper. In each section the main questions that should be answered by it are listed.
-\begin{enumerate}
-	\item Abstract
-	\item Introduction
-	\item Background
-	\begin{enumerate}
-		\item What is conformance checking, how is it useful and why would you do it, which methods are there, what are advantages and disadvantages of said methods.
-		\item What is NLP (briefly), what are embeddings generally and word embeddings specifically, what are word2vec and doc2vec and how do they approach the NLP problems.
-		\item What parallels are there between NLP and conformance checking
-		\item If there are these parallels, how could such NLP mechanism be adapted (theoretically not practically) for conformance checking, what could the advantages be of such an approach, what could be disadvantages and/or problems that will need addressing.
-	\end{enumerate}
-	\item Method
-	\begin{enumerate}
-		\item How were word2vec and doc2vec adapted to conformance checking in the paper (I.e. practical adaption)
-	\end{enumerate}
-	\item Results
-	\begin{enumerate}
-		\item What are the results given in the paper
-		\item What metrics were used to evaluate the performance of the approach presented in the paper, are they appropriate, are there other possible metrics, if so why was this one choses, what advantages or disadvantages do different metrics have.
-		\item What are the results when using their code and reproducing the results (ideally the same)
-	\end{enumerate}
-	\item Outlook
-	\begin{enumerate}
-		\item What future work do the authors suggest
-		\item What problems were encountered when trying to reproduce the results from the paper.
-Could they be reproduced completely, just in part or not at all.
-If so are there suggestions on how could these problems be mitigated.
-	\end{enumerate}
-\end{enumerate}
 \section{First Section}

### 2021-10-21 thesis.tex
Moved template to subdir

@@
 %
-\documentclass[runningheads]{llncs}
+\documentclass[runningheads]{template/llncs}
 %
@@
 \end{enumerate}
+
 \section{First Section}
-\subsection{A Subsection Sample}
-Please note that the first paragraph of a section or subsection is
-not indented. The first paragraph that follows a table, figure,
-equation etc. does not need an indent, either.
 
-Subsequent paragraphs, however, are indented.
-
-\subsubsection{Sample Heading (Third Level)} Only two levels of
-headings should be numbered. Lower level headings remain unnumbered;
-they are formatted as run-in headings.
-
-\paragraph{Sample Heading (Fourth Level)}
-The contribution should contain no more than four levels of
-headings. Table~\ref{tab1} gives a summary of all heading levels.
-
-\begin{table}
-\caption{Table captions should be placed above the
-tables.}\label{tab1}
-\begin{tabular}{|l|l|l|}
-\hline
-Heading level &  Example & Font size and style\\
-\hline
-Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-\hline
-\end{tabular}
-\end{table}
-
-\noindent Displayed equations are centered and set on a separate
-line.
-\begin{equation}
-x + y = z
-\end{equation}
-Please try to avoid rasterized images for line-art diagrams and
-schemas. Whenever possible, use vector graphics instead (see
-Fig.~\ref{fig1}).
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig1.eps}
-\caption{A figure caption is always placed below the illustration.
-Please note that short captions are centered, while long ones are
-justified by the macro package automatically.} \label{fig1}
-\end{figure}
-
-\begin{theorem}
-This is a sample theorem. The run-in heading is set in bold, while
-the following text appears in italics. Definitions, lemmas,
-propositions, and corollaries are styled the same way.
-\end{theorem}
-%
-% the environments 'definition', 'lemma', 'proposition', 'corollary',
-% 'remark', and 'example' are defined in the LLNCS documentclass as well.
-%
-\begin{proof}
-Proofs, examples, and remarks have the initial word in italics,
-while the following text appears in normal font.
-\end{proof}
-For citations of references, we prefer the use of square brackets
-and consecutive numbers. Citations using labels or the author/year
-convention are also acceptable. The following bibliography provides
-a sample reference list with entries for journal
-articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-and a homepage~\cite{ref_url1}. Multiple citations are grouped
-\cite{ref_article1,ref_lncs1,ref_book1},
-\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
 %
@@
 %
-\bibliographystyle{splncs04}
-\bibliography{bibliography}
+\bibliographystyle{template/splncs04}
+\bibliography{literature/bibliography}
 %

### 2021-10-22 thesis.tex
added some aims

@@
 	\item Introduction
+	\begin{enumerate}
+		What is the motivation of the paper
+	\end{enumerate}
 	\item Background
@@
 
-\section{First Section}
-
+\section{Aims}
+The main focus of the seminar paper will be a look at \cite{PBWe20}. The seminar paper should give an overview of the backgrounds that are omitted for brevity in the paper.
+Aside from that 
+Since the authors provide accompanying source code to their paper it is also possible to try and reproduce their results.
+As of now it is unclear if that will be possible within a reasonable time frame, as an actual implementation is outside of the scope of this seminar.
+Furthermore the aim of the seminar is to create a connection between business process intelligence and the Internet of Things.
+From this perspective there are two main interests to be derived: Firstly is it possible to apply their proposed method on limited hardware, as this is generally the case in the Internet of Things.
+%especially regarding processing speeds
+Secondly and probably more importantly the method in the paper is described in terms of an offline analysis, where process models and a full event log are available.
+In the Internet of Things however continuos processes are prevalent, and in general we would like to be able to detect deviations (i.e.
+non-conformance) already while the process is still running.
 %

### 2021-10-22 thesis.tex
Extended aims

@@
+% !TeX spellcheck = en_GB
 % This is samplepaper.tex, a sample chapter demonstrating the
@@
 %
-\title{Thesis paper in Seminar Business Processes and the Internet of Things on Conformance Checking Using Activity and Trace Embeddings.}
+\title{Thesis paper}
+\subtitle{Seminar Business Processes and the Internet of Things \\ Conformance Checking Using Activity and Trace Embeddings.}
 %
@@
 %
-\author{Jan Kruska}
+\author{Jan Kruska \and Supervisor: István Koren}
 %
@@
 		\item If there are these parallels, how could such NLP mechanism be adapted (theoretically not practically) for conformance checking, what could the advantages be of such an approach, what could be disadvantages and/or problems that will need addressing.
+		\item Whats the Internet of Things and why would one wish to perform process analysis there
 	\end{enumerate}
@@
 The main focus of the seminar paper will be a look at \cite{PBWe20}. The seminar paper should give an overview of the backgrounds that are omitted for brevity in the paper.
-Aside from that 
+After that a look into the proposed method will follow, including explanations on why the authors chose the design that they did.
+Then an overview of the authors' results should follow, especially focussing on their methods of validation and categorization, since measuring the quality of the proposed approach is much more difficult, when compared to more straightforward algorithms like Token-based Replay or Alignments.
 Since the authors provide accompanying source code to their paper it is also possible to try and reproduce their results.
 As of now it is unclear if that will be possible within a reasonable time frame, as an actual implementation is outside of the scope of this seminar.
+Currently the hope is that the code is compatible and simple enough that the results can be reproduced decently well.
+In the case that this works an overview of how this was done should be provided, as well as highlighting possible differences that were not reproducable.
+If this is not the case then this will be replaced by a brief explanation on what problems were encountered during the attempt.
 Furthermore the aim of the seminar is to create a connection between business process intelligence and the Internet of Things.
@@
 Secondly and probably more importantly the method in the paper is described in terms of an offline analysis, where process models and a full event log are available.
-In the Internet of Things however continuos processes are prevalent, and in general we would like to be able to detect deviations (i.e.
+In the Internet of Things however continuous processes are prevalent, and in general we would like to be able to detect deviations (i.e.
 non-conformance) already while the process is still running.
+Again an actual implementation or experimentation of these two aspects, i.e.
+approaching them from a practical perspective, is outside of the scope of this seminar paper, however it is intended to explore these possibilities from a theoretical perspective and maybe get some insights into how these could be approached from the practical perspective and what consideration would need to be made in that case.
 %

### 2021-10-23 thesis.tex
Added scope

@@
 %
-\author{Jan Kruska \and Supervisor: István Koren}
+\author{Jan Kruska \\ Supervisor: Dr. István Koren}
 %
-%\authorrunning{Pegoraro et al.}
+\authorrunning{Jan Kruska}
 % First names are abbreviated in the running head.
@@
 %
-%\institute{Chair of Process and Data Science\\Department of Computer Science, RWTH Aachen, Aachen, Germany
-%	\email{\{pegoraro,wvdaalst\}@pads.rwth-aachen.de}\\
+\institute{Chair of Process and Data Science\\Department of Computer Science, RWTH Aachen, Aachen, Germany}
+%	\email{jan.kruska@rwth-aachen.de}\\
 %	\url{http://www.pads.rwth-aachen.de/}}
@@
 	\begin{enumerate}
-		What is the motivation of the paper
+		\item What is the motivation of the paper
 	\end{enumerate}
@@
 		\item If there are these parallels, how could such NLP mechanism be adapted (theoretically not practically) for conformance checking, what could the advantages be of such an approach, what could be disadvantages and/or problems that will need addressing.
-		\item Whats the Internet of Things and why would one wish to perform process analysis there
+		\item What is the Internet of Things and why would one wish to perform process analysis there
 	\end{enumerate}
@@
 		\item What are the results given in the paper
-		\item What metrics were used to evaluate the performance of the approach presented in the paper, are they appropriate, are there other possible metrics, if so why was this one choses, what advantages or disadvantages do different metrics have.
+		\item What metrics were used to evaluate the performance of the approach presented in the paper, are they appropriate, are there other possible metrics, if so why was this one chosen, what advantages or disadvantages do different metrics have.
 		\item What are the results when using their code and reproducing the results (ideally the same)
@@
 		\item What problems were encountered when trying to reproduce the results from the paper.
-Could they be reproduced completely, just in part or not at all.
-If so are there suggestions on how could these problems be mitigated.
+Could they be reproduced completely, just in part or not at all?
+If so, are there suggestions on how could these problems be mitigated.
 	\end{enumerate}
@@
 Then an overview of the authors' results should follow, especially focussing on their methods of validation and categorization, since measuring the quality of the proposed approach is much more difficult, when compared to more straightforward algorithms like Token-based Replay or Alignments.
-Since the authors provide accompanying source code to their paper it is also possible to try and reproduce their results.
-As of now it is unclear if that will be possible within a reasonable time frame, as an actual implementation is outside of the scope of this seminar.
-Currently the hope is that the code is compatible and simple enough that the results can be reproduced decently well.
-In the case that this works an overview of how this was done should be provided, as well as highlighting possible differences that were not reproducable.
+Since the authors provide accompanying source code to their paper, it is also possible to try to reproduce their results.
+As of now it is unclear if that will be possible within a reasonable time frame, as an actual implementation is outside the scope of this seminar.
+Currently, the hope is that the code is compatible and simple enough that the results can be reproduced decently well.
+In the case that this works an overview of how this was done should be provided, as well as highlighting possible differences that were not reproducible.
 If this is not the case then this will be replaced by a brief explanation on what problems were encountered during the attempt.
-Furthermore the aim of the seminar is to create a connection between business process intelligence and the Internet of Things.
+Furthermore, the aim of the seminar is to create a connection between business process intelligence and the Internet of Things.
 From this perspective there are two main interests to be derived: Firstly is it possible to apply their proposed method on limited hardware, as this is generally the case in the Internet of Things.
@@
 Again an actual implementation or experimentation of these two aspects, i.e.
-approaching them from a practical perspective, is outside of the scope of this seminar paper, however it is intended to explore these possibilities from a theoretical perspective and maybe get some insights into how these could be approached from the practical perspective and what consideration would need to be made in that case.
+approaching them from a practical perspective, is outside the scope of this seminar paper, however it is intended to explore these possibilities from a theoretical perspective and maybe get some insights into how these could be approached from the practical perspective and what consideration would need to be made in that case.
+\section{Scope}
+It was already mentioned above, but it should be noted again that the scope of this paper is limited, and a clear consideration of what is possible within that scope is integral.
+As such it is very much desired to include certain practical considerations, but the available amount of effort for these will be very limited.
+It is currently also very difficult to estimate the amount effort needed to, for example, reproduce the results from the paper.
+This means, that such content should not be considered part of the expected result.
 %

### 2021-10-25 thesis.tex
Some fixes

@@
 \section{Planned structure}
-The following list shall give a short overview of both the intended general structure of the seminar paper. In each section the main questions that should be answered by it are listed.
+The following list shall give a short overview of the intended general structure of the seminar paper. For each section the main questions that should be answered by it are listed.
 \begin{enumerate}
@@
 \section{Aims}
-The main focus of the seminar paper will be a look at \cite{PBWe20}. The seminar paper should give an overview of the backgrounds that are omitted for brevity in the paper.
+The main focus of the seminar paper will be an in depth look at \cite{PBWe20}. The seminar paper should give an overview of the backgrounds that are omitted for brevity in the paper.
 After that a look into the proposed method will follow, including explanations on why the authors chose the design that they did.
@@
 This means, that such content should not be considered part of the expected result.
+
 %

### 2021-10-25 paper.tex
Initial paper

% !TeX spellcheck = en_GB
% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{template/llncs}
%
\usepackage{graphicx}
\usepackage{todonotes}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Seminar Paper}
\subtitle{Seminar Business Processes and the Internet of Things \\ Conformance Checking Using Activity and Trace Embeddings.}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jan Kruska \\ Supervisor: Dr. István Koren}
%
\authorrunning{Jan Kruska}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Chair of Process and Data Science\\Department of Computer Science, RWTH Aachen, Aachen, Germany}
%	\email{jan.kruska@rwth-aachen.de}\\
%	\url{http://www.pads.rwth-aachen.de/}}
%
\maketitle              % typeset the header of the contribution
%
%
%
%
%\section{Planned structure}
%The following list shall give a short overview of the intended general structure of the seminar paper. For each section the main questions that should be answered by it are listed.
%\begin{enumerate}
%	\item Abstract
%	\item Introduction
%	\begin{enumerate}
%		\item What is the motivation of the paper
%	\end{enumerate}
%	\item Background
%	\begin{enumerate}
%		\item What is conformance checking, how is it useful and why would you do it, which methods are there, what are advantages and disadvantages of said methods.
%		\item What is NLP (briefly), what are embeddings generally and word embeddings specifically, what are word2vec and doc2vec and how do they approach the NLP problems.
%		\item What parallels are there between NLP and conformance checking
%		\item If there are these parallels, how could such NLP mechanism be adapted (theoretically not practically) for conformance checking, what could the advantages be of such an approach, what could be disadvantages and/or problems that will need addressing.
%		\item What is the Internet of Things and why would one wish to perform process analysis there
%	\end{enumerate}
%	\item Method
%	\begin{enumerate}
%		\item How were word2vec and doc2vec adapted to conformance checking in the paper (I.e. practical adaption)
%	\end{enumerate}
%	\item Results
%	\begin{enumerate}
%		\item What are the results given in the paper
%		\item What metrics were used to evaluate the performance of the approach presented in the paper, are they appropriate, are there other possible metrics, if so why was this one chosen, what advantages or disadvantages do different metrics have.
%		\item What are the results when using their code and reproducing the results (ideally the same)
%	\end{enumerate}
%	\item Outlook
%	\begin{enumerate}
%		\item What future work do the authors suggest
%		\item What problems were encountered when trying to reproduce the results from the paper. Could they be reproduced completely, just in part or not at all? If so, are there suggestions on how could these problems be mitigated.
%	\end{enumerate}
%\end{enumerate}

\begin{abstract}
	In the last decade there has been growing interest, both scientific and non-scientific, in the field of process mining.
	While the main focus has been on business processes, the methods developed in the field of process mining are in now way limited to that area.
	One other area which lends itself to process mining is the growing Internet of Things.
	While there are many conceivable applications,  there has only been limited research interest in this synergy.
	The aim of this seminar paper is to recapitulate the findings of the focus paper \cite{PBWe20}, while also emphasizing the benefits and difficulties of applying the described methodology in the Internet of Things.
\end{abstract}

\section{Introduction}

Due to growing compute capabilities, as well as further digitalization allowed for more process data to be gathered and analysed.
The increase in compute and storage capabilities, as well as the growing digitalization of many parts of our lives has created the distinct field of data science, as an amalgamation of Statistics, technical knowledge and domain knowledge.

One benefactor of this development has been the subfield of process science, which is concerned with the analysis of processes.
The combination of process science and data science gave rise to techniques generally grouped under the term process mining\footnote{Please note that due to the relative young age of the field, the fact that it lies at the intersection of two different fields and the fact that there is a marketing interest for these topics the terminology is not always settled and different authors and/or groups may differ in usage. The terminology used here is oriented around the definitions in \cite{Aals16}, as it seems to be the most polished overview of the field at the moment.}.
Process mining is concerned with the automatic and algorithmic processing of event data. In its easiest form an event is a piece of data, that consists of a timestamp, an identifier to group events belonging to the same execution and a body containing further arbitrary values.
In most cases there is also an identifier for the event type, with the purpose of identifying similar events in different executions of the process, e.g. to be able to group all "Send invoice" events as the same type.

Historically most research in the topic of process mining has been on business processes. 
There are a few reasons for that. 
Namely, that there was already a well established field of non-algorithmic process science for business processes, which could act as a stepping stone.
Secondly some of these processes were already highly digitized, many companies already had well established ERP systems from which data could be gathered with reasonable ease.
Thirdly there was, and is, a large financial interest in optimizing such processes.
And lastly business processes often struck the balance between too simple and too complicated, in that they exhibited enough variability to be interesting to analyse but were still simple enough as to enable the use of the early process mining algorithms.
So it should be stated that while process mining is of great use for classical business processes, these are not the only areas for which it could be useful.

One such area of interest is the Internet of Things.
In recent years a vast infrastructure of small networked devices typically with some sensors attached has developed. 
This is especially interesting in the case for automation in manufacturing for which the term Internet of Production has been coined.
Both these "Internet"'s\footnote{Note that there will not be a very clear distinction between these two terms in this paper. The object of interest here is a highly distributed network of interacting devices, that generate a large amount of event data about their surroundings. Which specific environment they are in is less important here.} 
constitute a highly digitized network in which avast amount of data, including event data, is being generated and measured.
Especially in the case of manufacturing there is a large monetary interest in optimizing production pipelines.
And lastly in the case of the Internet of Things there are complex hidden processes to be discovered, which can challenge newer and more advanced process mining algorithms in a way that other areas might not.
\section{Background}

\section{Method}

\section{Results}

\section{Discussion}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{template/splncs04}
\bibliography{literature/bibliography}
%
\end{document}

### 2021-11-12 paper.tex
Something on conformance checking

@@
 \section{Background}
+\subsection{Conformance Checking}
+Conformance checking covers a range of different methods that aim to quantify how well an event log (or even just a single trace) and a process model fit together.
+Our intuitive expectation would be that a model that allows for exactly those traces contained in the event log would conform perfectly, whereas a model that allows for none of the traces seen in the log would have very low conformance.
+The aim of conformance checking is the formalization of this imprecise intuitive understanding of fitting together and the development of methods and algorithms that can quantify precisely that.
+
+The uses of such an approach can generally be divided into two relatively distinct subcategories, depending on whether the event log or the process model are seen as normative.
+In the case where the process model is considered normative, conformance checking allows for the detection of deviations, i.e. observed traces that are not possible according to the model.
+From such information a number of useful analyses can follow, e.g. where do deviations happen, which resources are involved in deviations, how exactly do these traces deviate from the model.
+Both positive and negative conclusions are possible from such situations.
+E.g. such an analysis may reveal that people often skip a step in the process, which actually improves the overall performance of the process, in which case such a step could be made optional.
+An example of negative conclusions may be the detections of deviations that do not follow proper legal or procedural requirements of the process, such as requiring two different persons to review an important document before signing off on it.
+In such a case knowledge of these deviations is required to ensure proper execution of the process.
+
+\subsection{Natural Language Processing}
 

### 2021-11-18 paper.tex
Token based replay

@@
 
+\subsubsection{Token based Replay}
+
+The easiest conformance checking method, both conceptually and algorithmically is probably Token based replay.
+The intuition behind token based replay is to replay an observed trace on a process model, specifically a petri net, and to determine where problems occur.
+
+This is done by keeping track of four numbers: \emph{\underline{p}roduced}, \emph{\underline{c}onsumed}, \emph{\underline{m}issing} and \emph{\underline{r}emaining} tokens during replay.
+According to the semantics of petri nets, whenever an action is fired it consumes one token from all input places and produces one token in each output place.
+However since we are dealing with possibly non-conformant trace, it is possible that a trace contains actions, that are not enabled in the model at that point in time.
+In this case a missing token is added to all input places, that did not contain a token, and the $m$ counter is incremented by the according amount.
+Conversely it might also happen, that a trace can be replayed, but that there are stray tokens left in the petri net after the replay. 
+At the end of the replay the sum of all leftover tokens makes up the $r$ counter.
+Both missing and remaining tokens signal deviation from the process model, but both of these numbers are dependant on the length of traces.
+The longer a trace is the more actions will be taken, the more tokens will be produced, and the more chances there are for tokens to be missing or remaining.
+Importantly a trace where half the produced tokens were never consumed, i.e. remained, should intuitively have a lower fitness than one where only a quarter of produced tokens remained.
+Of course the same relationship holds for the other two counters $m$ and $c$.
+Then one very naturally arrives at a trace fitness defined as 
+\begin{equation}
+fitness(σ,N) = \frac{1}{2}(1-\frac{m_{N,σ}}{c_{N,σ}})+\frac{1}{2}(1-\frac{r_{N,σ}}{p_{N,σ}})
+\end{equation}
+, where $x_{N,σ}$ is the counter when replaying trace $σ$ on petri net $N$.
+Often one does not just want to determine the fitness of one trace but a complete log, then this definition can be extended to 
+\begin{equation}
+	fitness(L,N) = \frac{1}{2}(1-\frac{\sum_{σ\in L}m_{N,σ}}{\sum_{σ\in L}c_{N,σ}})+\frac{1}{2}(1-\frac{\sum_{σ\in L}r_{N,σ}}{\sum_{σ\in L}p_{N,σ}})
+\end{equation}
+Note that log-fitness is not mathematically equivalent to the mean trace fitness.
+
+\subsubsection{Alignments}
+
 \subsection{Natural Language Processing}

### 2021-11-21 paper.tex
Added intro to alignments

@@
 \usepackage{todonotes}
+\usepackage{textalpha}
 % Used for displaying a sample figure. If possible, figure files should
@@
 This is done by keeping track of four numbers: \emph{\underline{p}roduced}, \emph{\underline{c}onsumed}, \emph{\underline{m}issing} and \emph{\underline{r}emaining} tokens during replay.
-According to the semantics of petri nets, whenever an action is fired it consumes one token from all input places and produces one token in each output place.
-However since we are dealing with possibly non-conformant trace, it is possible that a trace contains actions, that are not enabled in the model at that point in time.
+According to the semantics of petri nets, whenever a transition is fired it consumes one token from all input places and produces one token in each output place.
+However since we are dealing with possibly non-conformant trace, it is possible that a trace contains activities, that are not enabled in the model at that point in time.
 In this case a missing token is added to all input places, that did not contain a token, and the $m$ counter is incremented by the according amount.
-Conversely it might also happen, that a trace can be replayed, but that there are stray tokens left in the petri net after the replay. 
+Conversely, it might also happen, that a trace can be replayed, but that there are stray tokens left in the petri net after the replay. 
 At the end of the replay the sum of all leftover tokens makes up the $r$ counter.
-Both missing and remaining tokens signal deviation from the process model, but both of these numbers are dependant on the length of traces.
-The longer a trace is the more actions will be taken, the more tokens will be produced, and the more chances there are for tokens to be missing or remaining.
+Both missing and remaining tokens signal deviation from the process model, but both of these numbers are dependent on the length of traces.
+The longer a trace is the more activities will be taken, the more tokens will be produced, and the more chances there are for tokens to be missing or remaining.
 Importantly a trace where half the produced tokens were never consumed, i.e. remained, should intuitively have a lower fitness than one where only a quarter of produced tokens remained.
@@
 
+Token based methods are generally easy to implement and efficient algorithms are known, however they are not without problems.
+The first is the phenomenon known as "token flooding".
+Since token based methods create missing tokens to enable observed transitions in the log and remaining tokens are not removed, as more missing tokens are added during the simulation of a trace the  amount of stray tokens in the net also grows.
+This overabundance of tokens in the net can then lead to situations were many more transitions are enabled than should be, and later deviations are not detected by token based replay, since they are masked by earlier deviations.
+Also, token based diagnostics are  by their nature place-based diagnostics, they can determine whether a place was missing a token for the execution of a trace, but they cannot determine why said place was missing a token.
+Yet in conformance checking it is often the latter rather than the former question for which answers are desired.
+
 \subsubsection{Alignments}
+
+The second popular method for conformance checking are alignment based methods.
+The goal here is to construct an execution on the model that is as "close" as possible to the observed execution of events in the trace/log.
+If a trace is conformant with the model, this is trivially easy, the "closest" execution possible in the model is exactly the observed trace.
+In the conformant case all moves are so called, synchronous moves, where both the log and the model performed the same event at each step.
+However, if a trace is non-conformant, which is of course the case that is of interest, then a one-to-one mapping between model and trace is not possible.
+To describe that so-called non-synchronous moves are introduced, these describe the case that one of  the model or log perform an activity that does not happen in the other one.
+This can be either a move-on-model-only, where the model takes some transition, which was not observed in the log, or its dual, the move-on-log-only where an event is recorded in the log that is not possible according to the model.
+The weighted sum of misalignments can then be used as a cost metric for an alignment.
 

### 2021-11-22 paper.tex
Finished up on conformance checking

@@
 Conversely, it might also happen, that a trace can be replayed, but that there are stray tokens left in the petri net after the replay. 
-At the end of the replay the sum of all leftover tokens makes up the $r$ counter.
+At the end of the replay the sum of all leftover tokens makes up the $r$ counter. \todo{Some explanation models could be included if the space is there for them}
 Both missing and remaining tokens signal deviation from the process model, but both of these numbers are dependent on the length of traces.
@@
 Of course the same relationship holds for the other two counters $m$ and $c$.
-Then one very naturally arrives at a trace fitness defined as 
+Then one very naturally arrives at a trace fitness defined as:
 \begin{equation}
@@
 The weighted sum of misalignments can then be used as a cost metric for an alignment. 
+The goal is then to construct an optimal alignment between a trace and the model.
+It should be obvious that there are infinitely many such alignments, however we can construct a trace-agnostic alignment, which consists of $n$ moves-on-log-only followed by the shortest path through the model as moves-on-model-only.
+This means there is an effective upper limit on the length of alignments that need to be considered, which in turn means that the problem is decidable. 
+However, the search space can quickly grow infeasibly large, so heuristics need to be employed to determine optimal alignments in a reasonable time frame.
+
+\todo{formula}
+\todo{Possibly some examples}
+
+Alignments overcome many of the problems encountered in token based approaches: 
+They do not suffer from problems like token flooding, and they give transitions based diagnostics, which in the case of process mining is far more useful since transitions encode recorded or recordable activities.
+As such in alignments it is much easier to tell if a certain activity was skipped in a trace without performing further refinements of the diagnostics.
+These benefits do not come without drawbacks though, the main caveat of alignment based methods is that it boils down to a complex search in the alignment space, which is far more demanding than a replay based method.
+As such much research interest has been devoted to the development of heuristics that exploit certain  structures in event logs and/or process models to boost the performance of this search.
 
 \subsection{Natural Language Processing}
+
+As laid out in the previous section, both classical branches of conformance checking exhibit major drawbacks.
+Besides approaches aiming to ameliorate certain disadvantages of such methods, there has also been a growing interest in applying novel techniques from other fields to the problem of conformance checking.
+One such proposal is the application of techniques from the area of natural language processing for conformance checking as discussed in \cite{PBWe20}.
 

### 2021-11-23 paper.tex
-

@@
 Our intuitive expectation would be that a model that allows for exactly those traces contained in the event log would conform perfectly, whereas a model that allows for none of the traces seen in the log would have very low conformance.
-The aim of conformance checking is the formalization of this imprecise intuitive understanding of fitting together and the development of methods and algorithms that can quantify precisely that.
+The aim of conformance checking is the formalization of this imprecise intuitive understanding of fitting together and the development of methods and algorithms that can accurately quantify precisely this intuition.
 
+\subsubsection{Uses}
 The uses of such an approach can generally be divided into two relatively distinct subcategories, depending on whether the event log or the process model are seen as normative.
-In the case where the process model is considered normative, conformance checking allows for the detection of deviations, i.e. observed traces that are not possible according to the model.
-From such information a number of useful analyses can follow, e.g. where do deviations happen, which resources are involved in deviations, how exactly do these traces deviate from the model.
-Both positive and negative conclusions are possible from such situations.
-E.g. such an analysis may reveal that people often skip a step in the process, which actually improves the overall performance of the process, in which case such a step could be made optional.
+If the process model is considered normative, conformance checking allows for the detection of deviations, i.e. observed traces that are not possible according to the model.
+From such information a number of useful analyses can follow, e.g. where do deviations happen, which resources are involved in deviations, and how exactly these traces deviate from the model.
+It should be pointed out that the word "deviation" is negatively connotated in English, however for the purpose of process intelligence it should be viewed as a neutral category. 
+For example an analysis may reveal that people often skip a step in the process, which actually improves the overall performance of the process, based on which refinements to the process model could be made.
 An example of negative conclusions may be the detections of deviations that do not follow proper legal or procedural requirements of the process, such as requiring two different persons to review an important document before signing off on it.
 In such a case knowledge of these deviations is required to ensure proper execution of the process.
+
+In the second case the log is seen as normative and the model considered either imperfect or unknown.
+The most important representative application of this perspective is process discovery, or more specifically the evaluation of discovery algorithms.
+In the case of process discovery a process model has to be constructed from an event log.
+Obviously not all process models are able to describe a process equally good.
+So when developing or using a process discovery algorithm the question how well the discovered process models describe the log often arises.
+
+\subsubsection{Quality criteria}
+%Generally conformance is not a single dimensional criterion, instead it exists in a multi-dimensional space where the different axes represent different understandings of conformance.
+As such it is not really appropriate to talk about one conformance metric, but instead the four major axes should be considered.
+%1. Precision (false negatives): The first of these metrics is precision. This measures how many of the observed traces are actually possible according to the model.
+%2.
+Recall (false positives): Sometimes also referred to as sensitivity, this metric measures how many false positives there are.
+In the case of process models, this is the fraction of traces allowed by the model that are actually observed in the log.
+%3. Simplicity:
+%4. Generalization: Generalization is the models ability to be applicable to possible future traces of a given process. 
+%It would clearly be possible to create a model with perfect precision and recall, by simply encoding the traces themselves in the model.
+However that would not be a model that generalizes well since it captures none of the dynamism of the underlying process.
+This is the most difficult criterion, since it is arguing about unknown possible future behaviour
 
@@
 
+A lot of conformance checking algorithms, notably the classical ones outlined above aim to measure conformance between a log and a model.
+While this is the fundamental question to be answered this comparison between two different objects greatly complicates the task.
+Instead framing the problem in terms of log-to-log comparisons can make the problem much easier to deal with, and allows for a much broader array of techniques, since a multitude of approaches for comparison of similar objects exists.
+To realize this change of perspective a log is generated from the model, which is then compared to the original log.
+
 \section{Results}

### 2021-11-26 paper.tex
Quality criteria

@@
 \subsubsection{Quality criteria}
-%Generally conformance is not a single dimensional criterion, instead it exists in a multi-dimensional space where the different axes represent different understandings of conformance.
+It is important to note that model quality is not a single dimensional criterion, instead it exists in a multi-dimensional space where the different axes represent different quality criteria.
 As such it is not really appropriate to talk about one conformance metric, but instead the four major axes should be considered.
-%1. Precision (false negatives): The first of these metrics is precision. This measures how many of the observed traces are actually possible according to the model.
-%2.
+1. Precision (false negatives): The first of these metrics is precision. This measures how many of the observed traces are actually possible according to the model.
+2.
 Recall (false positives): Sometimes also referred to as sensitivity, this metric measures how many false positives there are.
 In the case of process models, this is the fraction of traces allowed by the model that are actually observed in the log.
-%3. Simplicity:
-%4. Generalization: Generalization is the models ability to be applicable to possible future traces of a given process. 
-%It would clearly be possible to create a model with perfect precision and recall, by simply encoding the traces themselves in the model.
+3. Simplicity: How "simple" a model is, generally a smaller model that describes a process equally well is preferred for reasons such as performance and comprehensibility .
+4. Generalization: Generalization is the models ability to be applicable to possible future traces of a given process. 
+It would clearly be possible to create a model with perfect precision and recall, by simply encoding the traces themselves in the model.
 However that would not be a model that generalizes well since it captures none of the dynamism of the underlying process.
 This is the most difficult criterion, since it is arguing about unknown possible future behaviour
+
+Of these four quality criteria conformance checking is mainly concerned precision and recall, but depending on the algorithms possibly some statements about generalization could be made as well.
 
@@
 Instead framing the problem in terms of log-to-log comparisons can make the problem much easier to deal with, and allows for a much broader array of techniques, since a multitude of approaches for comparison of similar objects exists.
-To realize this change of perspective a log is generated from the model, which is then compared to the original log.
+Such a reformulation of the problem can be achieved since all (reasonably defined) models are able to generate sample traces, and can therefore produce a log.
+This has the additional advantage that it is model-independent, i.e. no limitations except for the ability to generate traces are put on the type of model.
+
+First an activity embeddings for the log were trained, which then allows for the comparison of two traces by comparing their individual activities in the embedding space.
+Given some similarity metric and the real log as well as the model log a dissimilarity matrix can be built up.
+From here on we will assume that each row corresponds to a trace from the model log and each column corresponds to a trace from the real log, i.e.
+$a_{ij}$ is the dissimilarity of the $i$-th trace from the model log with the $j$-th trace of the real log.
 

### 2021-11-29 paper.tex
Extended method

@@
 $a_{ij}$ is the dissimilarity of the $i$-th trace from the model log with the $j$-th trace of the real log.
+As such each column contains the dissimilarity of a trace in the real log with all traces from the model log, with the minimum of a column being the closest match in the model log.
+A trace that can be closely replayed by the model, i.e. one that has a close match to a trace produced from the model, is a well fitting one.
+As such the column minimum corresponds to a fitness metric of the trace and thus the mean of all column minima is a fitness metric between log and log.
+Conversely each row contains all similarities between a trace in the model log and all traces in the real log.
+A precise model should not allow for more traces than observed in the real log, as such each model trace should have as close a match as possible in the real log for the model to be precise.
+As such the row minimum corresponds to a precision metric for the trace in the model log and thus the mean of all row minima is a precision metric between log and log.
+
+\subsection{Distance functions}
+\subsubsection{Word Mover's Distance}
 
 \section{Results}
+
+\subsection{Experimental setup}
+
+To evaluate the suitability of the method three sets of experiments were performed. 
+The first set of experiments focussed on the scalability of the approach, the second aimed to assess the the effect of applying noise to a log and comparing that to the noiseless log.
+The third and last set of experiments was designed to compare the performance of the proposed methods (WMD,ICT \& trace2vec) to existing established conformance metrics, namely alignments, behavioural fitness \cite{GMVB09} and ETC precision \cite{MuCa10}.
+This was achieved by generating 1000 traces from a randomly generated process tree, which form the real log.
+Then a discovery algorithm was applied to this log to discover a model, here Alpha Miner, Inductive Miner infrequent (IMi) with noise levels 0 and 1 and the ILP Miner were selected as discovery algorithms.
+Then fitness and precision between the discovered model and the real log were calculated using the previously mentioned algorithms aswell as the method described in the paper.
 

### 2021-11-29 paper.tex
Discussion

@@
 %
-\title{Seminar Paper}
-\subtitle{Seminar Business Processes and the Internet of Things \\ Conformance Checking Using Activity and Trace Embeddings.}
+\title{Conformance Checking Using Embeddings and the Applicability of Such Methods in the Internet of Things}
 %
@@
 %
-\author{Jan Kruska \\ Supervisor: Dr. István Koren}
+\author{Jan Kruska}
 %
@@
 As such the column minimum corresponds to a fitness metric of the trace and thus the mean of all column minima is a fitness metric between log and log.
-Conversely each row contains all similarities between a trace in the model log and all traces in the real log.
+Conversely, each row contains all similarities between a trace in the model log and all traces in the real log.
 A precise model should not allow for more traces than observed in the real log, as such each model trace should have as close a match as possible in the real log for the model to be precise.
@@
 To evaluate the suitability of the method three sets of experiments were performed. 
-The first set of experiments focussed on the scalability of the approach, the second aimed to assess the the effect of applying noise to a log and comparing that to the noiseless log.
+The first set of experiments focussed on the scalability of the approach, especially since more traditional approaches do not scale well.
+This aspect is doubly important when talking about the Internet of Things, where computing resources are generally far more constrained, while still producing large amounts of event data.
+
+The second set of experiments aimed to determine whether the method responded as expected when providing noisy logs.
+These experiments were designed to verify the soundness of approach.
+This was done by generating logs from random process trees generated by pm4py, applying random noise on these logs and determining the conformance between the noiseless and noisy logs.
+The expectation is that any reasonable conformance metric should deteriorate the more noise is added to the log.
+
 The third and last set of experiments was designed to compare the performance of the proposed methods (WMD,ICT \& trace2vec) to existing established conformance metrics, namely alignments, behavioural fitness \cite{GMVB09} and ETC precision \cite{MuCa10}.
@@
 Then a discovery algorithm was applied to this log to discover a model, here Alpha Miner, Inductive Miner infrequent (IMi) with noise levels 0 and 1 and the ILP Miner were selected as discovery algorithms.
-Then fitness and precision between the discovered model and the real log were calculated using the previously mentioned algorithms aswell as the method described in the paper.
+Then fitness and precision between the discovered model and the real log were calculated using the previously mentioned algorithms as well as the method described in the paper.
 
 \section{Discussion}
+
+Peeperkorn et al. obtained promising first results for a novel bedding based approach towards conformance checking.
+Yet as the focus was mainly on the introduction and development of a prototype for such an approach there are some natural limitations.
+Arguably the biggest limitation are the logs used for the experimental validation.
+All used logs were completely synthetic, generated from random process trees.
+It is unclear how well the 12 trees used for this resemble real processes and whether these tree configurations are sufficiently representative for the variation exhibited in real life trees\footnote{12 tree configurations were used, 3 sizes and 4 different probability distributions for operations, how strong these vary should be investigated}.
+As such it should be a priority to test the proposed methods on real logs, possibly popular benchmark cases and also to systematically broaden the parameters for random process tree generation to cover more different classes.
+
+%Secondly the sizes of the process logs for the scalability experiment were between 100 to 5000 traces, the log sizes for the noise and discovery experiment were fixed at 1000 traces.
+
+Furthermore, the algorithms used have several parameters which were set as seemingly reasonable standard values.
+A thorough investigation into the effect of these parameters should follow, since it can not be known whether similar defaults should be used in conformance checking  as in classical NLP problems.
+
+Apart from that two of the metrics proposed -- WMD and ICT -- do not take the order of words/activities into account.
+This is due to the fact that for a lot of NLP problems order is of lesser importance and tasks like document keyword detection can treat a document as an orderless bag of words.
+At least from an intuitive understanding of conformance checking order of activities is integrally important, and it should at least be investigated if there are significant differences between ordered and orderless approaches with regard to conformance checking.
+The authors themselves suggest considering the use of $n$-grams instead of 1-grams, since their application seems more feasible in business processes as compared to classical NLP.
+
+Lastly the paper should be understood as a first stepping stone for the use of NLP-related algorithms for the task of conformance checking.
+The use of embeddings is often a first step in such approaches, but it is entirely possible that more advanced NLP algorithms may give even better results.
+As such further research into the applicability of a variety of other methods could be fruitful.
+The authors especially mention $n$-grams, Embeddings from Language Models, Global Vectors for Word Representation and recurrent neural networks.
 

### 2021-11-30 paper.tex
Extended some parts

@@
 \begin{equation}
-fitness(σ,N) = \frac{1}{2}(1-\frac{m_{N,σ}}{c_{N,σ}})+\frac{1}{2}(1-\frac{r_{N,σ}}{p_{N,σ}})
+fitness(\sigma,N) = \frac{1}{2}(1-\frac{m_{N,\sigma}}{c_{N,\sigma}})+\frac{1}{2}(1-\frac{r_{N,\sigma}}{p_{N,\sigma}})
 \end{equation}
-, where $x_{N,σ}$ is the counter when replaying trace $σ$ on petri net $N$.
+, where $x_{N,\sigma}$ is the counter when replaying trace $\sigma$ on petri net $N$.
 Often one does not just want to determine the fitness of one trace but a complete log, then this definition can be extended to 
 \begin{equation}
-	fitness(L,N) = \frac{1}{2}(1-\frac{\sum_{σ\in L}m_{N,σ}}{\sum_{σ\in L}c_{N,σ}})+\frac{1}{2}(1-\frac{\sum_{σ\in L}r_{N,σ}}{\sum_{σ\in L}p_{N,σ}})
+	fitness(L,N) = \frac{1}{2}(1-\frac{\sum_{\sigma\in L}m_{N,\sigma}}{\sum_{\sigma\in L}c_{N,\sigma}})+\frac{1}{2}(1-\frac{\sum_{\sigma\in L}r_{N,\sigma}}{\sum_{\sigma\in L}p_{N,\sigma}})
 \end{equation}
@@
 
+\subsection{Embeddings}
+Embeddings are a popular machine learning approach that has been used for a variety of tasks with the most successful applications being in the fields of natural language processing and computer vision.
+The fundamental idea of embeddings is to train some form of embedding function that embeds complex objects, such as words or documents in the case of NLP or pictures and video sequences in the case of computer vision in a vectors space\footnote{To be more precise: a Hilbert space, since well-defined notions of distances and angles are necessary.}.
+Such an embedding function then enables a proper mathematical treatment of these non-vector objects as vectors, which allows for the application of a broad range of algorithms.
+Most importantly it makes it possible to define notions of distance and/or (dis-)similarity needed for machine learning and data analysis tasks.
+
+\subsection{word2vec}
+
 \section{Method}
@@
 \subsubsection{Word Mover's Distance}
+
+\subsubsection{Trace embeddings}
+In contrast to the two previous approaches, which used activity embeddings, it is also possible to train trace embeddings.
+The relationship between \emph{act2vec} and \emph{trace2vec} is analogous to the one between \emph{word2vec} and \emph{doc2vec}.
+This introduces additional instability on the trace level, since there will generally many more traces than activities, but allows for the direct application of distance metrics in the vector space when comparing two traces.
+This is much less computationally expensive as the previous two approaches which were complex distance metric between two sets of embeddings.
 

### 2021-11-30 paper.tex
Extended IoT intro

@@
 %
-\title{Conformance Checking Using Embeddings and the Applicability of Such Methods in the Internet of Things}
+\title{Conformance Checking Using Embeddings and their Applicability in the Internet of Things}
 %
@@
 And lastly business processes often struck the balance between too simple and too complicated, in that they exhibited enough variability to be interesting to analyse but were still simple enough as to enable the use of the early process mining algorithms.
-So it should be stated that while process mining is of great use for classical business processes, these are not the only areas for which it could be useful.
+So it should be stated that while process mining is of great use for classical business processes, these are not the only areas for which it could potentially be useful.
 
 One such area of interest is the Internet of Things.
-In recent years a vast infrastructure of small networked devices typically with some sensors attached has developed. 
-This is especially interesting in the case for automation in manufacturing for which the term Internet of Production has been coined.
+In the last two decades more and more devices and specifically controller for devices have moved from implementions in hardware to implementations in software.
+Additionally as the cost for networking components has shrunk more and more of these devices have some networking capabilities, e.g. in the form of IP, bluetooth or RFID.
+This vast infrastructure of small networked devices is fertile ground for process analysis.
+These controllers generally have some attached sensors to monitor and control the devices they are attached to and in combination with these produce an equally vast amount of events.
+This is especially interesting in the case of automation in manufacturing for which the term Internet of Production has been coined.
+Here fully digitized networked control systems and the information pooling and sharing thos bring with it could greatly enhance the production capabilities of not just single production lines but entire automated factories.
 Both these "Internet"'s\footnote{Note that there will not be a very clear distinction between these two terms in this paper.
-The object of interest here is a highly distributed network of interacting devices, that generate a large amount of event data about their surroundings.
-Which specific environment they are in is less important here.}
-constitute a highly digitized network in which avast amount of data, including event data, is being generated and measured.
-Especially in the case of manufacturing there is a large monetary interest in optimizing production pipelines.
-And lastly in the case of the Internet of Things there are complex hidden processes to be discovered, which can challenge newer and more advanced process mining algorithms in a way that other areas might not.
+The object of interest here is a highly distributed networks of interacting devices, that generate a large amount of event data about their surroundings.
+Which specific environment they are in, is  of lesser importance here.}
+constitute a highly digitized network in which vast amounts of data, including event data, are being generated and measured.
+Especially in the case of manufacturing there is a large financial interest in optimizing production pipelines.
+
+However, the Internet of Things is also very attractive from the process analysis research perspective.
+During the birth of process mining as a discipline a big focus laid on classical business processes, such as purchase-to-pay and order-to-cash.
+Yet as the field matures the capabilities of algorithms and accordingly the difficulty of interesting problems grows.
+As such there is research demand for different -- to test whether algorithms perform equally well in other scenarios --, larger -- to improve scalability of algorithms -- and more complex -- to test and improve the capacity to deal with more interwoven processes -- problems.
+At the same time only areas with a high level of digitalization can realistically be considered here since it is of paramount priority to be able to properly obtain the event data of any process in question.
+The Internet of Things fulfils all these categories, it is digital by design, so relatively few efforts have to be made to obtain large amount of well-enough structured event data and the scale and complexity of the problem can scale up very well with growing network sizes.
+
 \section{Background}
@@
 Embeddings are a popular machine learning approach that has been used for a variety of tasks with the most successful applications being in the fields of natural language processing and computer vision.
-The fundamental idea of embeddings is to train some form of embedding function that embeds complex objects, such as words or documents in the case of NLP or pictures and video sequences in the case of computer vision in a vectors space\footnote{To be more precise: a Hilbert space, since well-defined notions of distances and angles are necessary.}.
+The fundamental idea of embeddings is to train some form of embedding function that embeds complex objects, such as words or documents in the case of NLP or pictures and video sequences in the case of computer vision in a vectors space\footnote{To be more precise: a Hilbert space, since well-defined notions of distances and angles are necessary and for that a scalar product  is needed.}.
 Such an embedding function then enables a proper mathematical treatment of these non-vector objects as vectors, which allows for the application of a broad range of algorithms.

### 2021-12-01 paper.tex
Extended Internet of Things

@@
 \usepackage{todonotes}
-\usepackage{textalpha}
+\usepackage[autostyle]{csquotes}  
 % Used for displaying a sample figure. If possible, figure files should
@@
 
-One such area of interest is the Internet of Things.
-In the last two decades more and more devices and specifically controller for devices have moved from implementions in hardware to implementations in software.
-Additionally as the cost for networking components has shrunk more and more of these devices have some networking capabilities, e.g. in the form of IP, bluetooth or RFID.
-This vast infrastructure of small networked devices is fertile ground for process analysis.
+In the last two decades the cost for networking components has decreases significantly and a growing number of microcontrollers, embedded systems and electronic devices now have some form of networking ability.
+This increasing networked structure that enables easy information sharing between the members of the network has become known under a few names, most prominently sa the "Internet of Things".
+Unfortunately due to shifting developments in the last two decades and marketing efforts associated with the Internet of Things it is hard to pin down the exact meaning of the term. 
+The International Telecommunication Union gives the following succinct definition of the Internet of Things in their recommendation \cite{ITUT12} regarding just that:
+\blockquote{[The Internet of Things is] A  global  infrastructure  for  the  information  society,  enabling  advanced  services  by  interconnecting  (physical  and  virtual)  things  based  on  existing  and  evolving  interoperable information and communication technologies.}
+
+It should be noted that this definition is very broad and extends beyond the notion of the "Smart Home" that has become somewhat of a representative of the Internet of Things.
+The definition neither limits the scale (locally, nationally or even globally) nor the range of use cases.
+The rest of the paper will follow this definition since the object of interest here are fully digitized networked control systems and the information pooling and sharing those bring with it.
+
+This vast infrastructure of small networked devices could prove to be fertile ground for process analysis.
 These controllers generally have some attached sensors to monitor and control the devices they are attached to and in combination with these produce an equally vast amount of events.
-This is especially interesting in the case of automation in manufacturing for which the term Internet of Production has been coined.
-Here fully digitized networked control systems and the information pooling and sharing thos bring with it could greatly enhance the production capabilities of not just single production lines but entire automated factories.
-Both these "Internet"'s\footnote{Note that there will not be a very clear distinction between these two terms in this paper.
-The object of interest here is a highly distributed networks of interacting devices, that generate a large amount of event data about their surroundings.
-Which specific environment they are in, is  of lesser importance here.}
-constitute a highly digitized network in which vast amounts of data, including event data, are being generated and measured.
-Especially in the case of manufacturing there is a large financial interest in optimizing production pipelines.
+This is especially interesting in the case of automation in manufacturing\cite{JKM*20} for which the term Internet of Production has been coined, here the hope is that networked information sharing between controllers on a production line or factory floor could greatly enhance the production capabilities of not just single production lines but entire automated factories.
+Especially in the case of manufacturing there is a large financial interest in optimizing production efficiency for various reasons such as increasing speed, increasing productivity or reducing downtime.
 
@@
 Yet as the field matures the capabilities of algorithms and accordingly the difficulty of interesting problems grows.
-As such there is research demand for different -- to test whether algorithms perform equally well in other scenarios --, larger -- to improve scalability of algorithms -- and more complex -- to test and improve the capacity to deal with more interwoven processes -- problems.
+As such there is research demand \cite{JKM*20} for different -- to test whether algorithms perform equally well in other scenarios --, larger -- to improve scalability of algorithms -- and more complex -- to test and improve the capacity to deal with more interwoven processes -- problems.
 At the same time only areas with a high level of digitalization can realistically be considered here since it is of paramount priority to be able to properly obtain the event data of any process in question.
+This has been a problem in the past when considering any process for which event data has to be manually entered, since in all these cases there will be discrepancies between digitally recorded process and the real world execution.
 The Internet of Things fulfils all these categories, it is digital by design, so relatively few efforts have to be made to obtain large amount of well-enough structured event data and the scale and complexity of the problem can scale up very well with growing network sizes.
+Furthermore it is also possible to use techniques from the Internet of Things to further digitize classical processes and reduce dependencies on manual event recording.
+
+Naturally there are challenges to be overcome if one aims to integrate business process modelling into the Internet of Things.
+The first two major difference are attributable to the structure of the Internet of Things.
+Firstly the Internet of Things is made up numerous small devices all with limited compute capabilities.
 

### 2021-12-01 paper.tex
Reworked chapter 3

@@
 Firstly the Internet of Things is made up numerous small devices all with limited compute capabilities.
+This limits the complexity of algorithms that can be performed on each of the devices and means that either a separate system with the role of performing analyses needs to be introduced or distributed algorithms need to be developed.
+Overall it should be noted that asynchronous decentralized networks are common for the Internet of Things, which needs to be taken into account when applying BPM.
+Secondly the the Internet of Things has both the potential and demand for greater number of online analyses, i.e.
+in contrast to classical business processes it is much more important to evaluate a process during the execution, to give feedback and to possibly even influence a process during its execution.
 
@@
 
-A lot of conformance checking algorithms, notably the classical ones outlined above aim to measure conformance between a log and a model.
-While this is the fundamental question to be answered this comparison between two different objects greatly complicates the task.
-Instead framing the problem in terms of log-to-log comparisons can make the problem much easier to deal with, and allows for a much broader array of techniques, since a multitude of approaches for comparison of similar objects exists.
-Such a reformulation of the problem can be achieved since all (reasonably defined) models are able to generate sample traces, and can therefore produce a log.
-This has the additional advantage that it is model-independent, i.e. no limitations except for the ability to generate traces are put on the type of model.
+A lot of conformance checking algorithms, notably the classical ones outlined above, aim to measure conformance between a log and a model.
+While this is the fundamental question to be answered this comparison between two different types of objects greatly complicates the task.
+However by re-framing the problem on can greatly simplify it.
+Instead formulating the problem in terms comparing a model and a log one can formulate it as a comparison problem of a real log to a model log.
+Such a reformulation of the problem is possible since all (reasonably defined) models are able to generate sample traces, and can therefore produce a model log.
+Then the whole problem is reframed as log-to-log comparisons, i.e. determining similarities between objects of the same type, for which a broad range of techniques already exist.
+This has the additional advantage that it is model-independent, since no limitations apart from the ability to generate traces are put on the type of model.
 
-First an activity embeddings for the log were trained, which then allows for the comparison of two traces by comparing their individual activities in the embedding space.
+Given two logs, a model and a real one, it is first necessary to train the \emph{act2vec}\cite{KBWe18} (and also \emph{trace2vec}) embeddings.
+
+\subsection{act2vec}
+The first two methods utilize \emph{act2vec} to train activity embeddings.
+These activity embeddings then allows for the comparison of two traces by comparing their individual activities in the embedding space.
+Then every trace constitutes a set of different activities that can be expressed in the embedding space.
+Every trace then describes a probability distribution over the activities contained in it, so given an appropriate distance metric for probability distributions such as the Earth Movers Distance it is possible to determine the distance (or conversely similarity) of two traces.
+
+\subsubsection{Word Mover's Distance}
+
+\todo{Use pseudocode from paper?}
+\todo{Describe both WMD and ICT in separate sections, or just mention that ICT gives a relaxed formulation of WMD that can be easier to compute}
+
+\subsection{trace2vec}
+In contrast to the two previous approaches, which used activity embeddings, it is also possible to train trace embeddings.
+The relationship between \emph{act2vec} and \emph{trace2vec} is analogous to the one between \emph{word2vec} and \emph{doc2vec}.
+When using this method every trace is embedded into a vector space and any distance metric that is deemed appropriate can be chosen.
+In the paper the cosine similarity \todo{formula?} was chosen for its simplicity and the fact that it is bounded in the interval $[-1,1]$.
+This is much less computationally expensive as the previous two approaches which were complex distance metric between two sets of embeddings.
+
+\subsection{Definition of Fitness and precision}
 Given some similarity metric and the real log as well as the model log a dissimilarity matrix can be built up.
@@
 As such the row minimum corresponds to a precision metric for the trace in the model log and thus the mean of all row minima is a precision metric between log and log.
-
-\subsection{Distance functions}
-\subsubsection{Word Mover's Distance}
-
-\subsubsection{Trace embeddings}
-In contrast to the two previous approaches, which used activity embeddings, it is also possible to train trace embeddings.
-The relationship between \emph{act2vec} and \emph{trace2vec} is analogous to the one between \emph{word2vec} and \emph{doc2vec}.
-This introduces additional instability on the trace level, since there will generally many more traces than activities, but allows for the direct application of distance metrics in the vector space when comparing two traces.
-This is much less computationally expensive as the previous two approaches which were complex distance metric between two sets of embeddings.
 

### 2021-12-01 paper.tex
Fixes before preliminary version

@@
 \usepackage[autostyle]{csquotes}  
+\usepackage{hyperref}
 % Used for displaying a sample figure. If possible, figure files should
@@
 %
-%\titlerunning{Abbreviated paper title}
+\titlerunning{Conformance Checking Using Embeddings in the IoT}
 % If the paper title is too long for the running head, you can set
@@
 %
-%\section{Planned structure}
-%The following list shall give a short overview of the intended general structure of the seminar paper. For each section the main questions that should be answered by it are listed.
-%\begin{enumerate}
-%	\item Abstract
-%	\item Introduction
-%	\begin{enumerate}
-%		\item What is the motivation of the paper
-%	\end{enumerate}
-%	\item Background
-%	\begin{enumerate}
-%		\item What is conformance checking, how is it useful and why would you do it, which methods are there, what are advantages and disadvantages of said methods.
-%		\item What is NLP (briefly), what are embeddings generally and word embeddings specifically, what are word2vec and doc2vec and how do they approach the NLP problems.
-%		\item What parallels are there between NLP and conformance checking
-%		\item If there are these parallels, how could such NLP mechanism be adapted (theoretically not practically) for conformance checking, what could the advantages be of such an approach, what could be disadvantages and/or problems that will need addressing.
-%		\item What is the Internet of Things and why would one wish to perform process analysis there
-%	\end{enumerate}
-%	\item Method
-%	\begin{enumerate}
-%		\item How were word2vec and doc2vec adapted to conformance checking in the paper (I.e. practical adaption)
-%	\end{enumerate}
-%	\item Results
-%	\begin{enumerate}
-%		\item What are the results given in the paper
-%		\item What metrics were used to evaluate the performance of the approach presented in the paper, are they appropriate, are there other possible metrics, if so why was this one chosen, what advantages or disadvantages do different metrics have.
-%		\item What are the results when using their code and reproducing the results (ideally the same)
-%	\end{enumerate}
-%	\item Outlook
-%	\begin{enumerate}
-%		\item What future work do the authors suggest
-%		\item What problems were encountered when trying to reproduce the results from the paper.
-Could they be reproduced completely, just in part or not at all?
-If so, are there suggestions on how could these problems be mitigated.
-%	\end{enumerate}
-%\end{enumerate}
 
@@
 In the last two decades the cost for networking components has decreases significantly and a growing number of microcontrollers, embedded systems and electronic devices now have some form of networking ability.
-This increasing networked structure that enables easy information sharing between the members of the network has become known under a few names, most prominently sa the "Internet of Things".
+This increasing networked structure that enables easy information sharing between the members of the network has become known under a few names, most prominently as the "Internet of Things".
 Unfortunately due to shifting developments in the last two decades and marketing efforts associated with the Internet of Things it is hard to pin down the exact meaning of the term. 
-The International Telecommunication Union gives the following succinct definition of the Internet of Things in their recommendation \cite{ITUT12} regarding just that:
+The International Telecommunication Union gives the following succinct definition of the Internet of Things in their recommendation \cite{ITUT12} on the topic:
 \blockquote{[The Internet of Things is] A  global  infrastructure  for  the  information  society,  enabling  advanced  services  by  interconnecting  (physical  and  virtual)  things  based  on  existing  and  evolving  interoperable information and communication technologies.}
@@
 The Internet of Things fulfils all these categories, it is digital by design, so relatively few efforts have to be made to obtain large amount of well-enough structured event data and the scale and complexity of the problem can scale up very well with growing network sizes.
-Furthermore it is also possible to use techniques from the Internet of Things to further digitize classical processes and reduce dependencies on manual event recording.
+Furthermore, it is also possible to use techniques from the Internet of Things to further digitize classical processes and reduce dependencies on manual event recording.
 
@@
 Overall it should be noted that asynchronous decentralized networks are common for the Internet of Things, which needs to be taken into account when applying BPM.
-Secondly the the Internet of Things has both the potential and demand for greater number of online analyses, i.e.
+Secondly the Internet of Things has both the potential and demand for greater number of online analyses, i.e.
 in contrast to classical business processes it is much more important to evaluate a process during the execution, to give feedback and to possibly even influence a process during its execution.
@@
 Obviously not all process models are able to describe a process equally good.
-So when developing or using a process discovery algorithm the question how well the discovered process models describe the log often arises.
+So when developing or using a process discovery algorithm the question of how well the discovered process models describe the log often arises.
 
@@
 As such it is not really appropriate to talk about one conformance metric, but instead the four major axes should be considered.
-1. Precision (false negatives): The first of these metrics is precision. This measures how many of the observed traces are actually possible according to the model.
+1.
+Fitness (few false negatives): The first of these metrics is fitness.
+This quality criterion is closely related to the statistical measure of recall.
+In the case of business process management fitness measures how many of the observed traces are actually possible executions of the model.
 2.
-Recall (false positives): Sometimes also referred to as sensitivity, this metric measures how many false positives there are.
+Precision (few false positives): Closely related to the statistical measure of precision, this metric measures how many false positives there are in relation to true positives.
 In the case of process models, this is the fraction of traces allowed by the model that are actually observed in the log.
 3. Simplicity: How "simple" a model is, generally a smaller model that describes a process equally well is preferred for reasons such as performance and comprehensibility .
-4. Generalization: Generalization is the models ability to be applicable to possible future traces of a given process. 
+4. Generalization: Generalization is the model's ability to be applicable to possible future traces of a given process. 
 It would clearly be possible to create a model with perfect precision and recall, by simply encoding the traces themselves in the model.
-However that would not be a model that generalizes well since it captures none of the dynamism of the underlying process.
-This is the most difficult criterion, since it is arguing about unknown possible future behaviour
+However, that would not be a model that generalizes well since it captures none of the dynamism of the underlying process.
+This is the most difficult criterion, since it is arguing about unknown possible future behaviour.
 
@@
 The easiest conformance checking method, both conceptually and algorithmically is probably Token based replay.
-The intuition behind token based replay is to replay an observed trace on a process model, specifically a petri net, and to determine where problems occur.
+The intuition behind token based replay is to replay an observed trace on a process model, specifically a Petri net, and to determine where problems occur.
 
 This is done by keeping track of four numbers: \emph{\underline{p}roduced}, \emph{\underline{c}onsumed}, \emph{\underline{m}issing} and \emph{\underline{r}emaining} tokens during replay.
-According to the semantics of petri nets, whenever a transition is fired it consumes one token from all input places and produces one token in each output place.
+According to the semantics of Petri nets, whenever a transition is fired it consumes one token from all input places and produces one token in each output place.
 However since we are dealing with possibly non-conformant trace, it is possible that a trace contains activities, that are not enabled in the model at that point in time.
 In this case a missing token is added to all input places, that did not contain a token, and the $m$ counter is incremented by the according amount.
-Conversely, it might also happen, that a trace can be replayed, but that there are stray tokens left in the petri net after the replay. 
+Conversely, it might also happen, that a trace can be replayed, but that there are stray tokens left in the Petri net after the replay. 
 At the end of the replay the sum of all leftover tokens makes up the $r$ counter. \todo{Some explanation models could be included if the space is there for them}
@@
 \end{equation}
-, where $x_{N,\sigma}$ is the counter when replaying trace $\sigma$ on petri net $N$.
+, where $x_{N,\sigma}$ is the counter when replaying trace $\sigma$ on Petri net $N$.
 Often one does not just want to determine the fitness of one trace but a complete log, then this definition can be extended to 
@@
 A lot of conformance checking algorithms, notably the classical ones outlined above, aim to measure conformance between a log and a model.
-While this is the fundamental question to be answered this comparison between two different types of objects greatly complicates the task.
-However by re-framing the problem on can greatly simplify it.
-Instead formulating the problem in terms comparing a model and a log one can formulate it as a comparison problem of a real log to a model log.
+While this is the fundamental question to be answered, this comparison between two different types of objects greatly complicates the task.
+However, by re-framing the problem on can greatly simplify it.
+Instead of formulating the problem in terms of model-to-log comparison, one can formulate it as a comparison problem of a real log to a model log.
 Such a reformulation of the problem is possible since all (reasonably defined) models are able to generate sample traces, and can therefore produce a model log.

### 2021-12-12 paper.tex
Scalability experiment

@@
 \usepackage{hyperref}
+\usepackage{cleveref}
 % Used for displaying a sample figure. If possible, figure files should
@@
 
-Given two logs, a model and a real one, it is first necessary to train the \emph{act2vec}\cite{KBWe18} (and also \emph{trace2vec}) embeddings.
-
+\color{blue}
+Given two logs, one real and one produced by replaying the model, it is first necessary to train the \emph{act2vec}\cite{KBWe18} embedding.
+\color{black}
 \subsection{act2vec}
@@
 
+\color{blue}
+\subsection{Scalability experiment}
+\begin{figure}
+	\includegraphics[width=1\textwidth]{figures/scaling}
+	\caption{Runtimes for all three methods for varying sizes of logs and dictionaries. Data can be found in \cite{MuCa10} Table 2}
+	\label{fig:scalability}
+\end{figure}
+The first performed experiment aimed to asses the performance  of the three proposed methods.
+The experiments were run on an Intel Core i7-9850h, a mid-range consumer CPU.
+Experiments were run for all three methods for different sized logs and different sized dictionaries, in this case dictionary size is determined by the number of different activities in the log.
+All experiments were performed in python, however the Word Mover's distance was calculated using pyemd, a python wrapper to calculate the WMD/Emd with numpy efficiency.
+As such when comparing ICT and WMD times the efficiency difference between python and C should be taken into account.
+
+The resulting times are shown in \cref{fig:scalability}.
+Over all log sizes a similar pattern is observable, with WMD and ICT behaving somewhat similar and \emph{trace2vec} consistently outperforming the other two methods in all experiments.
+For small dictionary sizes  (~10) WMD does outperform ICT, however that is likely due to the aforementioned efficiency differences between the implementations.
+It is doubly notable that despite these efficiency differences ICT already starts to outperform WMD for dictionary sizes of 20, with the gap growing even larger for dictionaries of size 30, ICT is finished after roughly half the time WMD takes.
+These experiments seem to suggest that ICT scales much better with larger dictionary sizes.
+Especially when considering that the current implementation is still unoptimized ICT could very well serve as a more efficient alternative to WMD, especially when working with complex logs.
+It should also be noted that the relative run time difference between both methods seems so slightly scale in the ICT's favor, starting out at $\frac{45}{75}=0.6$ for a log of size 500 and improving to $\frac{3824}{7032}\approx 0.54$ for logs of size 5000.
+
+Lastly the \emph{trace2vec} methods substantially outperforms both the other methods, since only the cosine similarity, a simple mathematical formula needs to evaluated at run time.
+This comes with the additional overhead of training trace embeddings, however according to the authors training that "does not take a long time" but they don't include statistics in that regard.
+The \emph{trace2vec} method has the additional benefit of not being dependent on the activities during run time, since traces are directly compared in the trace embedding space, which means that the size of the dictionary is irrelevant for this approach, making it even more attractive for processes with large numbers of activities than the ICT.
+\todo{Include log size scaling plot? Do I have the space for that? It is not really that interesting as far as I can tell}
+
+\subsection{Noise experiment}
+
+\subsection{Discovery experiment}
+
+\color{black}
 \section{Discussion}

### 2021-12-12 paper.tex
Discovery experiment

@@
 The expectation is that any reasonable conformance metric should deteriorate the more noise is added to the log.
-
+\todo{Explain more how process trees were generated}
 The third and last set of experiments was designed to compare the performance of the proposed methods (WMD,ICT \& trace2vec) to existing established conformance metrics, namely alignments, behavioural fitness \cite{GMVB09} and ETC precision \cite{MuCa10}.
@@
 
+The purpose of the last experiment was the comparison of the three proposed techniques to established conformance checking algorithms.
+The results of this experiment can be found in \cite{PBWe20} Table 5.
+\todo{Include their data? Manually as table or maybe as plot. If so what kind plot would you suggest}
+The results from the discovery experiment seem to suggest that all three methods are able to capture a notion of conformance.
+Especially when the model is of high quality both the proposed and validation conformance checking techniques often agree on a perfect score.
+However, it should be noted that there are quite a few instances where all three proposed methods assign perfect fitness or precision despite the others producing imperfect scores.
+This is worrying since one of the most basic requirements for a good conformance checking technique is not assigning perfect scores to models that are able to replay fewer or more traces than in the log.
+It is unclear whether that is due to the unoptimized nature of the methods, it could be the case that the methods are not sensitive enough, which could be fixed by varying the parameters, or due to the limited size of the model logs, which were limited to 1000 traces, which puts an upper limit on the amount of behaviour that the embeddings are able to observe.
+
+Yet when models deteriorate there is a tendency for all measurements to move together.
+At the current point only a qualitative analysis for imperfect models is possible since the values determined by WMD, ICT and \emph{trace2vec} are not proper metrics since they do not fall into the $0,1$ range.
+As such it is hard to interpret what a non optimal value actually means, and as such the data does not allow for a quantitative comparison  at this point.
+The results that were obtained however suggest that these methods could be a useful alternative to established techniques, and that further research into them is warranted.
+
+It is of course also important to point out that the validation techniques should not be seen as perfect normative techniques, since both of these also significantly disagree for some models.
+
 \color{black}
 \section{Discussion}
+
+\todo{Proper fitness metric}
 
@@
 
-%Secondly the sizes of the process logs for the scalability experiment were between 100 to 5000 traces, the log sizes for the noise and discovery experiment were fixed at 1000 traces.
-
+\color{blue}
+It is also a  prerequisite for further research and possible usage of such methods to convert the distance metrics obtained into proper conformance metrics, especially by restricting values to the interval $[0,1]$.
+When that is done further quantitative comparisons between the updated methods and established conformance checking techniques should be performed.
 Furthermore, the algorithms used have several parameters which were set as seemingly reasonable standard values.
 A thorough investigation into the effect of these parameters should follow, since it can not be known whether similar defaults should be used in conformance checking  as in classical NLP problems.
-
+Special attention should be placed on those cases for which the NLP techniques produced perfect values, whereas the others did not.
+The methods should be tested with completely perfect and completely imperfect models regarding fitness and precision, as well as nearly perfect and nearly imperfect models to verify that the methods are able to correctly classify both ends of model spectrum and not misclassify nearly optimal models as perfect.
+\color{black}
 Apart from that two of the metrics proposed -- WMD and ICT -- do not take the order of words/activities into account.

### 2021-12-13 paper.tex
Structure + process trees

@@
 
-A lot of conformance checking algorithms, notably the classical ones outlined above, aim to measure conformance between a log and a model.
+Many conformance checking algorithms, notably the classical ones outlined above, aim to measure conformance between a log and a model.
 While this is the fundamental question to be answered, this comparison between two different types of objects greatly complicates the task.
@@
 This has the additional advantage that it is model-independent, since no limitations apart from the ability to generate traces are put on the type of model.
+\begin{figure}
+	\includegraphics[width=1\textwidth]{figures/structure}
+	\caption{General structure of the approach}
+	\label{fig:structure}
+\end{figure}
 
 \color{blue}
-Given two logs, one real and one produced by replaying the model, it is first necessary to train the \emph{act2vec}\cite{KBWe18} embedding.
+Three different techniques were outlined in the paper, all following a similar structure outlined in \cref{fig:structure}.
+First a model log is produced from the model by using an appropriate replay semantics for the model.
+Then, given these two logs, one real and one produced by replaying the model, it is possible to train the \emph{act2vec}\cite{KBWe18} embedding.
+Based on these embeddings a dissimilarity function needs to be defined to compare different traces, however the \emph{act2vec} embedding only yields distance measurements between activities and not between traces.
+Here the differences between the three techniques come into play.
+The first two, the Word Mover's Distance and Iterative Constrained Transfers, can directly utilize the distances between activities to determine a distance between two collections of activities.
+The last one, \emph{trace2vec}, further needs to train a trace embedding based on activity embeddings, and can then perform direct comparisons in the trace embedding space.
+All three methods however lead to a reasonable dissimilarity metric between traces.
+Using one of these metrics a dissimilarity matrix can be built up describing the pairwise dissimilarities between the real log and the model log.
 \color{black}
+From here on we will assume that each row corresponds to a trace from the model log and each column corresponds to a trace from the real log, i.e.
+$a_{ij}$ is the dissimilarity of the $i$-th trace from the model log with the $j$-th trace of the real log.
+As such each column contains the dissimilarity of a trace in the real log with all traces from the model log, with the minimum of a column being the closest match in the model log.
+A trace that can be closely replayed by the model, i.e. one that has a close match to a trace produced from the model, is a well fitting one.
+As such the column minimum corresponds to a fitness metric of the trace and thus the mean of all column minima is a fitness metric between log and log.
+Conversely, each row contains all similarities between a trace in the model log and all traces in the real log.
+A precise model should not allow for more traces than observed in the real log, as such each model trace should have as close a match as possible in the real log for the model to be precise.
+As such the row minimum corresponds to a precision metric for the trace in the model log and thus the mean of all row minima is a precision metric between log and log.
+
 \subsection{act2vec}
@@
 When using this method every trace is embedded into a vector space and any distance metric that is deemed appropriate can be chosen.
-In the paper the cosine similarity \todo{formula?} was chosen for its simplicity and the fact that it is bounded in the interval $[-1,1]$.
+In the paper the cosine similarity \cref{eq:cosine} was chosen for its simplicity and the fact that it is bounded in the interval $[-1,1]$.
+\begin{equation}
+	\cos(x,  y) = \frac { x \cdot  y}{|| x|| \cdot || y||}
+	\label{eq:cosine}
+\end{equation}
 This is much less computationally expensive as the previous two approaches which were complex distance metric between two sets of embeddings.
@@
 \subsection{Definition of Fitness and precision}
-Given some similarity metric and the real log as well as the model log a dissimilarity matrix can be built up.
-From here on we will assume that each row corresponds to a trace from the model log and each column corresponds to a trace from the real log, i.e.
-$a_{ij}$ is the dissimilarity of the $i$-th trace from the model log with the $j$-th trace of the real log.
-As such each column contains the dissimilarity of a trace in the real log with all traces from the model log, with the minimum of a column being the closest match in the model log.
-A trace that can be closely replayed by the model, i.e. one that has a close match to a trace produced from the model, is a well fitting one.
-As such the column minimum corresponds to a fitness metric of the trace and thus the mean of all column minima is a fitness metric between log and log.
-Conversely, each row contains all similarities between a trace in the model log and all traces in the real log.
-A precise model should not allow for more traces than observed in the real log, as such each model trace should have as close a match as possible in the real log for the model to be precise.
-As such the row minimum corresponds to a precision metric for the trace in the model log and thus the mean of all row minima is a precision metric between log and log.
 
@@
 To evaluate the suitability of the method three sets of experiments were performed. 
+\color{blue}
+All experiments utilized (the same) randomly generated process trees, that were constructed using the algorithms in the \emph{pm4py} library.
+Three size configurations described by minimum number, the mode and the maximum number of visible activities were chosen: 5-10-15, 10-20-30 and 15-30-45.
+Furthermore, four operator configurations were chosen described by the probability for randomly choosing each available operator.
+These were in no particular order: Sequence: $0.75$, Parallel $0.25$, secondly Sequence: $0.75$, Choice $0.25$, thirdly 1.
+Sequence: $0.5$, Parallel $0.25$, Choice $0.25$ and lastly $0.25$ for all (Sequence, Parallel, Choice and Loop) operators.
+Both of these configuration were combined to generate a grid of $12$ process trees, with the hope that these cover a sufficient range of different behaviour.
+\color{black}
+
 The first set of experiments focussed on the scalability of the approach, especially since more traditional approaches do not scale well.
@@
 The expectation is that any reasonable conformance metric should deteriorate the more noise is added to the log.
-\todo{Explain more how process trees were generated}
+
 The third and last set of experiments was designed to compare the performance of the proposed methods (WMD,ICT \& trace2vec) to existing established conformance metrics, namely alignments, behavioural fitness \cite{GMVB09} and ETC precision \cite{MuCa10}.

### 2021-12-13 paper.tex
WMD and ICT

@@
 Here the differences between the three techniques come into play.
-The first two, the Word Mover's Distance and Iterative Constrained Transfers, can directly utilize the distances between activities to determine a distance between two collections of activities.
+The first two, the Word Mover's Distance \cite{KSKW15} and Iterative Constrained Transfers, can directly utilize the distances between activities to determine a distance between two collections of activities.
 The last one, \emph{trace2vec}, further needs to train a trace embedding based on activity embeddings, and can then perform direct comparisons in the trace embedding space.
@@
 
+\color{blue}
+The Word Mover's Distance \cite{KSKW15} is a variant of the Earth Mover's Distance \cite{RTGu98} adapted for natural language processing.
+This family of metrics has proved itself to be quite robust as well as accurate in the past.
+The Earth Mover's distance measures the distance between two probability distributions.
+The informal interpretation of this is that there are two distributions, represented by piles of earth.
+The distance between two distributions can be interpreted as the amount of work that needs to be done to transform one into the other.
+Clearly the work and thus the distance between two distributions depends on both the amount of earth on each of the piles and on the distance between piles.
+Formally the EMD defines a distance metric for probability distributions over some vector space with a notion of distance.
+
+This can be formulated as linear program by formulating it as a min-cost-max-flow problem with two additional contraints.
+An outflow one stating, that from each source-pile no more can leave than actually present and an inflow constraint stating that now more can flow into each sink-pile no more can flow than being required.
+
+In the case of embeddings and natural language processing this metric has also become known as the Word Mover's Distance.
+Here the word embeddings represent the piles, i.e.
+the distance between two word embeddings represents the "work" needed to transform one into the other, whereas collections of words, or more specifically their embeddings, such as sentences or even documents represent the probability distributions.
+
+It should also be noted that the WMD does not take word order into account, which is reasonable for e.g.
+semantic classification of documents, but seems much more important in the case of business processes, where it at leat intuitively seems to be important to avoid classifying $\langle a,b,c\rangle$ as being zero distance from a trace like $\langle c,b,a \rangle$.
 \todo{Use pseudocode from paper?}
-\todo{Describe both WMD and ICT in separate sections, or just mention that ICT gives a relaxed formulation of WMD that can be easier to compute}
 
+\subsubsection{Iterative Constrained Transfers}
+The EMD and variants of it are very attractive since they are both very general and exhibit good accuracy for both search and classification.
+A major drawback of such methods however is the cubic complexity in the size of the input distributions, which makes it infeasible for larger problems.
+In the case of conformance checking the size of the input distribution is determined by the number of activities in the log, for which good scalability is desired.
+There are a number of techniques that aim to reduce the complexity of EMD-based approaches, that obtain an approximation of the EMD by relaxing some of the constraints.  
+One example of such methods is the Relaxed Word Mover's distance which drops the second (inflow) constraint, thus greatly simplifying the solution.
+While this makes it easier to calculate the solution, the RWMD only gives an lower bound on the WMD.
+Another such methods is the Iterative Constrained Transfers \cite{AtMi18} algorithm that has linear complexity in the size of the input distribution.
+Instead of just dropping the inflow constraint it is instead replaced by an edge capacity constraint.
+The main benefit of this is that it avoid the formulation as a linear program and is instead solvable using a much less powerful, but much quicker, direct algorithm.
+
+Furthermore there is also an approximation to the ICT called Approximate Computation of ICT (ACT), by limiting the number of iterations in said direct algorithm.
+ICT and ACT agree in the limit, however if the number of occuring activities is relatively low, even small numbers of iterations lead to sufficient results.
+Only if there are some activities that occur significantly more often than other it is necessary to perform more iterations.
+
+The ICT and ACT again provide a lower bound to the WMD, since it is not guaranteed that the inflow constraint is met, however the ICT/ACT lower bound is higher than the RWMD lower bound due to the additional constraint that was introduced.
+\todo{Pseudocode?}
+\color{black}
 \subsection{trace2vec}

### 2021-12-13 paper.tex
Some more part extended + grammar

@@
 \usepackage{cleveref}
+\usepackage{caption}
+\usepackage{subcaption}
 % Used for displaying a sample figure. If possible, figure files should
@@
 \begin{abstract}
-	In the last decade there has been growing interest, both scientific and non-scientific, in the field of process mining.
-	While the main focus has been on business processes, the methods developed in the field of process mining are in now way limited to that area.
+	In the last decade, there has been growing interest, both scientific and non-scientific, in the field of process mining.
+	While the main focus has been on business processes, the methods developed in the field of process mining are in no way limited to that area.
 	One other area which lends itself to process mining is the growing Internet of Things.
@@
 
-Due to growing compute capabilities, as well as further digitalization allowed for more process data to be gathered and analysed.
-The increase in compute and storage capabilities, as well as the growing digitalization of many parts of our lives has created the distinct field of data science, as an amalgamation of Statistics, technical knowledge and domain knowledge.
+Due to growing compute capabilities, as well as further digitalization allowed for more process data to be gathered and analyzed.
+The increase in compute and storage capabilities, as well as the growing digitalization of many parts of our lives, has created the distinct field of data science, as an amalgamation of Statistics, technical knowledge, and domain knowledge.
 
 One benefactor of this development has been the subfield of process science, which is concerned with the analysis of processes.
-The combination of process science and data science gave rise to techniques generally grouped under the term process mining\footnote{Please note that due to the relative young age of the field, the fact that it lies at the intersection of two different fields and the fact that there is a marketing interest for these topics the terminology is not always settled and different authors and/or groups may differ in usage.
+The combination of process science and data science gave rise to techniques generally grouped under the term process mining\footnote{Please note that due to the relatively young age of the field, the fact that it lies at the intersection of two different fields and the fact that there is a marketing interest for these topics the terminology is not always settled and different authors and/or groups may differ in usage.
 The terminology used here is oriented around the definitions in \cite{Aals16}, as it seems to be the most polished overview of the field at the moment.}.
 Process mining is concerned with the automatic and algorithmic processing of event data.
-In its easiest form an event is a piece of data, that consists of a timestamp, an identifier to group events belonging to the same execution and a body containing further arbitrary values.
-In most cases there is also an identifier for the event type, with the purpose of identifying similar events in different executions of the process, e.g.
+In its easiest form, an event is a piece of data, that consists of a timestamp, an identifier to group events belonging to the same execution, and a body containing further arbitrary values.
+In most cases, there is also an identifier for the event type, with the purpose of identifying similar events in different executions of the process, e.g.
 to be able to group all "Send invoice" events as the same type.
@@
 There are a few reasons for that. 
-Namely, that there was already a well established field of non-algorithmic process science for business processes, which could act as a stepping stone.
-Secondly some of these processes were already highly digitized, many companies already had well established ERP systems from which data could be gathered with reasonable ease.
+Namely, that there was already a well-established field of non-algorithmic process science for business processes, which could act as a stepping stone.
+Secondly, some of these processes were already highly digitized, many companies already had well-established ERP systems from which data could be gathered with reasonable ease.
 Thirdly there was, and is, a large financial interest in optimizing such processes.
-And lastly business processes often struck the balance between too simple and too complicated, in that they exhibited enough variability to be interesting to analyse but were still simple enough as to enable the use of the early process mining algorithms.
+And lastly, business processes often struck the balance between too simple and too complicated, in that they exhibited enough variability to be interesting to analyze but were still simple enough as to enable the use of the early process mining algorithms.
 So it should be stated that while process mining is of great use for classical business processes, these are not the only areas for which it could potentially be useful.
 
-In the last two decades the cost for networking components has decreases significantly and a growing number of microcontrollers, embedded systems and electronic devices now have some form of networking ability.
+In the last two decades, the cost for networking components has decreased significantly and a growing number of microcontrollers, embedded systems, and electronic devices now have some form of networking ability.
 This increasing networked structure that enables easy information sharing between the members of the network has become known under a few names, most prominently as the "Internet of Things".
-Unfortunately due to shifting developments in the last two decades and marketing efforts associated with the Internet of Things it is hard to pin down the exact meaning of the term. 
+Unfortunately due to shifting developments in the last two decades and marketing efforts associated with the Internet of Things, it is hard to pin down the exact meaning of the term. 
 The International Telecommunication Union gives the following succinct definition of the Internet of Things in their recommendation \cite{ITUT12} on the topic:
@@
 It should be noted that this definition is very broad and extends beyond the notion of the "Smart Home" that has become somewhat of a representative of the Internet of Things.
-The definition neither limits the scale (locally, nationally or even globally) nor the range of use cases.
+The definition neither limits the scale (locally, nationally, or even globally) nor the range of use cases.
 The rest of the paper will follow this definition since the object of interest here are fully digitized networked control systems and the information pooling and sharing those bring with it.
@@
 This is especially interesting in the case of automation in manufacturing\cite{JKM*20} for which the term Internet of Production has been coined, here the hope is that networked information sharing between controllers on a production line or factory floor could greatly enhance the production capabilities of not just single production lines but entire automated factories.
-Especially in the case of manufacturing there is a large financial interest in optimizing production efficiency for various reasons such as increasing speed, increasing productivity or reducing downtime.
+Especially in the case of manufacturing, there is a large financial interest in optimizing production efficiency for various reasons such as increasing speed, increasing productivity or reducing downtime.
 
@@
 Yet as the field matures the capabilities of algorithms and accordingly the difficulty of interesting problems grows.
-As such there is research demand \cite{JKM*20} for different -- to test whether algorithms perform equally well in other scenarios --, larger -- to improve scalability of algorithms -- and more complex -- to test and improve the capacity to deal with more interwoven processes -- problems.
-At the same time only areas with a high level of digitalization can realistically be considered here since it is of paramount priority to be able to properly obtain the event data of any process in question.
-This has been a problem in the past when considering any process for which event data has to be manually entered, since in all these cases there will be discrepancies between digitally recorded process and the real world execution.
-The Internet of Things fulfils all these categories, it is digital by design, so relatively few efforts have to be made to obtain large amount of well-enough structured event data and the scale and complexity of the problem can scale up very well with growing network sizes.
+As such there is research demand \cite{JKM*20} for different -- to test whether algorithms perform equally well in other scenarios --, larger -- to improve the scalability of algorithms -- and more complex -- to test and improve the capacity to deal with more interwoven processes -- problems.
+At the same time, only areas with a high level of digitalization can realistically be considered here since it is of paramount priority to be able to properly obtain the event data of any process in question.
+This has been a problem in the past when considering any process for which event data has to be manually entered, since in all these cases there will be discrepancies between digitally recorded processes and their real-world execution.
+The Internet of Things fulfills all these categories, it is digital by design, so relatively few efforts have to be made to obtain a large amount of well-enough structured event data and the scale and complexity of the problem can scale up very well with growing network sizes.
 Furthermore, it is also possible to use techniques from the Internet of Things to further digitize classical processes and reduce dependencies on manual event recording.
 
-Naturally there are challenges to be overcome if one aims to integrate business process modelling into the Internet of Things.
-The first two major difference are attributable to the structure of the Internet of Things.
-Firstly the Internet of Things is made up numerous small devices all with limited compute capabilities.
+Naturally, there are challenges to be overcome if one aims to integrate business process modeling into the Internet of Things.
+The first two major differences are attributable to the structure of the Internet of Things.
+Firstly the Internet of Things is made up of numerous small devices all with limited compute capabilities.
 This limits the complexity of algorithms that can be performed on each of the devices and means that either a separate system with the role of performing analyses needs to be introduced or distributed algorithms need to be developed.
 Overall it should be noted that asynchronous decentralized networks are common for the Internet of Things, which needs to be taken into account when applying BPM.
-Secondly the Internet of Things has both the potential and demand for greater number of online analyses, i.e.
-in contrast to classical business processes it is much more important to evaluate a process during the execution, to give feedback and to possibly even influence a process during its execution.
+Secondly, the Internet of Things has both the potential and demand for greater number of online analyses, i.e.
+in contrast to classical business processes it is much more important to evaluate a process during the execution, to give feedback, and to possibly even influence a process during its execution.
 
@@
 From such information a number of useful analyses can follow, e.g. where do deviations happen, which resources are involved in deviations, and how exactly these traces deviate from the model.
-It should be pointed out that the word "deviation" is negatively connotated in English, however for the purpose of process intelligence it should be viewed as a neutral category. 
-For example an analysis may reveal that people often skip a step in the process, which actually improves the overall performance of the process, based on which refinements to the process model could be made.
+It should be pointed out that the word "deviation" is negatively connotated in English, however, for the purpose of process intelligence it should be viewed as a neutral category. 
+For example, an analysis may reveal that people often skip a step in the process, which actually improves the overall performance of the process, based on which refinements to the process model could be made.
 An example of negative conclusions may be the detections of deviations that do not follow proper legal or procedural requirements of the process, such as requiring two different persons to review an important document before signing off on it.
@@
 
-In the second case the log is seen as normative and the model considered either imperfect or unknown.
+In the second case, the log is seen as normative and the model is considered either imperfect or unknown.
 The most important representative application of this perspective is process discovery, or more specifically the evaluation of discovery algorithms.
-In the case of process discovery a process model has to be constructed from an event log.
-Obviously not all process models are able to describe a process equally good.
+In the case of process discovery, a process model has to be constructed from an event log.
+Obviously, not all process models are able to describe a process equally well.
 So when developing or using a process discovery algorithm the question of how well the discovered process models describe the log often arises.
@@
 \subsubsection{Quality criteria}
-It is important to note that model quality is not a single dimensional criterion, instead it exists in a multi-dimensional space where the different axes represent different quality criteria.
-As such it is not really appropriate to talk about one conformance metric, but instead the four major axes should be considered.
+It is important to note that model quality is not a single-dimensional criterion, instead, it exists in a multi-dimensional space where the different axes represent different quality criteria.
+As such it is not really appropriate to talk about one conformance metric, but instead, the four major axes should be considered.
 1.
@@
 However, that would not be a model that generalizes well since it captures none of the dynamism of the underlying process.
-This is the most difficult criterion, since it is arguing about unknown possible future behaviour.
+This is the most difficult criterion, since it is arguing about unknown possible future behavior.
 
-Of these four quality criteria conformance checking is mainly concerned precision and recall, but depending on the algorithms possibly some statements about generalization could be made as well.
+Of these four quality criteria conformance checking is mainly concerned with precision and recall, but depending on the algorithms possibly some statements about generalization could be made as well.
 
-\subsubsection{Token based Replay}
+\subsubsection{Token-based Replay}
 
-The easiest conformance checking method, both conceptually and algorithmically is probably Token based replay.
-The intuition behind token based replay is to replay an observed trace on a process model, specifically a Petri net, and to determine where problems occur.
+The easiest conformance checking method, both conceptually and algorithmically is probably Token-based replay.
+The intuition behind token-based replay is to replay an observed trace on a process model, specifically a Petri net, and to determine where problems occur.
 
@@
 However since we are dealing with possibly non-conformant trace, it is possible that a trace contains activities, that are not enabled in the model at that point in time.
-In this case a missing token is added to all input places, that did not contain a token, and the $m$ counter is incremented by the according amount.
+In this case, a missing token is added to all input places, that did not contain a token, and the $m$ counter is incremented by the according amount.
 Conversely, it might also happen, that a trace can be replayed, but that there are stray tokens left in the Petri net after the replay. 
-At the end of the replay the sum of all leftover tokens makes up the $r$ counter. \todo{Some explanation models could be included if the space is there for them}
+At the end of the replay, the sum of all leftover tokens makes up the $r$ counter. \todo{Some explanation models could be included if the space is there for them}
 Both missing and remaining tokens signal deviation from the process model, but both of these numbers are dependent on the length of traces.
 The longer a trace is the more activities will be taken, the more tokens will be produced, and the more chances there are for tokens to be missing or remaining.
-Importantly a trace where half the produced tokens were never consumed, i.e. remained, should intuitively have a lower fitness than one where only a quarter of produced tokens remained.
-Of course the same relationship holds for the other two counters $m$ and $c$.
+Importantly a trace where half the produced tokens were never consumed, i.e. remained, should intuitively have lower fitness than one where only a quarter of produced tokens remained.
+Of course, the same relationship holds for the other two counters $m$ and $c$.
 Then one very naturally arrives at a trace fitness defined as:
@@
 
-Token based methods are generally easy to implement and efficient algorithms are known, however they are not without problems.
+Token-based methods are generally easy to implement and efficient algorithms are known, however, they are not without problems.
 The first is the phenomenon known as "token flooding".
-Since token based methods create missing tokens to enable observed transitions in the log and remaining tokens are not removed, as more missing tokens are added during the simulation of a trace the  amount of stray tokens in the net also grows.
-This overabundance of tokens in the net can then lead to situations were many more transitions are enabled than should be, and later deviations are not detected by token based replay, since they are masked by earlier deviations.
-Also, token based diagnostics are  by their nature place-based diagnostics, they can determine whether a place was missing a token for the execution of a trace, but they cannot determine why said place was missing a token.
+Since token-based methods create missing tokens to enable observed transitions in the log and remaining tokens are not removed, as more missing tokens are added during the simulation of a trace the  amount of stray tokens in the net also grows.
+This overabundance of tokens in the net can then lead to situations where many more transitions are enabled than should be, and later deviations are not detected by token-based replay, since they are masked by earlier deviations.
+Also, token-based diagnostics are  by their nature place-based diagnostics, they can determine whether a place was missing a token for the execution of a trace, but they cannot determine why said place was missing a token.
 Yet in conformance checking it is often the latter rather than the former question for which answers are desired.
@@
 
-The second popular method for conformance checking are alignment based methods.
+The second group of popular methods for conformance checking are alignment-based methods.
 The goal here is to construct an execution on the model that is as "close" as possible to the observed execution of events in the trace/log.
 If a trace is conformant with the model, this is trivially easy, the "closest" execution possible in the model is exactly the observed trace.
-In the conformant case all moves are so called, synchronous moves, where both the log and the model performed the same event at each step.
-However, if a trace is non-conformant, which is of course the case that is of interest, then a one-to-one mapping between model and trace is not possible.
-To describe that so-called non-synchronous moves are introduced, these describe the case that one of  the model or log perform an activity that does not happen in the other one.
-This can be either a move-on-model-only, where the model takes some transition, which was not observed in the log, or its dual, the move-on-log-only where an event is recorded in the log that is not possible according to the model.
+In the conformant case, all moves are so-called, synchronous moves, where both the log and the model performed the same event at each step.
+However, if a trace is non-conformant, which is, of course, the case that is of interest, then a one-to-one mapping between model and trace is not possible.
+To describe that so-called non-synchronous moves are introduced, these describe the case that one of  the model or log performs an activity that does not happen in the other one.
+This can be either a move-on-model-only, where the model takes some transition, which was not observed in the log, or it's dual, the move-on-log-only where an event is recorded in the log that is not possible according to the model.
 The weighted sum of misalignments can then be used as a cost metric for an alignment. 
 The goal is then to construct an optimal alignment between a trace and the model.
-It should be obvious that there are infinitely many such alignments, however we can construct a trace-agnostic alignment, which consists of $n$ moves-on-log-only followed by the shortest path through the model as moves-on-model-only.
+It should be obvious that there are infinitely many such alignments, however, we can construct a trace-agnostic alignment, which consists of $n$ moves-on-log-only followed by the shortest path through the model as moves-on-model-only.
 This means there is an effective upper limit on the length of alignments that need to be considered, which in turn means that the problem is decidable. 
@@
 
-Alignments overcome many of the problems encountered in token based approaches: 
-They do not suffer from problems like token flooding, and they give transitions based diagnostics, which in the case of process mining is far more useful since transitions encode recorded or recordable activities.
-As such in alignments it is much easier to tell if a certain activity was skipped in a trace without performing further refinements of the diagnostics.
-These benefits do not come without drawbacks though, the main caveat of alignment based methods is that it boils down to a complex search in the alignment space, which is far more demanding than a replay based method.
+Alignments overcome many of the problems encountered in token-based approaches: 
+They do not suffer from problems like token flooding, and they give transition-based diagnostics, which in the case of process mining is far more useful since transitions encode recorded or recordable activities.
+As such in alignments, it is much easier to tell if a certain activity was skipped in a trace without performing further refinements of the diagnostics.
+These benefits do not come without drawbacks though, the main caveat of alignment-based methods is that it boils down to a complex search in the alignment space, which is far more demanding than a replay-based method.
 As such much research interest has been devoted to the development of heuristics that exploit certain  structures in event logs and/or process models to boost the performance of this search.
@@
 Embeddings are a popular machine learning approach that has been used for a variety of tasks with the most successful applications being in the fields of natural language processing and computer vision.
-The fundamental idea of embeddings is to train some form of embedding function that embeds complex objects, such as words or documents in the case of NLP or pictures and video sequences in the case of computer vision in a vectors space\footnote{To be more precise: a Hilbert space, since well-defined notions of distances and angles are necessary and for that a scalar product  is needed.}.
+The fundamental idea of embeddings is to train some form of embedding function that embeds complex objects, such as words or documents in the case of NLP or pictures and video sequences in the case of computer vision in a vectors space\footnote{To be more precise: a Hilbert space, since well-defined notions of distances and angles, are necessary and for that, a scalar product  is needed.}.
 Such an embedding function then enables a proper mathematical treatment of these non-vector objects as vectors, which allows for the application of a broad range of algorithms.
@@
 While this is the fundamental question to be answered, this comparison between two different types of objects greatly complicates the task.
-However, by re-framing the problem on can greatly simplify it.
+However, by re-framing the problem one can greatly simplify it.
 Instead of formulating the problem in terms of model-to-log comparison, one can formulate it as a comparison problem of a real log to a model log.
@@
 Then the whole problem is reframed as log-to-log comparisons, i.e. determining similarities between objects of the same type, for which a broad range of techniques already exist.
-This has the additional advantage that it is model-independent, since no limitations apart from the ability to generate traces are put on the type of model.
+This has the additional advantage that it is model-independent since no limitations apart from the ability to generate traces are put on the type of model.
 \begin{figure}
 	\includegraphics[width=1\textwidth]{figures/structure}
-	\caption{General structure of the approach}
+	\caption{The general structure of the approach}
 	\label{fig:structure}
@@
 Three different techniques were outlined in the paper, all following a similar structure outlined in \cref{fig:structure}.
-First a model log is produced from the model by using an appropriate replay semantics for the model.
+First, a model log is produced from the model by using appropriate replay semantics for the model.
 Then, given these two logs, one real and one produced by replaying the model, it is possible to train the \emph{act2vec}\cite{KBWe18} embedding.
-Based on these embeddings a dissimilarity function needs to be defined to compare different traces, however the \emph{act2vec} embedding only yields distance measurements between activities and not between traces.
+Based on these embeddings a dissimilarity function needs to be defined to compare different traces, however, the \emph{act2vec} embedding only yields distance measurements between activities and not between traces.
 Here the differences between the three techniques come into play.
@@
 As such each column contains the dissimilarity of a trace in the real log with all traces from the model log, with the minimum of a column being the closest match in the model log.
-A trace that can be closely replayed by the model, i.e. one that has a close match to a trace produced from the model, is a well fitting one.
+A trace that can be closely replayed by the model, i.e. one that has a close match to a trace produced from the model, is a well-fitting one.
 As such the column minimum corresponds to a fitness metric of the trace and thus the mean of all column minima is a fitness metric between log and log.
@@
 The first two methods utilize \emph{act2vec} to train activity embeddings.
-These activity embeddings then allows for the comparison of two traces by comparing their individual activities in the embedding space.
+These activity embeddings then allow for the comparison of two traces by comparing their individual activities in the embedding space.
 Then every trace constitutes a set of different activities that can be expressed in the embedding space.
-Every trace then describes a probability distribution over the activities contained in it, so given an appropriate distance metric for probability distributions such as the Earth Movers Distance it is possible to determine the distance (or conversely similarity) of two traces.
+Every trace then describes a probability distribution over the activities contained in it, so given an appropriate distance metric for probability distributions such as the Earth Movers Distance, it is possible to determine the distance (or conversely similarity) of two traces.
 
@@
 The distance between two distributions can be interpreted as the amount of work that needs to be done to transform one into the other.
-Clearly the work and thus the distance between two distributions depends on both the amount of earth on each of the piles and on the distance between piles.
+Clearly, the work and thus the distance between two distributions depends on both the amount of earth on each of the piles and on the distance between piles.
 Formally the EMD defines a distance metric for probability distributions over some vector space with a notion of distance.
 
-This can be formulated as linear program by formulating it as a min-cost-max-flow problem with two additional contraints.
+This can be formulated as a linear program by formulating it as a min-cost-max-flow problem with two additional constraints.
 An outflow one stating, that from each source-pile no more can leave than actually present and an inflow constraint stating that now more can flow into each sink-pile no more can flow than being required.
@@
 Here the word embeddings represent the piles, i.e.
-the distance between two word embeddings represents the "work" needed to transform one into the other, whereas collections of words, or more specifically their embeddings, such as sentences or even documents represent the probability distributions.
+the distance between two-word embeddings represents the "work" needed to transform one into the other, whereas collections of words, or more specifically their embeddings, such as sentences or even documents represent the probability distributions.
 
 It should also be noted that the WMD does not take word order into account, which is reasonable for e.g.
-semantic classification of documents, but seems much more important in the case of business processes, where it at leat intuitively seems to be important to avoid classifying $\langle a,b,c\rangle$ as being zero distance from a trace like $\langle c,b,a \rangle$.
+semantic classification of documents, but seems much more important in the case of business processes, where it at least intuitively seems to be important to avoid classifying $\langle a,b,c\rangle$ as being zero distance from a trace like $\langle c,b,a \rangle$.
 \todo{Use pseudocode from paper?}
@@
 A major drawback of such methods however is the cubic complexity in the size of the input distributions, which makes it infeasible for larger problems.
-In the case of conformance checking the size of the input distribution is determined by the number of activities in the log, for which good scalability is desired.
+In the case of conformance checking the size of the input, distribution is determined by the number of activities in the log, for which good scalability is desired.
 There are a number of techniques that aim to reduce the complexity of EMD-based approaches, that obtain an approximation of the EMD by relaxing some of the constraints.  
-One example of such methods is the Relaxed Word Mover's distance which drops the second (inflow) constraint, thus greatly simplifying the solution.
-While this makes it easier to calculate the solution, the RWMD only gives an lower bound on the WMD.
-Another such methods is the Iterative Constrained Transfers \cite{AtMi18} algorithm that has linear complexity in the size of the input distribution.
+One example of such a method is the Relaxed Word Mover's distance which drops the second (inflow) constraint, thus greatly simplifying the solution.
+While this makes it easier to calculate the solution, the RWMD only gives a lower bound on the WMD.
+Another such method is the Iterative Constrained Transfers \cite{AtMi18} algorithm that has linear complexity in the size of the input distribution.
 Instead of just dropping the inflow constraint it is instead replaced by an edge capacity constraint.
-The main benefit of this is that it avoid the formulation as a linear program and is instead solvable using a much less powerful, but much quicker, direct algorithm.
+The main benefit of this is that it avoids the formulation as a linear program and is instead solvable using a much less powerful, but much quicker, direct algorithm.
 
-Furthermore there is also an approximation to the ICT called Approximate Computation of ICT (ACT), by limiting the number of iterations in said direct algorithm.
-ICT and ACT agree in the limit, however if the number of occuring activities is relatively low, even small numbers of iterations lead to sufficient results.
-Only if there are some activities that occur significantly more often than other it is necessary to perform more iterations.
+Furthermore, there is also an approximation to the ICT called Approximate Computation of ICT (ACT), by limiting the number of iterations in said direct algorithm.
+ICT and ACT agree in the limit, however, if the number of occurring activities is relatively low, even small numbers of iterations lead to sufficient results.
+Only if there are some activities that occur significantly more often than others it is necessary to perform more iterations.
 
-The ICT and ACT again provide a lower bound to the WMD, since it is not guaranteed that the inflow constraint is met, however the ICT/ACT lower bound is higher than the RWMD lower bound due to the additional constraint that was introduced.
+The ICT and ACT again provide a lower bound to the WMD, since it is not guaranteed that the inflow constraint is met, however, the ICT/ACT lower bound is higher than the RWMD lower bound due to the additional constraint that was introduced.
 \todo{Pseudocode?}
@@
 When using this method every trace is embedded into a vector space and any distance metric that is deemed appropriate can be chosen.
-In the paper the cosine similarity \cref{eq:cosine} was chosen for its simplicity and the fact that it is bounded in the interval $[-1,1]$.
+In the paper, the cosine similarity \cref{eq:cosine} was chosen for its simplicity and the fact that it is bounded in the interval $[-1,1]$.
 \begin{equation}
@@
 \end{equation}
-This is much less computationally expensive as the previous two approaches which were complex distance metric between two sets of embeddings.
+This is much less computationally expensive than the previous two approaches which were complex distance metrics between two sets of embeddings.
 
@@
 All experiments utilized (the same) randomly generated process trees, that were constructed using the algorithms in the \emph{pm4py} library.
-Three size configurations described by minimum number, the mode and the maximum number of visible activities were chosen: 5-10-15, 10-20-30 and 15-30-45.
+Three size configurations described by minimum number, the mode,l, and the maximum number of visible activities were chosen: 5-10-15, 10-20-30, and 15-30-45.
 Furthermore, four operator configurations were chosen described by the probability for randomly choosing each available operator.
@@
 Sequence: $0.5$, Parallel $0.25$, Choice $0.25$ and lastly $0.25$ for all (Sequence, Parallel, Choice and Loop) operators.
-Both of these configuration were combined to generate a grid of $12$ process trees, with the hope that these cover a sufficient range of different behaviour.
+Both of these configurations were combined to generate a grid of $12$ process trees, with the hope that these cover a sufficient range of different behavior.
 \color{black}
@@
 The second set of experiments aimed to determine whether the method responded as expected when providing noisy logs.
-These experiments were designed to verify the soundness of approach.
-This was done by generating logs from random process trees generated by pm4py, applying random noise on these logs and determining the conformance between the noiseless and noisy logs.
+These experiments were designed to verify the soundness of the approach.
+This was done by generating logs from random process trees generated by pm4py, applying random noise on these logs, and determining the conformance between the noiseless and noisy logs.
+\color{blue}
+Three different types of noise were used: replacing a random activity with another, swapping two random activities, and removing a random activity.
+Then  two noise experiments were performed.
+In the first experiment, the percentage of traces that noise was applied to was varied between $10\%$ and $50\%$, but each noise type was applied at most once to each trace.
+In the second experiment instead, the percentage of traces to which noise was applied was kept constant at $40\%$, but the number of activities to which noise was applied was varied.
+Furthermore, the second experiment only utilized the replacement noise function  omitting the other two.
+\color{black}
 The expectation is that any reasonable conformance metric should deteriorate the more noise is added to the log.
@@
 \end{figure}
-The first performed experiment aimed to asses the performance  of the three proposed methods.
+The first performed experiment aimed to assess the performance  of the three proposed methods.
 The experiments were run on an Intel Core i7-9850h, a mid-range consumer CPU.
-Experiments were run for all three methods for different sized logs and different sized dictionaries, in this case dictionary size is determined by the number of different activities in the log.
-All experiments were performed in python, however the Word Mover's distance was calculated using pyemd, a python wrapper to calculate the WMD/Emd with numpy efficiency.
+Experiments were run for all three methods for different sized logs and different sized dictionaries, in this case, dictionary size is determined by the number of different activities in the log.
+All experiments were performed in python, however, the Word Mover's distance was calculated using pyemd, a python wrapper to calculate the WMD/Emd with NumPy efficiency.
 As such when comparing ICT and WMD times the efficiency difference between python and C should be taken into account.
@@
 The resulting times are shown in \cref{fig:scalability}.
-Over all log sizes a similar pattern is observable, with WMD and ICT behaving somewhat similar and \emph{trace2vec} consistently outperforming the other two methods in all experiments.
-For small dictionary sizes  (~10) WMD does outperform ICT, however that is likely due to the aforementioned efficiency differences between the implementations.
+Overall log sizes a similar pattern is observable, with WMD and ICT behaving somewhat similar and \emph{trace2vec} consistently outperforming the other two methods in all experiments.
+For small dictionary sizes  (~10) WMD does outperform ICT, however, that is likely due to the aforementioned efficiency differences between the implementations.
 It is doubly notable that despite these efficiency differences ICT already starts to outperform WMD for dictionary sizes of 20, with the gap growing even larger for dictionaries of size 30, ICT is finished after roughly half the time WMD takes.
@@
 
-Lastly the \emph{trace2vec} methods substantially outperforms both the other methods, since only the cosine similarity, a simple mathematical formula needs to evaluated at run time.
+Lastly, the \emph{trace2vec} method substantially outperforms both the other methods, since only the cosine similarity, a simple mathematical formula needs to be evaluated at run time.
 This comes with the additional overhead of training trace embeddings, however according to the authors training that "does not take a long time" but they don't include statistics in that regard.
@@
 \subsection{Noise experiment}
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{figures/noise-first}
+		\caption{Average of first noise experiment (Varying trace percentage) Raw data can be found in \cite{PBWe20} Table 4}
+		\label{fig:noise-first}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{figures/noise-second}
+		\caption{Average of second noise experiment (Varying amount of noise applied to trace)}
+		\label{fig:noise-second}
+	\end{subfigure}
+\end{figure}
+The second experiment aimed to determine how the algorithms behaved when different amounts of noise were introduced on the logs.
+The expectation is that higher levels of noise further deteriorate fitness and precision, however since the used methods are somewhat involved and since it can be hard to exactly tell what a system is doing for a lot of learning-based methods, whether the algorithms are well-behaved or not should be verified.
+
+The first noise experiment in which the number of traces to which noise was applied was varied seems to confirm the expectation.
+In all the trees the distance smoothly increased with larger amounts of noise added, there were neither cases where the dissimilarity would go down again with more noise nor any significant unexpected patterns like stark jumps or plateauing around certain points.
+The average of all the values from the first noise experiment is shown in \cref{fig:noise-first}.
+Here it is also clearly visible that the dissimilarity gain seems to slow down the more noise is added, however, that is perfectly expected.
+
+The second noise experiment also seems to back up the soundness of the approach, where again the dissimilarity increased the more activities were replaced.
+The results from the second noise experiment can be seen in \cref{fig:noise-second}.
+
+It should be noted that for both experiments the absolute values for WMD and ICT are not comparable to \emph{trace2vec}, since these are on different scales.
 
@@
 
-The purpose of the last experiment was the comparison of the three proposed techniques to established conformance checking algorithms.
+The purpose of the last experiment was the comparison of the three proposed techniques to establish conformance checking algorithms.
 The results of this experiment can be found in \cite{PBWe20} Table 5.
@@
 This is worrying since one of the most basic requirements for a good conformance checking technique is not assigning perfect scores to models that are able to replay fewer or more traces than in the log.
-It is unclear whether that is due to the unoptimized nature of the methods, it could be the case that the methods are not sensitive enough, which could be fixed by varying the parameters, or due to the limited size of the model logs, which were limited to 1000 traces, which puts an upper limit on the amount of behaviour that the embeddings are able to observe.
+It is unclear whether that is due to the unoptimized nature of the methods, it could be the case that the methods are not sensitive enough, which could be fixed by varying the parameters, or due to the limited size of the model logs, which were limited to 1000 traces, which puts an upper limit on the amount of behavior that the embeddings are able to observe.
 
 Yet when models deteriorate there is a tendency for all measurements to move together.
-At the current point only a qualitative analysis for imperfect models is possible since the values determined by WMD, ICT and \emph{trace2vec} are not proper metrics since they do not fall into the $0,1$ range.
-As such it is hard to interpret what a non optimal value actually means, and as such the data does not allow for a quantitative comparison  at this point.
+At the current point, only a qualitative analysis for imperfect models is possible since the values determined by WMD, ICT and \emph{trace2vec} are not proper metrics since they do not fall into the $0,1$ range.
+As such it is hard to interpret what a non-optimal value actually means, and as such the data does not allow for a quantitative comparison  at this point.
 The results that were obtained however suggest that these methods could be a useful alternative to established techniques, and that further research into them is warranted.
@@
 
-Peeperkorn et al. obtained promising first results for a novel bedding based approach towards conformance checking.
+Peeperkorn et al. obtained promising first results for a novel embedding-based approach towards conformance checking.
 Yet as the focus was mainly on the introduction and development of a prototype for such an approach there are some natural limitations.
-Arguably the biggest limitation are the logs used for the experimental validation.
+Arguably the biggest limitation is the logs used for the experimental validation.
 All used logs were completely synthetic, generated from random process trees.
 It is unclear how well the 12 trees used for this resemble real processes and whether these tree configurations are sufficiently representative for the variation exhibited in real life trees\footnote{12 tree configurations were used, 3 sizes and 4 different probability distributions for operations, how strong these vary should be investigated}.
-As such it should be a priority to test the proposed methods on real logs, possibly popular benchmark cases and also to systematically broaden the parameters for random process tree generation to cover more different classes.
+As such it should be a priority to test the proposed methods on real logs, possibly popular benchmark cases, and also to systematically broaden the parameters for random process tree generation to cover more different classes.
 
@@
 Furthermore, the algorithms used have several parameters which were set as seemingly reasonable standard values.
-A thorough investigation into the effect of these parameters should follow, since it can not be known whether similar defaults should be used in conformance checking  as in classical NLP problems.
+A thorough investigation into the effect of these parameters should follow since it can not be known whether similar defaults should be used in conformance checking  as in classical NLP problems.
 Special attention should be placed on those cases for which the NLP techniques produced perfect values, whereas the others did not.
-The methods should be tested with completely perfect and completely imperfect models regarding fitness and precision, as well as nearly perfect and nearly imperfect models to verify that the methods are able to correctly classify both ends of model spectrum and not misclassify nearly optimal models as perfect.
+The methods should be tested with completely perfect and completely imperfect models regarding fitness and precision, as well as nearly perfect and nearly imperfect models to verify that the methods are able to correctly classify both ends of the model spectrum and not misclassify nearly optimal models as perfect.
 \color{black}
@@
 
-Lastly the paper should be understood as a first stepping stone for the use of NLP-related algorithms for the task of conformance checking.
+Lastly, the paper should be understood as a first stepping stone for the use of NLP-related algorithms for the task of conformance checking.
 The use of embeddings is often a first step in such approaches, but it is entirely possible that more advanced NLP algorithms may give even better results.
 As such further research into the applicability of a variety of other methods could be fruitful.
-The authors especially mention $n$-grams, Embeddings from Language Models, Global Vectors for Word Representation and recurrent neural networks.
+The authors especially mention $n$-grams, Embeddings from Language Models, Global Vectors for Word Representation, and recurrent neural networks.
 

### 2021-12-15 paper.tex
Added algorithms

@@
-% !TeX spellcheck = en_GB
+% !TeX spellcheck = en_US
 % This is samplepaper.tex, a sample chapter demonstrating the
@@
 \usepackage{subcaption}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 % Used for displaying a sample figure. If possible, figure files should
@@
 The International Telecommunication Union gives the following succinct definition of the Internet of Things in their recommendation \cite{ITUT12} on the topic:
-\blockquote{[The Internet of Things is] A  global  infrastructure  for  the  information  society,  enabling  advanced  services  by  interconnecting  (physical  and  virtual)  things  based  on  existing  and  evolving  interoperable information and communication technologies.}
+\blockquote{[The Internet of Things is] A  global  infrastructure  for  the  information  society,  enabling  advanced  services  by  interconnecting  (physical  and  virtual)  things  based  on  existing  and  evolving  inter-operable information and communication technologies.}
 
@@
 
+\color{green}
+The following paper is structured as follows.
+First some background and important concepts for the rest of the paper are introduced n \cref{sec:background}.
+This includes a deeper look the conformance checking problem, which is given in \cref{sub:conformance}, including a description of the two established families of techniques.
+Furthermore the important limitations of these two approaches are highlighted.
+Then a brief overview over the required NLP techniques is given in \cref{sub:nlp}.
+Provided with the basic knowledge concerning both conformance checking and NLP, the novel embedding based conformance checking approaches from \cite{PBWe20} are described in \cref{sec:method}.
+After the techniques have been outlined a discussion of the results from their experiments follows in \cref{sec:results}.
+\cref{sec:discussion} concludes the paper with a consideration of limitations in their approach and possible future work, as well as a discussion of the applicability of these techniques in the Internet of Things.
+\color{black}
+
 \section{Background}
+\label{sec:background}
+\color{green}
+Naturally there are numerous sub problems to be solved in business process management.
+Often each problem can be viewed as a building block in a bigger system, and good solutions to one problem can enable more insightful further analyses in dependent problems.
+For example the first step in many business process management use cases will be the discovery of a process model.
+Once a process model has been obtained through some means further analyses can follow.
+One of these fields is conformance checking, which as a technique, closely follows discovery, since it's main goal is to quantify how well a model conforms to a log.
+There are currently two dominant branches of conformance checking, replay based algorithms and trace alignment algorithms.
+Peeperkorn et al.
+present a novel conformance checking technique that follows and alternate route \cite{PBWe20} to address the conformance checking problem, through techniques adapted from natural language processing.
+However, before this technique can be discussed in depth it is paramount to understand some of the basic ideas underlying both conformance checking and natural language processing. 
+\color{black}
+
 \subsection{Conformance Checking}
+\label{sub:conformance}
 Conformance checking covers a range of different methods that aim to quantify how well an event log (or even just a single trace) and a process model fit together.
@@
 The aim of conformance checking is the formalization of this imprecise intuitive understanding of fitting together and the development of methods and algorithms that can accurately quantify precisely this intuition.
-
 \subsubsection{Uses}
@@
 For example, an analysis may reveal that people often skip a step in the process, which actually improves the overall performance of the process, based on which refinements to the process model could be made.
-An example of negative conclusions may be the detections of deviations that do not follow proper legal or procedural requirements of the process, such as requiring two different persons to review an important document before signing off on it.
+An example of negative conclusions may be the detection of deviations that do not follow proper legal or procedural requirements of the process, such as requiring two different persons to review an important document before signing off on it.
 In such a case knowledge of these deviations is required to ensure proper execution of the process.
@@
 \subsection{Natural Language Processing}
-
+\label{sub:nlp}
 As laid out in the previous section, both classical branches of conformance checking exhibit major drawbacks.
@@
 \section{Method}
-
+\label{sec:method}
 Many conformance checking algorithms, notably the classical ones outlined above, aim to measure conformance between a log and a model.
@@
 Such a reformulation of the problem is possible since all (reasonably defined) models are able to generate sample traces, and can therefore produce a model log.
-Then the whole problem is reframed as log-to-log comparisons, i.e. determining similarities between objects of the same type, for which a broad range of techniques already exist.
+Then the whole problem is re-framed as log-to-log comparisons, i.e. determining similarities between objects of the same type, for which a broad range of techniques already exist.
 This has the additional advantage that it is model-independent since no limitations apart from the ability to generate traces are put on the type of model.
@@
 \color{blue}
+\begin{algorithm}
+	\caption{Word Mover's distance}\label{alg:wmd}
+	\begin{algorithmic}
+		\State $n:=$ vocabulary size
+		\State $p_i,q_i := $ normalized count of activity $i$ in $p$ or $q$ respectively
+		\State $c(i,j) :=$ Distance between embeddings of activity $i$ and $j$
+		\Function{$F_{WMD}$}{$p,q,c$}
+			\State distance $\gets$ $\min \sum_{i,j=1}^n T_{ij}c(i,j)$
+			\State subject to:
+			\State $\sum_{j=1}^{n}T_{ij}=p_i \forall i \in \{1,...,n\}$ \Comment{Outflow}
+			\State $\sum_{i=1}^{n}T_{ij}=q_j \forall j \in \{1,...,n\}$ \Comment{Inflow}
+			\Return distance
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
 The Word Mover's Distance \cite{KSKW15} is a variant of the Earth Mover's Distance \cite{RTGu98} adapted for natural language processing.
@@
 \subsubsection{Iterative Constrained Transfers}
+\begin{algorithm}
+	\caption{ACT}\label{alg:act}
+	\begin{algorithmic}
+		\State $k:=$ number of edges considered per activity
+		\State $p_i,q_i := $ normalized count of activity $i$ in $p$ or $q$ respectively
+		\State $c(i,j) :=$ Distance between embeddings of activity $i$ and $j$
+		\State $h_p,h_q :=$ amount of different activities in trace $p$ and trace $q$ 
+		\Function{$F_{ICT}$}{$p,q,c,k$}
+		\For{$i=1...h_p$}
+			\State $s \gets \arg \min_k(c(i,[1,...,h_q]))$ \Comment{Find $k$ activities with the smallest cost}
+			\While{$l < k$}
+				\State $r \gets \min(p_i,q_{s(l)}))$ \Comment{Edge constraint, move as much as possible but no more than allowed}
+				\State $p_i \gets p_i - r$ \Comment{Move weight}
+				\State $t \gets t + rc(i,j)$ \Comment{Update cost}
+				\State $l \gets l+1$
+			\EndWhile
+			\If{$p_i \neq 0$} \Comment{Move any remaining weight in $p_i$ to $q_{s(k)}$}
+				$t \gets t + p_ic(i,s(k))$ \Comment{Move rest to $q_{s(k)}$}
+			\EndIf
+		\EndFor
+		\Return $t$
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
 The EMD and variants of it are very attractive since they are both very general and exhibit good accuracy for both search and classification.
@@
 \section{Results}
-
+\label{sec:results}
 \subsection{Experimental setup}
@@
 \section{Discussion}
-
-\todo{Proper fitness metric}
-
+\label{sec:discussion}
+\subsection{Future Work}
 Peeperkorn et al. obtained promising first results for a novel embedding-based approach towards conformance checking.
@@
 Apart from that two of the metrics proposed -- WMD and ICT -- do not take the order of words/activities into account.
-This is due to the fact that for a lot of NLP problems order is of lesser importance and tasks like document keyword detection can treat a document as an orderless bag of words.
+This is due to the fact that for a lot of NLP problems order is of lesser importance and tasks like document keyword detection can treat a document as an order-less bag of words.
 At least from an intuitive understanding of conformance checking order of activities is integrally important, and it should at least be investigated if there are significant differences between ordered and orderless approaches with regard to conformance checking.
@@
 
+\color{green}
+\subsection{Internet of Things}
+An important question that was not yet properly addressed is whether this method offers benefits in the sue case of the internet of things and how well it would be adaptable to such an environment.
+\color{black}
 %

### 2021-12-15 paper.tex
Fixes

@@
 
-\color{green}
+\color{red}
 The following paper is structured as follows.
@@
 \label{sec:background}
-\color{green}
+\color{red}
 Naturally there are numerous sub problems to be solved in business process management.
@@
 			\State $\sum_{i=1}^{n}T_{ij}=q_j \forall j \in \{1,...,n\}$ \Comment{Inflow}
-			\Return distance
+			\State \Return distance
 		\EndFunction
@@
 			\If{$p_i \neq 0$} \Comment{Move any remaining weight in $p_i$ to $q_{s(k)}$}
-				$t \gets t + p_ic(i,s(k))$ \Comment{Move rest to $q_{s(k)}$}
+				\State $t \gets t + p_ic(i,s(k))$ \Comment{Move rest to $q_{s(k)}$}
 			\EndIf
 		\EndFor
-		\Return $t$
+		\State \Return $t$
 		\EndFunction

### 2021-12-15 paper.tex
Minor fixes

@@
 \usepackage{hyperref}
-\usepackage{cleveref}
+\usepackage[capitalise]{cleveref}
 \usepackage{caption}
@@
 The International Telecommunication Union gives the following succinct definition of the Internet of Things in their recommendation \cite{ITUT12} on the topic:
-\blockquote{[The Internet of Things is] A  global  infrastructure  for  the  information  society,  enabling  advanced  services  by  interconnecting  (physical  and  virtual)  things  based  on  existing  and  evolving  inter-operable information and communication technologies.}
+\blockquote{[The Internet of Things is] A  global  infrastructure  for  the  information  society,  enabling  advanced  services  by  interconnecting  (physical  and  virtual)  things  based  on  existing  and  evolving  interoperable information and communication technologies.}
 
@@
 The definition neither limits the scale (locally, nationally, or even globally) nor the range of use cases.
-The rest of the paper will follow this definition since the object of interest here are fully digitized networked control systems and the information pooling and sharing those bring with it.
+The rest of the paper will follow this definition since the objects of interest here are fully digitized networked control systems and the information pooling and sharing those bring with it.
 
-This vast infrastructure of small networked devices could prove to be fertile ground for process analysis.
+This vast infrastructure of small networked devices could prove to be fertile ground for process analysis \cite{JKM*20}.
 These controllers generally have some attached sensors to monitor and control the devices they are attached to and in combination with these produce an equally vast amount of events.
-This is especially interesting in the case of automation in manufacturing\cite{JKM*20} for which the term Internet of Production has been coined, here the hope is that networked information sharing between controllers on a production line or factory floor could greatly enhance the production capabilities of not just single production lines but entire automated factories.
+This is especially interesting in the case of automation in manufacturing, where networked information sharing between controllers on a production line or factory floor has the potential to greatly enhance the production capabilities of not just single production lines but entire automated factories.
 Especially in the case of manufacturing, there is a large financial interest in optimizing production efficiency for various reasons such as increasing speed, increasing productivity or reducing downtime.
@@
 At the same time, only areas with a high level of digitalization can realistically be considered here since it is of paramount priority to be able to properly obtain the event data of any process in question.
-This has been a problem in the past when considering any process for which event data has to be manually entered, since in all these cases there will be discrepancies between digitally recorded processes and their real-world execution.
+This has been a problem in the past when considering any process for which event data has to be manually entered since in all these cases there will be discrepancies between digitally recorded processes and their real-world execution.
 The Internet of Things fulfills all these categories, it is digital by design, so relatively few efforts have to be made to obtain a large amount of well-enough structured event data and the scale and complexity of the problem can scale up very well with growing network sizes.
@@
 Overall it should be noted that asynchronous decentralized networks are common for the Internet of Things, which needs to be taken into account when applying BPM.
-Secondly, the Internet of Things has both the potential and demand for greater number of online analyses, i.e.
+Secondly, the Internet of Things has both the potential and demand for a greater number of online analyses, i.e.
 in contrast to classical business processes it is much more important to evaluate a process during the execution, to give feedback, and to possibly even influence a process during its execution.
@@
 The following paper is structured as follows.
-First some background and important concepts for the rest of the paper are introduced n \cref{sec:background}.
-This includes a deeper look the conformance checking problem, which is given in \cref{sub:conformance}, including a description of the two established families of techniques.
-Furthermore the important limitations of these two approaches are highlighted.
-Then a brief overview over the required NLP techniques is given in \cref{sub:nlp}.
-Provided with the basic knowledge concerning both conformance checking and NLP, the novel embedding based conformance checking approaches from \cite{PBWe20} are described in \cref{sec:method}.
+First, some background and important concepts for the rest of the paper are introduced n \cref{sec:background}.
+This includes a deeper look at the conformance checking problem, which is given in \cref{sub:conformance}, including a description of the two established families of techniques.
+Furthermore, the important limitations of these two approaches are highlighted.
+Then a brief overview of the required NLP techniques is given in \cref{sub:nlp}.
+Provided with the basic knowledge concerning both conformance checking and NLP, the novel embedding-based conformance checking approaches from \cite{PBWe20} are described in \cref{sec:method}.
 After the techniques have been outlined a discussion of the results from their experiments follows in \cref{sec:results}.
@@
 \color{red}
-Naturally there are numerous sub problems to be solved in business process management.
-Often each problem can be viewed as a building block in a bigger system, and good solutions to one problem can enable more insightful further analyses in dependent problems.
-For example the first step in many business process management use cases will be the discovery of a process model.
+Naturally, there are numerous subproblems to be solved in business process management.
+Often each problem can be viewed as a building block in a bigger system, and good solutions to one problem can enable more insightful further analyses in subsequent problems.
+For example, the first step in many business process management use cases will be the discovery of a process model.
 Once a process model has been obtained through some means further analyses can follow.
-One of these fields is conformance checking, which as a technique, closely follows discovery, since it's main goal is to quantify how well a model conforms to a log.
-There are currently two dominant branches of conformance checking, replay based algorithms and trace alignment algorithms.
+One of these fields is conformance checking, which as a technique, closely follows discovery, since its main goal is to quantify how well a model conforms to a log.
+There are currently two dominant branches of conformance checking, replay-based algorithms, and trace alignment algorithms.
 Peeperkorn et al.
-present a novel conformance checking technique that follows and alternate route \cite{PBWe20} to address the conformance checking problem, through techniques adapted from natural language processing.
-However, before this technique can be discussed in depth it is paramount to understand some of the basic ideas underlying both conformance checking and natural language processing. 
+present a novel conformance checking technique that follows an alternate route \cite{PBWe20} to address the conformance checking problem, through techniques adapted from natural language processing.
+However, before this technique can be discussed in-depth it is paramount to understand some of the basic ideas underlying both conformance checking and natural language processing. 
 \color{black}
@@
 As such it is not really appropriate to talk about one conformance metric, but instead, the four major axes should be considered.
-1.
-Fitness (few false negatives): The first of these metrics is fitness.
+\begin{enumerate}
+	\item Fitness (few false negatives): The first of these metrics is fitness.
 This quality criterion is closely related to the statistical measure of recall.
 In the case of business process management fitness measures how many of the observed traces are actually possible executions of the model.
-2.
-Precision (few false positives): Closely related to the statistical measure of precision, this metric measures how many false positives there are in relation to true positives.
+	\item Precision (few false positives): Closely related to the statistical measure of precision, this metric measures how many false positives there are in relation to true positives.
 In the case of process models, this is the fraction of traces allowed by the model that are actually observed in the log.
-3. Simplicity: How "simple" a model is, generally a smaller model that describes a process equally well is preferred for reasons such as performance and comprehensibility .
-4. Generalization: Generalization is the model's ability to be applicable to possible future traces of a given process. 
+	\item Simplicity: How "simple" a model is, generally a smaller model that describes a process equally well is preferred for reasons such as performance and comprehensibility.
+	\item Generalization: Generalization is the model's ability to be applicable to possible future traces of a given process. 
 	It would clearly be possible to create a model with perfect precision and recall, by simply encoding the traces themselves in the model.
 However, that would not be a model that generalizes well since it captures none of the dynamism of the underlying process.
-This is the most difficult criterion, since it is arguing about unknown possible future behavior.
+	This is the most difficult criterion since it is arguing about unknown possible future behavior.
+\end{enumerate}
 
@@
 
-The easiest conformance checking method, both conceptually and algorithmically is probably Token-based replay.
+The easiest conformance checking method both conceptually and algorithmically is probably Token-based replay.
 The intuition behind token-based replay is to replay an observed trace on a process model, specifically a Petri net, and to determine where problems occur.
@@
 
-\subsection{Definition of Fitness and precision}
-
 \section{Results}
@@
 
-The third and last set of experiments was designed to compare the performance of the proposed methods (WMD,ICT \& trace2vec) to existing established conformance metrics, namely alignments, behavioural fitness \cite{GMVB09} and ETC precision \cite{MuCa10}.
+The third and last set of experiments was designed to compare the performance of the proposed methods (WMD,ICT \& trace2vec) to existing established conformance metrics, namely alignments, behavioral fitness \cite{GMVB09} and ETC precision \cite{MuCa10}.
 This was achieved by generating 1000 traces from a randomly generated process tree, which form the real log.
-Then a discovery algorithm was applied to this log to discover a model, here Alpha Miner, Inductive Miner infrequent (IMi) with noise levels 0 and 1 and the ILP Miner were selected as discovery algorithms.
+Then a discovery algorithm was applied to this log to discover a model, here Alpha Miner, Inductive Miner infrequent (IMi) with noise levels 0 and 1, and the ILP Miner were selected as discovery algorithms.
 Then fitness and precision between the discovered model and the real log were calculated using the previously mentioned algorithms as well as the method described in the paper.
@@
 As such it is hard to interpret what a non-optimal value actually means, and as such the data does not allow for a quantitative comparison  at this point.
-The results that were obtained however suggest that these methods could be a useful alternative to established techniques, and that further research into them is warranted.
+The results that were obtained however suggest that these methods could be a useful alternative to established techniques and that further research into them is warranted.
 
@@
 Lastly, the paper should be understood as a first stepping stone for the use of NLP-related algorithms for the task of conformance checking.
-The use of embeddings is often a first step in such approaches, but it is entirely possible that more advanced NLP algorithms may give even better results.
+The use of embeddings is often the first step in such approaches, but it is entirely possible that more advanced NLP algorithms may give even better results.
 As such further research into the applicability of a variety of other methods could be fruitful.
@@
 \subsection{Internet of Things}
-An important question that was not yet properly addressed is whether this method offers benefits in the sue case of the internet of things and how well it would be adaptable to such an environment.
+An important question that was not yet properly addressed is whether this method offers benefits in the use case of the internet of things and how well it would be adaptable to such an environment.
 \color{black}

### 2021-12-15 paper.tex
Last IoT section

@@
 \end{figure}
+\todo{maybe talk about scaling}
 The first performed experiment aimed to assess the performance  of the three proposed methods.
@@
 
-\color{green}
+\color{red}
 \subsection{Internet of Things}
 An important question that was not yet properly addressed is whether this method offers benefits in the use case of the internet of things and how well it would be adaptable to such an environment.
+The first important thing to note in that regard is performance.
+Sadly the authors did not include a performance measure for the baseline methods but it should be noted that there was one case where alignments did not produce a result in a reasonable time frame. 
+However, it is well known that alignments are a rather inefficient technique due to the inherent non-determinism and complex search structures needed to find an optimal alignment.
+As such it should be pointed out that any performance efficient technique that rivals alignments in expressive power, is desired in normal process mining, while being doubly important in any environment where computing power is much more limited and where data needs to be processed in real time.
+Furthermore, embeddings provide a way to move computations out of the conformance calculation into preliminary calculations, namely determining the embedding function.
+While the embeddings were trained separately and independently for each tree in the focus paper, a good embedding function for a process's activities and/or traces could theoretically be shared in an Internet of Things.
+This is attractive since it further decreases the amount of work needed to evaluate a dissimilarity, and, as can be seen at the \emph{trace2vec} case, generally exhibits much better scaling properties.
+Separating the conformance checking algorithm into a (more) efficient and well scaling evaluation part and a less efficient but shareable training part, could make such algorithms much more desirable in use-cases with many activities, long traces and/or high performance requirements.
 \color{black}

### 2021-12-17 paper.tex
Extenden IoT part

@@
 \subsection{Internet of Things}
+When analyzing such an approach in the context of the Internet of Things, there are three main facets that need to be considered.
+Due to the fact that the Internet of Things itself, as well as it's architectures, are very heterogeneous it will always be possible to find networks where one of the following limitations or requirements does not hold to some extent, however generally speaking the following should be the main considerations when trying to adapt a process management technique to the Internet of Things.
+First the Internet of Things is made up of many less powerful machines that generate a lot of data, and while it is of course possible to integrate more powerful computers into the internet of things, high performance, especially on limited hardware, is a major goal.
+The second consideration should be that the Internet of Things is very "online", in the sense that Events are constantly produced and thus analysis, such as conformance checking, during process execution is a high desired property of any technique.
+Lastly the Internet of Things is distributed, and as such certain features such as perfect connectivity, knowledge of all members of the network and others are much more relaxed.
+
+\subsubsection{Performance}
 An important question that was not yet properly addressed is whether this method offers benefits in the use case of the internet of things and how well it would be adaptable to such an environment.
@@
 This is attractive since it further decreases the amount of work needed to evaluate a dissimilarity, and, as can be seen at the \emph{trace2vec} case, generally exhibits much better scaling properties.
-Separating the conformance checking algorithm into a (more) efficient and well scaling evaluation part and a less efficient but shareable training part, could make such algorithms much more desirable in use-cases with many activities, long traces and/or high performance requirements.
+Separating the conformance checking algorithm into a (more) efficient and well scaling evaluation part and a less efficient but shareable training part, could make such algorithms much more desirable in use-cases with many activities, long traces and/or high performance requirements, such as real time evaluation.
+\subsubsection{Online/Streaming algorithms}
+An online conformance checking technique based on alignments is presented in \cite{ZBK*19}.
+Online conformance checking generally has two problems.
+Not underestimating the conformance of running traces, as running traces are missing events necessary for completion, while not overestimating the conformance of terminated traces, without explicit knowledge of termination.
+
+A naïve way to perform conformance checking analysis of the prefixes using the techniques outline above, is to simply add all prefixes of traces in the model log  to the model log.
+While this approach would give decent estimations for any incomplete traces such an approach runs into several problems.
+The first is that the explosion of the model log greatly increases the number of (dis)similarities that need to be calculated, which degrades performance.
+Secondly, as for all online conformance checking algorithms that don't assume explicit knowledge of termination, this will greatly overestimate the conformance of many non-fitting traces, especially since the fitness of a trace is a minimum of all distances between itself and model traces, it is very sensitive to the sudden inclusion of a lot of new model traces.
+Precision would be less affected by such a change since the percentage of incomplete traces in the real log is assumed to be relatively small.
+
+Overall it should be noted that online conformance checking is a difficult problem, but that there are certainly possibilities for solutions using the proposed techniques, especially considering their novelty there has been less research how they could be adapted in an online setting, and how such adaptions perform in reality.
+
+\subsubsection{Distributed}
 \color{black}

### 2021-12-17 paper.tex
Extended streaming

@@
 A naïve way to perform conformance checking analysis of the prefixes using the techniques outline above, is to simply add all prefixes of traces in the model log  to the model log.
+This approach essentially replicates the prefix-conformance technique presented in \cite{ZBK*19} for any model-log to real-log technique.
+The basic approach there was to relax one of the restrictions, namely that the end marking of an alignment had to be a final marking, to consider all traces who's end marking can reach the final marking, i.e.
+that there exists some remainder execution that completes the trace.
+Given a large enough sampling this is equivalent to enumerating all prefixes of the replay.
 While this approach would give decent estimations for any incomplete traces such an approach runs into several problems.
@@
 
+However more complicated techniques are also imaginable.
+Both WMD and ICT seem rather problematic approaches, when it comes to online conformance checking as both require normalization over activities, so even a prefect prefix like $\langle a,b\rangle$ of $\langle a,b,c\rangle$ would be encoded as $(0.5,0.5,0)$ and $(0.33,0.33,0.33)$ respectively.
+This means that through the modeling approach prefix relationships are already substantially degraded.
+It is possible that there are subset-like variants of the WMD, however I am not aware of any.
+
+The \emph{trace2vec} method could be more interesting, since it gives a framework to directly compare traces.
+If we look at any trace we would assume that the longer a prefix we take and determine the embedding of the more similar it is to the trace itself, i.e.
+it convergence in some sense to the embedding of the complete trace.
+An improvement on the naïve method above could be to just check all prefixes of the $k$ nearest neighbors to any trace.
+
 Overall it should be noted that online conformance checking is a difficult problem, but that there are certainly possibilities for solutions using the proposed techniques, especially considering their novelty there has been less research how they could be adapted in an online setting, and how such adaptions perform in reality.
+There are definitely parallels like word prediction systems for example, where such an approach could prove fruitful in both an online or offline setting.
 

### 2021-12-18 paper.tex
changes from 2nd preliminary feedback

@@
 \usepackage{algpseudocode}
+
+\MakeOuterQuote{"}
 % Used for displaying a sample figure. If possible, figure files should
@@
 
-\subsection{word2vec}
-
-\section{Method}
+\section{Embedding Based Conformance Checking}
 \label{sec:method}
@@
 First, a model log is produced from the model by using appropriate replay semantics for the model.
-Then, given these two logs, one real and one produced by replaying the model, it is possible to train the \emph{act2vec}\cite{KBWe18} embedding.
+Then, given these two logs, one real and one produced by replaying the model, it is possible to train the \emph{act2vec} \cite{KBWe18} embedding.
 Based on these embeddings a dissimilarity function needs to be defined to compare different traces, however, the \emph{act2vec} embedding only yields distance measurements between activities and not between traces.
@@
 $a_{ij}$ is the dissimilarity of the $i$-th trace from the model log with the $j$-th trace of the real log.
-As such each column contains the dissimilarity of a trace in the real log with all traces from the model log, with the minimum of a column being the closest match in the model log.
+As such, each column contains the dissimilarity of a trace in the real log with all traces from the model log, with the minimum of a column being the closest match in the model log.
 A trace that can be closely replayed by the model, i.e. one that has a close match to a trace produced from the model, is a well-fitting one.
@@
 Conversely, each row contains all similarities between a trace in the model log and all traces in the real log.
-A precise model should not allow for more traces than observed in the real log, as such each model trace should have as close a match as possible in the real log for the model to be precise.
-As such the row minimum corresponds to a precision metric for the trace in the model log and thus the mean of all row minima is a precision metric between log and log.
+A precise model should not allow for more traces than observed in the real log, so each model trace should have as close a match as possible in the real log for the model to be precise.
+As such the row minimum corresponds to a precision metric for the trace in the model log and thus the mean of all row minima is a precision metric between the logs.
 
@@
 These activity embeddings then allow for the comparison of two traces by comparing their individual activities in the embedding space.
-Then every trace constitutes a set of different activities that can be expressed in the embedding space.
-Every trace then describes a probability distribution over the activities contained in it, so given an appropriate distance metric for probability distributions such as the Earth Movers Distance, it is possible to determine the distance (or conversely similarity) of two traces.
+Every trace then constitutes a distribution over the embeddings of the activities contained in it, so given an appropriate distance metric for probability distributions such as the Earth Mover's Distance, it is possible to determine the distance (or conversely similarity) between two traces.
 
@@
 The Word Mover's Distance \cite{KSKW15} is a variant of the Earth Mover's Distance \cite{RTGu98} adapted for natural language processing.
-This family of metrics has proved itself to be quite robust as well as accurate in the past.
+This family of metrics has proved to be quite robust as well as accurate for a lot of embedding based NLP tasks.
+For this reason it was chosen as an initial candidate for the distance function of an embedding based conformance checking technique.
 The Earth Mover's distance measures the distance between two probability distributions.
@@
 This can be formulated as a linear program by formulating it as a min-cost-max-flow problem with two additional constraints. 
-An outflow one stating, that from each source-pile no more can leave than actually present and an inflow constraint stating that now more can flow into each sink-pile no more can flow than being required.
+%The outflow constraint stating, that from each source-vertex no more can leave than actually present and an inflow constraint stating that now more can flow into each sink-pile no more can flow than being required.
 
@@
 It should also be noted that the WMD does not take word order into account, which is reasonable for e.g.
-semantic classification of documents, but seems much more important in the case of business processes, where it at least intuitively seems to be important to avoid classifying $\langle a,b,c\rangle$ as being zero distance from a trace like $\langle c,b,a \rangle$.
-\todo{Use pseudocode from paper?}
+semantic classification of documents, but seems much more important in the case of business processes, where it seems intuitively important to avoid classifying $\langle a,b,c\rangle$ as being zero distance from a trace like $\langle c,b,a \rangle$.
 
@@
 The relationship between \emph{act2vec} and \emph{trace2vec} is analogous to the one between \emph{word2vec} and \emph{doc2vec}.
-When using this method every trace is embedded into a vector space and any distance metric that is deemed appropriate can be chosen.
+When using this method, every trace is embedded into a vector space and any distance metric that is deemed appropriate can be chosen.
 In the paper, the cosine similarity \cref{eq:cosine} was chosen for its simplicity and the fact that it is bounded in the interval $[-1,1]$.
@@
 
-\section{Results}
+\section{Experiments}
 \label{sec:results}
-\subsection{Experimental setup}
+To assess the performance of the three proposed embedding based techniques the authors designed and performed three experiments.
+These aimed to test and compare the scalability of the methods, whether noise deteriorates the results in an expected manner, and lastly to compare these techniques to established well researched conformance checking techniques.
 
-To evaluate the suitability of the method three sets of experiments were performed. 
+\subsection{Experimental Setup}
+
+%To evaluate the suitability of the method three sets of experiments were performed. 
 \color{blue}
 All experiments utilized (the same) randomly generated process trees, that were constructed using the algorithms in the \emph{pm4py} library.
-Three size configurations described by minimum number, the mode,l, and the maximum number of visible activities were chosen: 5-10-15, 10-20-30, and 15-30-45.
+Three size configurations described by minimum number, the model, and the maximum number of visible activities were chosen: 5-10-15, 10-20-30, and 15-30-45.
 Furthermore, four operator configurations were chosen described by the probability for randomly choosing each available operator.
@@
 
-The first set of experiments focussed on the scalability of the approach, especially since more traditional approaches do not scale well.
-This aspect is doubly important when talking about the Internet of Things, where computing resources are generally far more constrained, while still producing large amounts of event data.
+The first set of experiments focused on the scalability of the approach, especially since more traditional approaches do not scale well.
+This aspect is doubly important when talking about the Internet of Things, where the granularity of events is much easier controllable, which makes it possible to produce large amounts of event data with comparatively little effort.
+Due to this scalability is an important factor for the IoT, since it is desired to process these large amounts of data.
 
@@
 Three different types of noise were used: replacing a random activity with another, swapping two random activities, and removing a random activity.
-Then  two noise experiments were performed.
+Then,  two noise experiments were performed.
 In the first experiment, the percentage of traces that noise was applied to was varied between $10\%$ and $50\%$, but each noise type was applied at most once to each trace.
@@
 
-The third and last set of experiments was designed to compare the performance of the proposed methods (WMD,ICT \& trace2vec) to existing established conformance metrics, namely alignments, behavioral fitness \cite{GMVB09} and ETC precision \cite{MuCa10}.
-This was achieved by generating 1000 traces from a randomly generated process tree, which form the real log.
-Then a discovery algorithm was applied to this log to discover a model, here Alpha Miner, Inductive Miner infrequent (IMi) with noise levels 0 and 1, and the ILP Miner were selected as discovery algorithms.
+The third and last set of experiments was designed to compare the performance of the proposed methods (WMD, ICT \& trace2vec) to existing established conformance metrics, namely alignments, behavioral fitness \cite{GMVB09} and ETC precision \cite{MuCa10}.
+This was achieved by generating 1000 traces from a randomly generated process tree, to obtain an event log.
+Then, a discovery algorithm was applied to this log to discover a model.
+Here, Alpha Miner, Inductive Miner infrequent (IMi) with noise levels 0 and 1, and the ILP Miner were selected as discovery algorithms.
 Then fitness and precision between the discovered model and the real log were calculated using the previously mentioned algorithms as well as the method described in the paper.
@@
 \color{blue}
-\subsection{Scalability experiment}
+\subsection{Scalability Experiment}
 \begin{figure}
@@
 The experiments were run on an Intel Core i7-9850h, a mid-range consumer CPU.
-Experiments were run for all three methods for different sized logs and different sized dictionaries, in this case, dictionary size is determined by the number of different activities in the log.
-All experiments were performed in python, however, the Word Mover's distance was calculated using pyemd, a python wrapper to calculate the WMD/Emd with NumPy efficiency.
-As such when comparing ICT and WMD times the efficiency difference between python and C should be taken into account.
+Experiments were run for all three methods for different sized logs and different sized dictionaries, for embedding based conformance checking algorithms dictionary size is determined by the number of different activities in the log.
+All experiments were performed in Python, however, the Word Mover's distance was calculated using pyemd, a Python wrapper to calculate the WMD/EMD with NumPy efficiency.
+As such, when comparing ICT and WMD times, the efficiency difference between Python and C should be taken into account.
 
 The resulting times are shown in \cref{fig:scalability}.
-Overall log sizes a similar pattern is observable, with WMD and ICT behaving somewhat similar and \emph{trace2vec} consistently outperforming the other two methods in all experiments.
-For small dictionary sizes  (~10) WMD does outperform ICT, however, that is likely due to the aforementioned efficiency differences between the implementations.
-It is doubly notable that despite these efficiency differences ICT already starts to outperform WMD for dictionary sizes of 20, with the gap growing even larger for dictionaries of size 30, ICT is finished after roughly half the time WMD takes.
+Over all log sizes a similar pattern is observable, with WMD and ICT behaving similar and \emph{trace2vec} consistently outperforming the other two methods in all experiments.
+For small dictionary sizes  (10) WMD does outperform ICT, however, that is likely due to the aforementioned efficiency differences between the implementations.
+It is notable that despite these efficiency differences ICT already starts to outperform WMD for dictionary sizes of 20.
+For dictionaries of size 30 this gap grows even larger.
+Here ICT is finished after roughly half the time needed by the WMD approach.
 These experiments seem to suggest that ICT scales much better with larger dictionary sizes.
 Especially when considering that the current implementation is still unoptimized ICT could very well serve as a more efficient alternative to WMD, especially when working with complex logs.
-It should also be noted that the relative run time difference between both methods seems so slightly scale in the ICT's favor, starting out at $\frac{45}{75}=0.6$ for a log of size 500 and improving to $\frac{3824}{7032}\approx 0.54$ for logs of size 5000.
+It should also be noted that the relative run time difference between both methods slightly scale in the ICT's favor, starting out at $\frac{45}{75}=0.6$ for a log of size 500 and improving to $\frac{3824}{7032}\approx 0.54$ for logs of size 5000.
 
 Lastly, the \emph{trace2vec} method substantially outperforms both the other methods, since only the cosine similarity, a simple mathematical formula needs to be evaluated at run time.
-This comes with the additional overhead of training trace embeddings, however according to the authors training that "does not take a long time" but they don't include statistics in that regard.
+This comes with the additional overhead of training trace embeddings, however, according to the authors training that "does not take a long time" but they don't include statistics in that regard.
 The \emph{trace2vec} method has the additional benefit of not being dependent on the activities during run time, since traces are directly compared in the trace embedding space, which means that the size of the dictionary is irrelevant for this approach, making it even more attractive for processes with large numbers of activities than the ICT.
-\todo{Include log size scaling plot? Do I have the space for that? It is not really that interesting as far as I can tell}
 
@@
 The second experiment aimed to determine how the algorithms behaved when different amounts of noise were introduced on the logs.
-The expectation is that higher levels of noise further deteriorate fitness and precision, however since the used methods are somewhat involved and since it can be hard to exactly tell what a system is doing for a lot of learning-based methods, whether the algorithms are well-behaved or not should be verified.
+The expectation is that higher levels of noise further deteriorate fitness and precision. 
+However since the defined similarity notion is not very intuitive it is important to verify, whether the algorithms are well-behaved, i.e.
+if their results match up with the intuitive expectation we have for conformance.
+%However since the used methods are somewhat involved and since it can be hard to exactly tell what a system is doing for a lot of learning-based methods, whether the algorithms are well-behaved or not should be verified.
 
-The first noise experiment in which the number of traces to which noise was applied was varied seems to confirm the expectation.
-In all the trees the distance smoothly increased with larger amounts of noise added, there were neither cases where the dissimilarity would go down again with more noise nor any significant unexpected patterns like stark jumps or plateauing around certain points.
+The first noise experiment in which the number of noisy traces was varied seems to confirm the expectation.
+In all the trees, the distance smoothly increased with larger amounts of noise added, there were neither cases where the dissimilarity would go down again with more noise nor any significant unexpected patterns like jumps or plateauing around certain points.
 The average of all the values from the first noise experiment is shown in \cref{fig:noise-first}.
@@
 
-The second noise experiment also seems to back up the soundness of the approach, where again the dissimilarity increased the more activities were replaced.
+The second noise experiment also seems to back up the soundness of the approach, where again the dissimilarity increased, the more activities were replaced.
 The results from the second noise experiment can be seen in \cref{fig:noise-second}.
@@
 
-\subsection{Discovery experiment}
+\subsection{Discovery Experiment}
 
@@
 At the current point, only a qualitative analysis for imperfect models is possible since the values determined by WMD, ICT and \emph{trace2vec} are not proper metrics since they do not fall into the $0,1$ range.
-As such it is hard to interpret what a non-optimal value actually means, and as such the data does not allow for a quantitative comparison  at this point.
+As such it is hard to interpret what a non-optimal value actually means, and therefore the data does not allow for a quantitative comparison  at this point.
 The results that were obtained however suggest that these methods could be a useful alternative to established techniques and that further research into them is warranted.
@@
 Yet as the focus was mainly on the introduction and development of a prototype for such an approach there are some natural limitations.
-Arguably the biggest limitation is the logs used for the experimental validation.
+Arguably the biggest limitation were the logs used for the experimental validation.
 All used logs were completely synthetic, generated from random process trees.
@@
 
-Lastly, the paper should be understood as a first stepping stone for the use of NLP-related algorithms for the task of conformance checking.
-The use of embeddings is often the first step in such approaches, but it is entirely possible that more advanced NLP algorithms may give even better results.
+Lastly, the paper should be understood as a successful first use of NLP-related algorithms for the task of conformance checking.
+The use of embeddings is often the easiest method in such approaches, but it is entirely possible that more advanced NLP algorithms may give even better results.
 As such further research into the applicability of a variety of other methods could be fruitful.
-The authors especially mention $n$-grams, Embeddings from Language Models, Global Vectors for Word Representation, and recurrent neural networks.
+The authors especially mention $n$-grams, Embeddings from Language Models, Global Vectors for Word Representation, and Recurrent Neural Networks.
 

### 2021-12-19 paper.tex
First feedback

@@
 	%
-	\title{Conformance Checking Using Embeddings and their Applicability in the Internet of Things}
+	\title{Conformance Checking Using Embeddings and it's Applicability in the Internet of Things}
 	%
@@
 
-Due to growing compute capabilities, as well as further digitalization allowed for more process data to be gathered and analyzed.
-The increase in compute and storage capabilities, as well as the growing digitalization of many parts of our lives, has created the distinct field of data science, as an amalgamation of Statistics, technical knowledge, and domain knowledge.
+Growing compute capabilities, as well as further digitalization now allow for the gathering and analysis of vast amounts of data.
+The increase in compute and storage capabilities, as well as the growing digitalization of many parts of our lives, has created the distinct field of data science, as an amalgamation of statistics, technical knowledge, and domain knowledge.
 
 One benefactor of this development has been the subfield of process science, which is concerned with the analysis of processes.
-The combination of process science and data science gave rise to techniques generally grouped under the term process mining\footnote{Please note that due to the relatively young age of the field, the fact that it lies at the intersection of two different fields and the fact that there is a marketing interest for these topics the terminology is not always settled and different authors and/or groups may differ in usage.
+The combination of process science and data science gave rise to techniques generally grouped under the term process mining
+%\footnote{Please note that due to the relatively young age of the field, the fact that it lies at the intersection of two different fields and the fact that there is a marketing interest for these topics the terminology is not always settled and different authors and/or groups may differ in usage.
 The terminology used here is oriented around the definitions in \cite{Aals16}, as it seems to be the most polished overview of the field at the moment.}.
@@
 
-Historically most research in the topic of process mining has been on business processes. 
+Historically, most research in the topic of process mining has been on business processes. 
 There are a few reasons for that. 
@@
 Secondly, some of these processes were already highly digitized, many companies already had well-established ERP systems from which data could be gathered with reasonable ease.
-Thirdly there was, and is, a large financial interest in optimizing such processes.
+Thirdly, there was, and is, a large financial interest in optimizing such processes.
 And lastly, business processes often struck the balance between too simple and too complicated, in that they exhibited enough variability to be interesting to analyze but were still simple enough as to enable the use of the early process mining algorithms.
@@
 
-It should be noted that this definition is very broad and extends beyond the notion of the "Smart Home" that has become somewhat of a representative of the Internet of Things.
+It should be noted, that this definition is very broad and extends beyond the notion of the "Smart Home" that has become somewhat of a representative of the Internet of Things.
 The definition neither limits the scale (locally, nationally, or even globally) nor the range of use cases.
@@
 
-Naturally, there are challenges to be overcome if one aims to integrate business process modeling into the Internet of Things.
+Naturally, there are challenges to overcome if one aims to integrate business process modeling into the Internet of Things.
 The first two major differences are attributable to the structure of the Internet of Things.
@@
 Conversely, it might also happen, that a trace can be replayed, but that there are stray tokens left in the Petri net after the replay. 
-At the end of the replay, the sum of all leftover tokens makes up the $r$ counter. \todo{Some explanation models could be included if the space is there for them}
+At the end of the replay, the sum of all leftover tokens makes up the $r$ counter.
 Both missing and remaining tokens signal deviation from the process model, but both of these numbers are dependent on the length of traces.
@@
 \todo{formula}
-\todo{Possibly some examples}
 
@@
 \subsection{Embeddings}
-Embeddings are a popular machine learning approach that has been used for a variety of tasks with the most successful applications being in the fields of natural language processing and computer vision.
+Embedding based methods are popular machine learning approaches that have been used for a variety of tasks with the most successful applications being in the fields of natural language processing and computer vision.
 The fundamental idea of embeddings is to train some form of embedding function that embeds complex objects, such as words or documents in the case of NLP or pictures and video sequences in the case of computer vision in a vectors space\footnote{To be more precise: a Hilbert space, since well-defined notions of distances and angles, are necessary and for that, a scalar product  is needed.}.
@@
 While this is the fundamental question to be answered, this comparison between two different types of objects greatly complicates the task.
-However, by re-framing the problem one can greatly simplify it.
+However, by re-framing the problem it  can be greatly simplified.
 Instead of formulating the problem in terms of model-to-log comparison, one can formulate it as a comparison problem of a real log to a model log.
@@
 The ICT and ACT again provide a lower bound to the WMD, since it is not guaranteed that the inflow constraint is met, however, the ICT/ACT lower bound is higher than the RWMD lower bound due to the additional constraint that was introduced.
-\todo{Pseudocode?}
 \color{black}
@@
 	\includegraphics[width=1\textwidth]{figures/scaling}
-	\caption{Runtimes for all three methods for varying sizes of logs and dictionaries. Data can be found in \cite{MuCa10} Table 2}
+	\caption{Runtimes for all three methods for varying sizes of logs and dictionaries. Data can be found in \cite{MuCa10} Table 2.}
 	\label{fig:scalability}
 \end{figure}
-\todo{maybe talk about scaling}
 The first performed experiment aimed to assess the performance  of the three proposed methods.
@@
 
-The resulting times are shown in \cref{fig:scalability}.
+The resulting times are shown in \cref{fig:scalability}\footnote{Note that when two logs of size $n$ are compared, $n^2$ comparisons are needed.
+This is the reason why the needed time scales quadratically with log size}.
 Over all log sizes a similar pattern is observable, with WMD and ICT behaving similar and \emph{trace2vec} consistently outperforming the other two methods in all experiments.

### 2021-12-19 paper.tex
Integrated feedback

@@
 Thirdly, there was, and is, a large financial interest in optimizing such processes.
-And lastly, business processes often struck the balance between too simple and too complicated, in that they exhibited enough variability to be interesting to analyze but were still simple enough as to enable the use of the early process mining algorithms.
+And lastly, business processes often struck the balance between too simple and too complicated, in that they exhibited enough variability to be interesting to analyze but were still simple enough to enable the use of the early process mining algorithms.
 So it should be stated that while process mining is of great use for classical business processes, these are not the only areas for which it could potentially be useful.
@@
 According to the semantics of Petri nets, whenever a transition is fired it consumes one token from all input places and produces one token in each output place.
-However since we are dealing with possibly non-conformant trace, it is possible that a trace contains activities, that are not enabled in the model at that point in time.
+However since it is also possible that we are dealing with a non-conformant trace, it can be the case that a trace contains activities, that are not enabled in the model at that point in time.
 In this case, a missing token is added to all input places, that did not contain a token, and the $m$ counter is incremented by the according amount.
@@
 \color{blue}
-Three different techniques were outlined in the paper, all following a similar structure outlined in \cref{fig:structure}.
+Three different techniques were outlined in the focus paper \cite{PBWe20}, all following a similar structure outlined in \cref{fig:structure}.
 First, a model log is produced from the model by using appropriate replay semantics for the model.
@@
 Every trace then constitutes a distribution over the embeddings of the activities contained in it, so given an appropriate distance metric for probability distributions such as the Earth Mover's Distance, it is possible to determine the distance (or conversely similarity) between two traces.
+Note that many NLP algorithms use a so called bag of words approach, where the order of words is disregarded.
+Both the WMD and ICT take the same approach as a bag of words and treat a trace as a bag of activities.
 
@@
 \subsection{Experimental Setup}
-
+\begin{figure}
+	\includegraphics[width=1\textwidth]{figures/process-tree}
+	\caption{A process tree generated by pm4py using parameters: Min 15, Mode 30, Max 45, sequence 0.75, parallel 0.25. }
+	\label{fig:process-tree}
+\end{figure}
 %To evaluate the suitability of the method three sets of experiments were performed. 
@@
 Both of these configurations were combined to generate a grid of $12$ process trees, with the hope that these cover a sufficient range of different behavior.
+An example of such a random process tree is shown in \cref{fig:process-tree}
+\footnote{Note that this tree is not the one used by the authors since they did not share their trees or logs, but one generated with the same parameters.}.
 \color{black}
@@
 
-The resulting times are shown in \cref{fig:scalability}\footnote{Note that when two logs of size $n$ are compared, $n^2$ comparisons are needed.
-This is the reason why the needed time scales quadratically with log size}.
+The resulting times are shown in \cref{fig:scalability}
+\footnote{Note that when two logs of size $n$ are compared, $n^2$ comparisons are needed. This is the reason why the needed time scales quadratically with log size}.
 Over all log sizes a similar pattern is observable, with WMD and ICT behaving similar and \emph{trace2vec} consistently outperforming the other two methods in all experiments.
@@
 The average of all the values from the first noise experiment is shown in \cref{fig:noise-first}.
-Here it is also clearly visible that the dissimilarity gain seems to slow down the more noise is added, however, that is perfectly expected.
+Here it is also clearly visible that the dissimilarity gain slows down for larger levels of noise, however, that is perfectly expected.
 
-The second noise experiment also seems to back up the soundness of the approach, where again the dissimilarity increased, the more activities were replaced.
+The second noise experiment also seems to back up the soundness of the approach, where the dissimilarity again increased, the more activities were replaced.
 The results from the second noise experiment can be seen in \cref{fig:noise-second}.
@@
 This is due to the fact that for a lot of NLP problems order is of lesser importance and tasks like document keyword detection can treat a document as an order-less bag of words.
-At least from an intuitive understanding of conformance checking order of activities is integrally important, and it should at least be investigated if there are significant differences between ordered and orderless approaches with regard to conformance checking.
+At least from an intuitive understanding of conformance checking, the order of activities is integrally important, and it should at least be investigated if there are significant differences between ordered and orderless approaches with regard to conformance checking.
 The authors themselves suggest considering the use of $n$-grams instead of 1-grams, since their application seems more feasible in business processes as compared to classical NLP.
@@
 Furthermore, embeddings provide a way to move computations out of the conformance calculation into preliminary calculations, namely determining the embedding function.
-While the embeddings were trained separately and independently for each tree in the focus paper, a good embedding function for a process's activities and/or traces could theoretically be shared in an Internet of Things.
+While the embeddings were trained separately and independently for each tree in the focus paper, a good embedding function for a process's activities and/or traces could theoretically be shared in the Internet of Things.
 This is attractive since it further decreases the amount of work needed to evaluate a dissimilarity, and, as can be seen at the \emph{trace2vec} case, generally exhibits much better scaling properties.
@@
 This approach essentially replicates the prefix-conformance technique presented in \cite{ZBK*19} for any model-log to real-log technique.
-The basic approach there was to relax one of the restrictions, namely that the end marking of an alignment had to be a final marking, to consider all traces who's end marking can reach the final marking, i.e.
+The basic approach there was to relax one of the restrictions, namely that the end marking of an alignment had to be a final marking, to consider all traces whose end marking can reach the final marking, i.e.
 that there exists some remainder execution that completes the trace.
@@
 
-However more complicated techniques are also imaginable.
+However, more complicated techniques are also imaginable.
 Both WMD and ICT seem rather problematic approaches, when it comes to online conformance checking as both require normalization over activities, so even a prefect prefix like $\langle a,b\rangle$ of $\langle a,b,c\rangle$ would be encoded as $(0.5,0.5,0)$ and $(0.33,0.33,0.33)$ respectively.

### 2021-12-19 paper.tex
Discovery plot

@@
 \subsection{Discovery Experiment}
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{figures/fitness}
+		\caption{Fitness}
+		\label{fig:fitness}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{figures/precision}
+		\caption{Precision}
+		\label{fig:precision}
+	\end{subfigure}
+\caption{Fitness and Precision for different tree, discovery technique pairings for the three proposed techniques as well as the two verification techniques. 
+	Note that values are shown for WMD,ICT and \emph{trace2vec} are mirrored along x, since they are not proper metrics and larger values means worse fitness/precision. 
+	This way all results move in the same direction for better/worse values.
+Raw data can be found in \cite{PBWe20} Table 5.}
+\label{fig:discovery}
+\end{figure}
 
 The purpose of the last experiment was the comparison of the three proposed techniques to establish conformance checking algorithms.
-The results of this experiment can be found in \cite{PBWe20} Table 5.
-\todo{Include their data? Manually as table or maybe as plot. If so what kind plot would you suggest}
+The results of this experiment can be found in \cref{fig:discovery}.
 The results from the discovery experiment seem to suggest that all three methods are able to capture a notion of conformance.

### 2021-12-20 paper.tex
reproducibility

@@
 
-\subsubsection{Quality criteria}
-It is important to note that model quality is not a single-dimensional criterion, instead, it exists in a multi-dimensional space where the different axes represent different quality criteria.
-As such it is not really appropriate to talk about one conformance metric, but instead, the four major axes should be considered.
-\begin{enumerate}
-	\item Fitness (few false negatives): The first of these metrics is fitness.
+%\subsubsection{Quality criteria}
+%It is important to note that model quality is not a single-dimensional criterion, instead, it exists in a multi-dimensional space where the different axes represent different quality criteria.
+%As such it is not really appropriate to talk about one conformance metric, but instead, the four major axes should be considered.
+%\begin{enumerate}
+%	\item Fitness (few false negatives): The first of these metrics is fitness.
 This quality criterion is closely related to the statistical measure of recall.
 In the case of business process management fitness measures how many of the observed traces are actually possible executions of the model.
-	\item Precision (few false positives): Closely related to the statistical measure of precision, this metric measures how many false positives there are in relation to true positives.
+%	\item Precision (few false positives): Closely related to the statistical measure of precision, this metric measures how many false positives there are in relation to true positives.
 In the case of process models, this is the fraction of traces allowed by the model that are actually observed in the log.
-	\item Simplicity: How "simple" a model is, generally a smaller model that describes a process equally well is preferred for reasons such as performance and comprehensibility.
-	\item Generalization: Generalization is the model's ability to be applicable to possible future traces of a given process. 
-	It would clearly be possible to create a model with perfect precision and recall, by simply encoding the traces themselves in the model.
+%	\item Simplicity: How "simple" a model is, generally a smaller model that describes a process equally well is preferred for reasons such as performance and comprehensibility.
+%	\item Generalization: Generalization is the model's ability to be applicable to possible future traces of a given process. 
+%	It would clearly be possible to create a model with perfect precision and recall, by simply encoding the traces themselves in the model.
 However, that would not be a model that generalizes well since it captures none of the dynamism of the underlying process.
-	This is the most difficult criterion since it is arguing about unknown possible future behavior.
-\end{enumerate}
-
-Of these four quality criteria conformance checking is mainly concerned with precision and recall, but depending on the algorithms possibly some statements about generalization could be made as well.
+%	This is the most difficult criterion since it is arguing about unknown possible future behavior.
+%\end{enumerate}
+%
+%Of these four quality criteria conformance checking is mainly concerned with precision and recall, but depending on the algorithms possibly some statements about generalization could be made as well.
 
@@
 However, the search space can quickly grow infeasibly large, so heuristics need to be employed to determine optimal alignments in a reasonable time frame.
-
-\todo{formula}
 
@@
 
+\subsection{Reproduction of Experiments}
+The authors published some \href{https://github.com/jaripeeperkorn/Conformance-checking-using-activity-and-trace-embeddings}{source code} accompanying the paper.
+To verify their results as well possibly perform some additional experiments it seemed appropriate to look at said code and try to reproduce their results as good as possible.
+After some initial technical difficulties, since very specific package versions were needed, their code was successfully run.
+They provide three separate Python scripts for their implementations of the  WMD,ICT and \emph{trace2vec} methods.
+
+Aside from that they also provide Jupyter notebooks for their experiments, however sadly these do not run the whole experiment, instead they only perform the experiment for one parameter combination.
+To reproduce their noise experiment it is thus necessary to manually run the corresponding notebook twelve times, once for each parameter combination, manually note down the results of each run and merge them manually at the end.
+This was deemed to be out of scope for this paper.
+Additionally, the discovery experiment only determined fitness and precision of the WMD, ICT and \emph{trace2vec} methods and not the reference methods, so it is unclear at this point how the fitness and precision values for the reference methods were determined.
+Overall it can be said that the results from the paper are at least partially reproducible, and the provided implementation gives good pointer into how the methods were set up in detail, but running the experiments and collecting the results requires more effort than should be necessary.
+
+Lastly, it was considered to design and run another experiment here to evaluate performance and scaling differences between the embedding based approaches and reference approaches like alignments, behavioral fitness and ETC precision, as this is one of the main selling point especially in the IoT and the authors sadly did not include an experiment to that effect.
+In light of the complications with the existing experiments and the fact that no evaluation of the reference metrics was included in their code this idea was deemed out of scope for this paper.
 \color{black}

### 2021-12-20 paper.tex
Some final touches

@@
 
-\color{red}
 The following paper is structured as follows.
@@
 \cref{sec:discussion} concludes the paper with a consideration of limitations in their approach and possible future work, as well as a discussion of the applicability of these techniques in the Internet of Things.
-\color{black}
 
@@
 \label{sec:background}
-\color{red}
+
 Naturally, there are numerous subproblems to be solved in business process management.
@@
 However, before this technique can be discussed in-depth it is paramount to understand some of the basic ideas underlying both conformance checking and natural language processing.
-\color{black}
 
@@
 Both missing and remaining tokens signal deviation from the process model, but both of these numbers are dependent on the length of traces.
-The longer a trace is the more activities will be taken, the more tokens will be produced, and the more chances there are for tokens to be missing or remaining.
-Importantly a trace where half the produced tokens were never consumed, i.e. remained, should intuitively have lower fitness than one where only a quarter of produced tokens remained.
-Of course, the same relationship holds for the other two counters $m$ and $c$.
+%The longer a trace is the more activities will be taken, the more tokens will be produced, and the more chances there are for tokens to be missing or remaining.
+%Importantly a trace where half the produced tokens were never consumed, i.e. remained, should intuitively have lower fitness than one where only a quarter of produced tokens remained.
+%Of course, the same relationship holds for the other two counters $m$ and $c$.
 Then one very naturally arrives at a trace fitness defined as:
@@
 \end{equation}
-Note that log-fitness is not mathematically equivalent to the mean trace fitness.
+%Note that log-fitness is not mathematically equivalent to the mean trace fitness.
 
@@
 The goal here is to construct an execution on the model that is as "close" as possible to the observed execution of events in the trace/log.
-If a trace is conformant with the model, this is trivially easy, the "closest" execution possible in the model is exactly the observed trace.
 In the conformant case, all moves are so-called, synchronous moves, where both the log and the model performed the same event at each step.
-However, if a trace is non-conformant, which is, of course, the case that is of interest, then a one-to-one mapping between model and trace is not possible.
-To describe that so-called non-synchronous moves are introduced, these describe the case that one of  the model or log performs an activity that does not happen in the other one.
+%However, if a trace is non-conformant, which is, of course, the case that is of interest, then a one-to-one mapping between model and trace is not possible.
+In the non-conformant case so-called non-synchronous moves are introduced, these describe the case that one of  the model or log performs an activity that does not happen in the other one.
 This can be either a move-on-model-only, where the model takes some transition, which was not observed in the log, or it's dual, the move-on-log-only where an event is recorded in the log that is not possible according to the model.
@@
 The goal is then to construct an optimal alignment between a trace and the model.
-It should be obvious that there are infinitely many such alignments, however, we can construct a trace-agnostic alignment, which consists of $n$ moves-on-log-only followed by the shortest path through the model as moves-on-model-only.
-This means there is an effective upper limit on the length of alignments that need to be considered, which in turn means that the problem is decidable. 
-However, the search space can quickly grow infeasibly large, so heuristics need to be employed to determine optimal alignments in a reasonable time frame.
+%It should be obvious that there are infinitely many such alignments, however, we can construct a trace-agnostic alignment, which consists of $n$ moves-on-log-only followed by the shortest path through the model as moves-on-model-only.
+%This means there is an effective upper limit on the length of alignments that need to be considered, which in turn means that the problem is decidable. 
+%However, the search space can quickly grow infeasibly large, so heuristics need to be employed to determine optimal alignments in a reasonable time frame.
 
@@
 
-\color{blue}
 Three different techniques were outlined in the focus paper \cite{PBWe20}, all following a similar structure outlined in \cref{fig:structure}.
@@
 Using one of these metrics a dissimilarity matrix can be built up describing the pairwise dissimilarities between the real log and the model log.
-\color{black}
+
 From here on we will assume that each row corresponds to a trace from the model log and each column corresponds to a trace from the real log, i.e.
@@
 
-\color{blue}
 \begin{algorithm}
@@
 The ICT and ACT again provide a lower bound to the WMD, since it is not guaranteed that the inflow constraint is met, however, the ICT/ACT lower bound is higher than the RWMD lower bound due to the additional constraint that was introduced.
-\color{black}
+
 \subsection{trace2vec}
@@
 %To evaluate the suitability of the method three sets of experiments were performed.
-\color{blue}
+
 All experiments utilized (the same) randomly generated process trees, that were constructed using the algorithms in the \emph{pm4py} library.
@@
 \footnote{Note that this tree is not the one used by the authors since they did not share their trees or logs, but one generated with the same parameters.}.
-\color{black}
 
@@
 This was done by generating logs from random process trees generated by pm4py, applying random noise on these logs, and determining the conformance between the noiseless and noisy logs.
-\color{blue}
+
 Three different types of noise were used: replacing a random activity with another, swapping two random activities, and removing a random activity.
@@
 Furthermore, the second experiment only utilized the replacement noise function  omitting the other two.
-\color{black}
+
 The expectation is that any reasonable conformance metric should deteriorate the more noise is added to the log.
@@
 
-\color{blue}
 \subsection{Scalability Experiment}
@@
 In light of the complications with the existing experiments and the fact that no evaluation of the reference metrics was included in their code this idea was deemed out of scope for this paper.
-\color{black}
+
 \section{Discussion}
@@
 
-\color{blue}
 It is also a  prerequisite for further research and possible usage of such methods to convert the distance metrics obtained into proper conformance metrics, especially by restricting values to the interval $[0,1]$.
@@
 The methods should be tested with completely perfect and completely imperfect models regarding fitness and precision, as well as nearly perfect and nearly imperfect models to verify that the methods are able to correctly classify both ends of the model spectrum and not misclassify nearly optimal models as perfect.
-\color{black}
+
 Apart from that two of the metrics proposed -- WMD and ICT -- do not take the order of words/activities into account.
@@
 
-\color{red}
 \subsection{Internet of Things}
@@
 Due to the fact that the Internet of Things itself, as well as it's architectures, are very heterogeneous it will always be possible to find networks where one of the following limitations or requirements does not hold to some extent, however generally speaking the following should be the main considerations when trying to adapt a process management technique to the Internet of Things.
-First the Internet of Things is made up of many less powerful machines that generate a lot of data, and while it is of course possible to integrate more powerful computers into the internet of things, high performance, especially on limited hardware, is a major goal.
-The second consideration should be that the Internet of Things is very "online", in the sense that Events are constantly produced and thus analysis, such as conformance checking, during process execution is a high desired property of any technique.
-Lastly the Internet of Things is distributed, and as such certain features such as perfect connectivity, knowledge of all members of the network and others are much more relaxed.
+First the Internet of Things generates a lot of data, and the amount of potential data that can be generated is enormous.
+This means high performance, for things like real-time analysis, is a major goal.
+The second consideration should be that the Internet of Things is very "online", in the sense that events are constantly produced and thus analysis, such as conformance checking, during process execution is a highly desired property of any technique.
 
@@
 Overall it should be noted that online conformance checking is a difficult problem, but that there are certainly possibilities for solutions using the proposed techniques, especially considering their novelty there has been less research how they could be adapted in an online setting, and how such adaptions perform in reality.
-There are definitely parallels like word prediction systems for example, where such an approach could prove fruitful in both an online or offline setting.
+But even beyond that there are many potential interesting use cases for embedding based methods in an online method.
+For example the use case of predicting the next activity, while outside the bounds of conformance checking, maps very cleanly to word prediction tasks, when using embeddings, so there are certainly very interesting topics in applying embeddings to not only conformance checking  but other process mining tasks as well.
 
-\subsubsection{Distributed}
-\color{black}
 %

### 2021-12-20 paper.tex
Fixes

@@
 	One other area which lends itself to process mining is the growing Internet of Things.
-	While there are many conceivable applications,  there has only been limited research interest in this synergy.
+	This synergy is interesting from the side of the Internet of Things, where a desire exists for greater analytical capacities regarding processes, 
+	but it is also interesting from the side of process management, where a desire for new and different types of processes is growing.
 	The aim of this seminar paper is to recapitulate the findings of the focus paper \cite{PBWe20}, while also emphasizing the benefits and difficulties of applying the described methodology in the Internet of Things.
@@
 The terminology used here is oriented around the definitions in \cite{Aals16}, as it seems to be the most polished overview of the field at the moment.}.
-Process mining is concerned with the automatic and algorithmic processing of event data.
+Process mining  \cite{Aals16} is concerned with the automatic and algorithmic processing of event data.
 In its easiest form, an event is a piece of data, that consists of a timestamp, an identifier to group events belonging to the same execution, and a body containing further arbitrary values.

### 2021-12-20 paper.tex
Final version for submission

@@
 	%
-	\title{Conformance Checking Using Embeddings and it's Applicability in the Internet of Things}
+	\title{Conformance Checking Using Embeddings and its Applicability in the Internet of Things}
 	%
@@
 One benefactor of this development has been the subfield of process science, which is concerned with the analysis of processes.
-The combination of process science and data science gave rise to techniques generally grouped under the term process mining
+The combination of process science and data science gave rise to techniques generally grouped under the term process mining.
 %\footnote{Please note that due to the relatively young age of the field, the fact that it lies at the intersection of two different fields and the fact that there is a marketing interest for these topics the terminology is not always settled and different authors and/or groups may differ in usage.
@@
 
-Historically, most research in the topic of process mining has been on business processes. 
+Historically, most research on the topic of process mining has been on business processes. 
 There are a few reasons for that. 
@@
 Secondly, the Internet of Things has both the potential and demand for a greater number of online analyses, i.e.
-in contrast to classical business processes it is much more important to evaluate a process during the execution, to give feedback, and to possibly even influence a process during its execution.
+in contrast to classical business processes it is much more important to evaluate a process, give feedback, and possibly even influence a process during its execution.
 
@@
 %However, if a trace is non-conformant, which is, of course, the case that is of interest, then a one-to-one mapping between model and trace is not possible.
-In the non-conformant case so-called non-synchronous moves are introduced, these describe the case that one of  the model or log performs an activity that does not happen in the other one.
+In the non-conformant case, so-called non-synchronous moves are introduced, these describe the case that one of  the model or log performs an activity that does not happen in the other one.
 This can be either a move-on-model-only, where the model takes some transition, which was not observed in the log, or it's dual, the move-on-log-only where an event is recorded in the log that is not possible according to the model.
@@
 \subsection{Embeddings}
-Embedding based methods are popular machine learning approaches that have been used for a variety of tasks with the most successful applications being in the fields of natural language processing and computer vision.
+Embedding-based methods are popular machine learning approaches that have been used for a variety of tasks with the most successful applications being in the fields of natural language processing and computer vision.
 The fundamental idea of embeddings is to train some form of embedding function that embeds complex objects, such as words or documents in the case of NLP or pictures and video sequences in the case of computer vision in a vectors space\footnote{To be more precise: a Hilbert space, since well-defined notions of distances and angles, are necessary and for that, a scalar product  is needed.}.
@@
 Every trace then constitutes a distribution over the embeddings of the activities contained in it, so given an appropriate distance metric for probability distributions such as the Earth Mover's Distance, it is possible to determine the distance (or conversely similarity) between two traces.
-Note that many NLP algorithms use a so called bag of words approach, where the order of words is disregarded.
+Note that many NLP algorithms use a so-called bag of words approach, where the order of words is disregarded.
 Both the WMD and ICT take the same approach as a bag of words and treat a trace as a bag of activities.
@@
 The Word Mover's Distance \cite{KSKW15} is a variant of the Earth Mover's Distance \cite{RTGu98} adapted for natural language processing.
-This family of metrics has proved to be quite robust as well as accurate for a lot of embedding based NLP tasks.
-For this reason it was chosen as an initial candidate for the distance function of an embedding based conformance checking technique.
+This family of metrics has proved to be quite robust as well as accurate for a lot of embedding-based NLP tasks.
+For this reason, it was chosen as an initial candidate for the distance function of an embedding-based conformance checking technique.
 The Earth Mover's distance measures the distance between two probability distributions.
@@
 \label{sec:results}
-To assess the performance of the three proposed embedding based techniques the authors designed and performed three experiments.
-These aimed to test and compare the scalability of the methods, whether noise deteriorates the results in an expected manner, and lastly to compare these techniques to established well researched conformance checking techniques.
+To assess the performance of the three proposed embedding-based techniques the authors designed and performed three experiments.
+These aimed to test and compare the scalability of the methods, whether noise deteriorates the results in an expected manner, and lastly to compare these techniques to established well-researched conformance checking techniques.
 
@@
 The experiments were run on an Intel Core i7-9850h, a mid-range consumer CPU.
-Experiments were run for all three methods for different sized logs and different sized dictionaries, for embedding based conformance checking algorithms dictionary size is determined by the number of different activities in the log.
+Experiments were run for all three methods for different sized logs and different sized dictionaries, for embedding-based conformance checking algorithms dictionary size is determined by the number of different activities in the log.
 All experiments were performed in Python, however, the Word Mover's distance was calculated using pyemd, a Python wrapper to calculate the WMD/EMD with NumPy efficiency.
@@
 \footnote{Note that when two logs of size $n$ are compared, $n^2$ comparisons are needed. This is the reason why the needed time scales quadratically with log size}.
-Over all log sizes a similar pattern is observable, with WMD and ICT behaving similar and \emph{trace2vec} consistently outperforming the other two methods in all experiments.
+Over all log sizes, a similar pattern is observable, with WMD and ICT behaving similarly and \emph{trace2vec} consistently outperforming the other two methods in all experiments.
 For small dictionary sizes  (10) WMD does outperform ICT, however, that is likely due to the aforementioned efficiency differences between the implementations.
 It is notable that despite these efficiency differences ICT already starts to outperform WMD for dictionary sizes of 20.
-For dictionaries of size 30 this gap grows even larger.
+For dictionaries of size 30, this gap grows even larger.
 Here ICT is finished after roughly half the time needed by the WMD approach.
@@
 The authors published some \href{https://github.com/jaripeeperkorn/Conformance-checking-using-activity-and-trace-embeddings}{source code} accompanying the paper.
-To verify their results as well possibly perform some additional experiments it seemed appropriate to look at said code and try to reproduce their results as good as possible.
+To verify their results as well as possibly perform some additional experiments it seemed appropriate to look at said code and try to reproduce their results as well as possible.
 After some initial technical difficulties, since very specific package versions were needed, their code was successfully run.
-They provide three separate Python scripts for their implementations of the  WMD,ICT and \emph{trace2vec} methods.
+They provide three separate Python scripts for their implementations of the  WMD, ICT and \emph{trace2vec} methods.
 
-Aside from that they also provide Jupyter notebooks for their experiments, however sadly these do not run the whole experiment, instead they only perform the experiment for one parameter combination.
-To reproduce their noise experiment it is thus necessary to manually run the corresponding notebook twelve times, once for each parameter combination, manually note down the results of each run and merge them manually at the end.
+Aside from that they also provide Jupyter notebooks for their experiments, however sadly these do not run the whole experiment, instead, they only perform the experiment for one parameter combination.
+To reproduce their noise experiment it is thus necessary to manually run the corresponding notebook twelve times, once for each parameter combination, manually note down the results of each run, and merge them manually at the end.
 This was deemed to be out of scope for this paper.
-Additionally, the discovery experiment only determined fitness and precision of the WMD, ICT and \emph{trace2vec} methods and not the reference methods, so it is unclear at this point how the fitness and precision values for the reference methods were determined.
-Overall it can be said that the results from the paper are at least partially reproducible, and the provided implementation gives good pointer into how the methods were set up in detail, but running the experiments and collecting the results requires more effort than should be necessary.
+Additionally, the discovery experiment only determined the fitness and precision of the WMD, ICT, and \emph{trace2vec} methods and not the reference methods, so it is unclear at this point how the fitness and precision values for the reference methods were determined.
+Overall it can be said that the results from the paper are at least partially reproducible, and the provided implementation gives a good pointer into how the methods were set up in detail, but running the experiments and collecting the results requires more effort than should be necessary.
 
-Lastly, it was considered to design and run another experiment here to evaluate performance and scaling differences between the embedding based approaches and reference approaches like alignments, behavioral fitness and ETC precision, as this is one of the main selling point especially in the IoT and the authors sadly did not include an experiment to that effect.
-In light of the complications with the existing experiments and the fact that no evaluation of the reference metrics was included in their code this idea was deemed out of scope for this paper.
+Lastly, it was considered to design and run another experiment here to evaluate performance and scaling differences between the embedding based approaches and reference approaches like alignments, behavioral fitness, and ETC precision, as this is one of the main selling points especially in the IoT and the authors sadly did not include an experiment to that effect.
+In light of the complications with the existing experiments and the fact that no evaluation of the reference metrics was included in their code, this idea was deemed out of scope for this paper.
 
@@
 When analyzing such an approach in the context of the Internet of Things, there are three main facets that need to be considered.
-Due to the fact that the Internet of Things itself, as well as it's architectures, are very heterogeneous it will always be possible to find networks where one of the following limitations or requirements does not hold to some extent, however generally speaking the following should be the main considerations when trying to adapt a process management technique to the Internet of Things.
-First the Internet of Things generates a lot of data, and the amount of potential data that can be generated is enormous.
+Due to the fact that the Internet of Things itself, as well as its architectures, are very heterogeneous, it will always be possible to find networks where one of the following limitations or requirements does not hold to some extent, however generally speaking the following should be the main considerations when trying to adapt a process management technique to the Internet of Things.
+First, the Internet of Things generates a lot of data, and the amount of potential data that can be generated is enormous.
 This means high performance, for things like real-time analysis, is a major goal.
@@
 However, it is well known that alignments are a rather inefficient technique due to the inherent non-determinism and complex search structures needed to find an optimal alignment.
-As such it should be pointed out that any performance efficient technique that rivals alignments in expressive power, is desired in normal process mining, while being doubly important in any environment where computing power is much more limited and where data needs to be processed in real time.
+As such it should be pointed out that any performance efficient technique that rivals alignments in expressive power, is desired in normal process mining, while being doubly important in any environment where computing power is much more limited and where data needs to be processed in real-time.
 Furthermore, embeddings provide a way to move computations out of the conformance calculation into preliminary calculations, namely determining the embedding function.
@@
 This is attractive since it further decreases the amount of work needed to evaluate a dissimilarity, and, as can be seen at the \emph{trace2vec} case, generally exhibits much better scaling properties.
-Separating the conformance checking algorithm into a (more) efficient and well scaling evaluation part and a less efficient but shareable training part, could make such algorithms much more desirable in use-cases with many activities, long traces and/or high performance requirements, such as real time evaluation.
+Separating the conformance checking algorithm into a (more) efficient and well-scaling evaluation part and a less efficient but shareable training part could make such algorithms much more desirable in use-cases with many activities, long traces, and/or high-performance requirements, such as real-time evaluation.
 \subsubsection{Online/Streaming algorithms}
@@
 
-A naïve way to perform conformance checking analysis of the prefixes using the techniques outline above, is to simply add all prefixes of traces in the model log  to the model log.
-This approach essentially replicates the prefix-conformance technique presented in \cite{ZBK*19} for any model-log to real-log technique.
+A naïve way to perform conformance checking analysis of the prefixes using the techniques outlined above is to simply add all prefixes of traces in the model log  to the model log.
+This approach essentially replicates the prefix-conformance technique presented \cite{ZBK*19} for any model-log to real-log technique.
 The basic approach there was to relax one of the restrictions, namely that the end marking of an alignment had to be a final marking, to consider all traces whose end marking can reach the final marking, i.e.
 that there exists some remainder execution that completes the trace.
-Given a large enough sampling this is equivalent to enumerating all prefixes of the replay.
+Given a large enough sampling, this is equivalent to enumerating all prefixes of the replay.
 While this approach would give decent estimations for any incomplete traces such an approach runs into several problems.
@@
 This means that through the modeling approach prefix relationships are already substantially degraded.
-It is possible that there are subset-like variants of the WMD, however I am not aware of any.
+It is possible that there are subset-like variants of the WMD, however, I am not aware of any.
 
-The \emph{trace2vec} method could be more interesting, since it gives a framework to directly compare traces.
+The \emph{trace2vec} method could be more interesting since it gives a framework to directly compare traces.
 If we look at any trace we would assume that the longer a prefix we take and determine the embedding of the more similar it is to the trace itself, i.e.
@@
 
-Overall it should be noted that online conformance checking is a difficult problem, but that there are certainly possibilities for solutions using the proposed techniques, especially considering their novelty there has been less research how they could be adapted in an online setting, and how such adaptions perform in reality.
-But even beyond that there are many potential interesting use cases for embedding based methods in an online method.
-For example the use case of predicting the next activity, while outside the bounds of conformance checking, maps very cleanly to word prediction tasks, when using embeddings, so there are certainly very interesting topics in applying embeddings to not only conformance checking  but other process mining tasks as well.
+Overall it should be noted that online conformance checking is a difficult problem, but that there are certainly possibilities for solutions using the proposed techniques, especially considering their novelty there has been less research on how they could be adapted in an online setting, and how such adaptions perform in reality.
+But even beyond that, there are many potential interesting use cases for embedding-based methods in an online method.
+For example, the use case of predicting the next activity, while outside the bounds of conformance checking, maps very cleanly to word prediction tasks, when using embeddings, so there are certainly very interesting topics in applying embeddings to not only conformance checking  but other process mining tasks as well.
 

### 2021-12-21 slides.tex
Init slides

\documentclass{beamer}
%Information to be included in the title page:
\title{Conformance Checking Using Embeddings and its Applicability in the Internet of Things}
\author{Jan Kruska}
\date{\today}

\begin{document}

\frame{\titlepage}

\begin{frame}
	\frametitle{Table of Contents}
	\tableofcontents
\end{frame}
\section{Conformance Checking}
\begin{frame}
	\frametitle{Conformance Checking}
\end{frame}

\section{Embeddings}
\begin{frame}
	\frametitle{Embeddings}
\end{frame}

\begin{frame}
	\frametitle{\emph{act2vec} \& \emph{trace2vec}}
\end{frame}

\section{Experiments}
\begin{frame}
	\frametitle{Noise}
\end{frame}

\begin{frame}
	\frametitle{Discovery}
\end{frame}

\begin{frame}
	\frametitle{Scalability}
\end{frame}

\section{Internet of Things}
\begin{frame}
	\frametitle{Challenges}
	\begin{itemize}
		\item log-comparison method. Performance dependent on model complexity. How many traces are needed to describe the model sufficiently well.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Benefits}
	\begin{itemize}
		\item Better performance, and especially better scaling w.r.t. number of activities and trace length.
		\item Embeddings have other advantages, no more binary activity equality, could allow for more fine grained conformance.
	\end{itemize}
\end{frame}

\end{document}

### 2021-12-22 paper.tex
Updated slides

@@
 Furthermore, four operator configurations were chosen described by the probability for randomly choosing each available operator.
-These were in no particular order: Sequence: $0.75$, Parallel $0.25$, secondly Sequence: $0.75$, Choice $0.25$, thirdly 1.
-Sequence: $0.5$, Parallel $0.25$, Choice $0.25$ and lastly $0.25$ for all (Sequence, Parallel, Choice and Loop) operators.
+These were in no particular order: Sequence: $0.75$, Parallel $0.25$, secondly Sequence: $0.75$, Choice $0.25$, thirdly Sequence: $0.5$, Parallel $0.25$, Choice $0.25$ and lastly $0.25$ for all (Sequence, Parallel, Choice and Loop) operators.
 Both of these configurations were combined to generate a grid of $12$ process trees, with the hope that these cover a sufficient range of different behavior.
@@
 	\includegraphics[width=1\textwidth]{figures/scaling}
-	\caption{Runtimes for all three methods for varying sizes of logs and dictionaries. Data can be found in \cite{MuCa10} Table 2.}
+	\caption{Runtimes for all three methods for varying sizes of logs and dictionaries. Data can be found in \cite{PBWe20} Table 2.}
 	\label{fig:scalability}

### 2021-12-22 slides.tex
Updated slides
Expanded slides

@@
 \documentclass{beamer}
-%Information to be included in the title page:
+\usepackage{caption}
+\usepackage{subcaption}
+
 \title{Conformance Checking Using Embeddings and its Applicability in the Internet of Things}
@@
 	\begin{frame}
+		\frametitle{Setup}
+		Random trees were generated using pm4py and the following configurations:
+
+		\begin{tabular}{lll}
+			Min & Mode & Max \\
+			5 & 10 & 15 \\
+			10 & 20 & 30 \\
+			15 & 30 & 45 \\
+		\end{tabular}
+		\begin{tabular}{llll}
+			Sequence & Parallel & Choice & Loop \\
+			0.75 & 0.25 & 0 & 0 \\
+			0.75 & 0 & 0.25 & 0 \\
+			0.5 & 0.25 & 0.25 & 0 \\
+			0.25 & 0.25 & 0.25 & 0.25 \\
+		\end{tabular}
+
+		Using these parameters $3\times4=12$ trees were generated.
+	\end{frame}
+	\begin{frame}
+		\frametitle{Example tree}
+		\begin{figure}
+			\includegraphics[width=1\textwidth]{figures/process-tree}
+			\caption{A process tree generated by pm4py using parameters: Min 15, Mode 30, Max 45, sequence 0.75, parallel 0.25. }
+			\label{fig:process-tree}
+		\end{figure}
+	\end{frame}
+
+	\begin{frame}
 		\frametitle{Noise}
+		\begin{figure}
+			\centering
+			\begin{subfigure}[b]{0.49\textwidth}
+				\centering
+				\includegraphics[width=\textwidth]{figures/noise-first}
+				\caption{Average of first noise experiment (Varying trace percentage).}
+				\label{fig:noise-first}
+			\end{subfigure}
+			\hfill
+			\begin{subfigure}[b]{0.49\textwidth}
+				\centering
+				\includegraphics[width=\textwidth]{figures/noise-second}
+				\caption{Average of second noise experiment (Varying amount of noise applied to trace).}
+				\label{fig:noise-second}
+			\end{subfigure}
+		\end{figure}
 	\end{frame}
@@
 		\frametitle{Discovery}
+		\begin{figure}
+			\centering
+			\begin{subfigure}[b]{0.49\textwidth}
+				\centering
+				\includegraphics[width=\textwidth]{figures/fitness}
+				\caption{Fitness}
+				\label{fig:fitness}
+			\end{subfigure}
+			\hfill
+			\begin{subfigure}[b]{0.49\textwidth}
+				\centering
+				\includegraphics[width=\textwidth]{figures/precision}
+				\caption{Precision}
+				\label{fig:precision}
+			\end{subfigure}
+			\caption{Fitness and Precision for different tree, discovery technique pairings for the three proposed techniques as well as the two verification techniques.}
+			\label{fig:discovery}
+		\end{figure}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Discovery}
+		\begin{itemize}
+			\item Measures for proposed methods are not proper fitness metrics, so careful with quantitative analyses!
+			\item 
+		\end{itemize}
 	\end{frame}
@@
 		\frametitle{Scalability}
+		\begin{figure}
+			\includegraphics[width=1\textwidth]{figures/scaling}
+			\caption{Runtimes for all three methods for varying sizes of logs and dictionaries.}
+			\label{fig:scalability}
+		\end{figure}
 	\end{frame}

### 2022-01-01 slides.tex
Motivation and structure

@@
 \begin{document}
-
+	\beamertemplatenavigationsymbolsempty
+	\addtobeamertemplate{navigation symbols}{}{%
+		\usebeamerfont{footline}%
+		\usebeamercolor[fg]{footline}%
+		\hspace{1em}%
+		\insertframenumber
+	}
 	\frame{\titlepage}
@@
 	\end{frame}
-	\section{Conformance Checking}
+	\section{Motivation}
 	\begin{frame}
-		\frametitle{Conformance Checking}
+		\frametitle{Motivation}
+		\begin{itemize}
+			\item We know that traditional approaches (replay and alignments) are able to measure conformance, but have some meaningful disadvantages as well.
+			\item At least conceptually NLP and BPM share some important characteristics. Both deal with sequences (sentences/traces) of words/activities and aim to define similarity measures between those.
+		\end{itemize}
+		\begin{block}{Research Question:}
+			Are adaptations of NLP techniques feasible solutions for problems in the BPM field, specifically for the problem of conformance checking.
+		\end{block}
+		\alert{Theoretical exploration in previous paper, here implementation and evaluation was the main concern}
 	\end{frame}
 
-	\section{Embeddings}
+	\section{Structure}
 	\begin{frame}
-		\frametitle{Embeddings}
+		\frametitle{Structure}
+		\begin{figure}
+			\includegraphics[width=1\textwidth]{figures/structure}
+			\caption{The general structure of the approach}
+			\label{fig:structure}
+		\end{figure}
 	\end{frame}
@@
 	\begin{frame}
-		\frametitle{\emph{act2vec} \& \emph{trace2vec}}
+		\frametitle{Used dissimilarity functions}
+		\begin{enumerate}
+			\item \textbf{Word Mover's distance} How much "work" is needed to transform one distribution of dirt on piles into another. Both distance between piles and amount of dirt on piles matter.
+			\item \textbf{Iterative Constraint Transfers} WMD has cubic complexity in the dictionary size, which makes it unattractive.
+ICT is a linear time approximation of WMD obtained by relaxing one of the constraints of the LP.
+			\item \textbf{\emph{trace2vec}} Analogously to \emph{doc2vec} train an embedding of bags of activities called \emph{trace2vec}.
+Use cosine similarity to directly compare traces in the trace embedding space.
+		\end{enumerate}
 	\end{frame}

### 2022-01-02 slides.tex
additions

@@
 		\end{enumerate}
+	\alert{The obtained metrics are not proper fitness metrics, i.e. they do not fall within the interval $[0,1]$. As such quantitative analyses is not really possible at this point.}
 	\end{frame}
@@
 	\section{Experiments}
+	\begin{frame}
+		\frametitle{Setup}
+		Three experiments were performed:
+		\begin{enumerate}
+			\item Noise: Applying noise to a varying amount of traces/ varying amount of noise applied to same amount of traces. Investigate how the methods react. Do they deteriorate smoothly?
+			\item Discovery: Discover model using different miners, determine fitness and precision using the three proposed methods as well as alignments, behavioural fitness and ETC precision.
+			\item Scaling: Vary log and dictionary sizes (number of activities). Compare runtimes \alert{Sadly no runtimes of traditional methods were included.}
+		\end{enumerate}
+	\end{frame}
 	\begin{frame}
@@
 		Using these parameters $3\times4=12$ trees were generated.
+		Then from each of those the "real" logs of 1000 traces were gathered by play-out.
+
+		The scaling experiment used different unspecified trees varying the amount of activities and the size of the played-out log.
 	\end{frame}
@@
 	\begin{frame}
-		\frametitle{Discovery}
+		\frametitle{Results from Noise \& Discovery}
 		\begin{itemize}
-			\item Measures for proposed methods are not proper fitness metrics, so careful with quantitative analyses!
-			\item 
+			\item Overall, noise behaves as expected
+			\item Again quantitative analyses can not be made from this data!
+			\item Very often the NLP and reference methods agree on perfect fitness or precision
+			\item For imperfect values the methods also seem to move in a similar direction, though further research is probably needed.
 		\end{itemize}
@@
 	\begin{frame}
-		\frametitle{Scalability}
+		\frametitle{Scaling}
 		\begin{figure}
@@
 
-	\section{Internet of Things}
 	\begin{frame}
-		\frametitle{Challenges}
+		\frametitle{Scaling}
 		\begin{itemize}
+			\item unoptimized ICT already rivalling WMD, very likely attractive alternative.
+			\item ICT scales well, \emph{trace2vec} stays the same with dictionary size
+			\item All methods scale roughly quadratically with log-size, since the number of necessary comparisons grows quadratically
 			\item log-comparison method. Performance dependent on model complexity. How many traces are needed to describe the model sufficiently well.
@@
 
+	\section{Internet of Things}
 	\begin{frame}
-		\frametitle{Benefits}
+		\frametitle{Internet of Things}
 		\begin{itemize}
 			\item Better performance, and especially better scaling w.r.t. number of activities and trace length.
+			\item Learned embeddings could be shared between devices, moving work out of the evaluation to a preceding training step.
 			\item Embeddings have other advantages, no more binary activity equality, could allow for more fine grained conformance.
+			\item Possibly much more complex tasks. E.g. an analogy to predictive text, i.e. predicting the next event given a sequence of observed events.
 		\end{itemize}

### 2022-01-13 slides/slides.tex
RWTH style
Integrated some comments, Fixed titlepage

--- 2022-01-02 slides.tex
@@
 
-\title{Conformance Checking Using Embeddings and its Applicability in the Internet of Things}
-\author{Jan Kruska}
-\date{\today}
+\usetheme{rwth}
+%\title{Conformance Checking Using Embeddings and its Applicability in the Internet of Things}
+%\author{Jan Kruska}
+%\date{\today}
+
+\newcommand{\figures}{../figures/}
+
+\newcommand{\pro}{\item[\color{green}\textbf{+}\color{black}]}
+\newcommand{\con}{\item[\color{red}\boldmath{$-$}\color{black}]}
+
+\logo{\includegraphics{figures/rwth_pads_en_rgb}}
+
+\input{config}
+\author[\firstname]{\firstname~\lastname~\email}
+\institute[RWTH]{RWTH Aachen University}
 
@@
 	}
-	\frame{\titlepage}
+% Title page with a 1/3rd size picture
+\setbeamercolor{title page bar}{fg=white}
+\setbeamertemplate{title page}[rwth][figures/title_small]{}
+\begin{frame}[plain]
+	\vspace{1cm}
+	\titlepage
 
+	\vspace{-6em}
+	\parbox{0cm}{
+		\begin{tabbing}
+			\=\textbf{\firstname~\lastname}\=\\[0.4em]
+			\=Study Program: \studyProgram~~~\=Matr.-Nr.:\matrNo\\[0.4em]
+			\=Chair of Process and Data Science \=\\%[0.4em]
+%			\={Supervisors}:~~~\=\firstsupervisor\\
+%			\>                 \>\secondsupervisor\\[0.4em]
+%			\={Advisor}:       \>\firstadvisor\ifdefined\secondadvisor\\
+%			\>                 \>\secondadvisor\\[0.4em]
+%			\fi
+		\end{tabbing}
+	}
+\end{frame}
 	\begin{frame}
@@
 		\begin{itemize}
-			\item We know that traditional approaches (replay and alignments) are able to measure conformance, but have some meaningful disadvantages as well.
-			\item At least conceptually NLP and BPM share some important characteristics. Both deal with sequences (sentences/traces) of words/activities and aim to define similarity measures between those.
+			\item Traditional approaches (replay and alignments) are able to measure conformance, but have some meaningful disadvantages (inaccurate diagnostics through phenomena like token flooding, high complexity) as well.
+			\item At least conceptually, Natural Language Processing and Business Process management share some important characteristics.
+Both deal with sequences (sentences/traces) of words/activities and aim to define similarity measures between those.
 		\end{itemize}
 		\begin{block}{Research Question:}
-			Are adaptations of NLP techniques feasible solutions for problems in the BPM field, specifically for the problem of conformance checking.
+			Are adaptations of NLP techniques feasible solutions for problems in the BPM field, specifically for the problem of conformance checking?
 		\end{block}
@@
 
-	\section{Structure}
+	\section{Structure of Embedding based conformance checking}
 \begin{frame}
-		\frametitle{Structure}
+	\frametitle{Proposed approach}
+	\begin{enumerate}
+		\item Given a model play it out to obtain a so called model log
+		\item Train activity embeddings (\emph{act2vec}) based on real and model log
+		\item Any trace is a sequence of activities. Given an embedding (dis)similarity metrics can be defined
+		\item Using a (dis)similarity metric pairwise compare all traces in real and model log.
+		\item The best dissimilarity between a real trace and all model traces is a measure for fitness, the best similarity between a model trace and all real traces is a measure for precision.
+	\end{enumerate}
+\end{frame}
+
+	\begin{frame}
+		\frametitle{Diagram}
 		\begin{figure}
-			\includegraphics[width=1\textwidth]{figures/structure}
+			\includegraphics[width=1\linewidth, height=0.6\paperheight, keepaspectratio]{\figures structure}
 			\caption{The general structure of the approach}
@@
 ICT is a linear time approximation of WMD obtained by relaxing one of the constraints of the LP.
-			\item \textbf{\emph{trace2vec}} Analogously to \emph{doc2vec} train an embedding of bags of activities called \emph{trace2vec}.
+			\item \textbf{\emph{trace2vec}} Analogously to \emph{doc2vec}, train an embedding of bags of activities called \emph{trace2vec}.
 Use cosine similarity to directly compare traces in the trace embedding space.
 		\end{enumerate}
-	\alert{The obtained metrics are not proper fitness metrics, i.e. they do not fall within the interval $[0,1]$. As such quantitative analyses is not really possible at this point.}
+	\alert{The obtained metrics are not proper fitness metrics, i.e. they do not fall within the interval $[0,1]$. As such, quantitative analyses are not really possible at this point.}
 	\end{frame}
@@
 	\begin{frame}
-		\frametitle{Setup}
-		Three experiments were performed:
+		\frametitle{Experimental Setup}
+		In the paper three experiments were performed:
 		\begin{enumerate}
@@
 	\begin{frame}
-		\frametitle{Setup}
+		\frametitle{Random Trees}
 		Random trees were generated using pm4py and the following configurations:
 
+		\begin{center}
 		\begin{tabular}{lll}
@@
 		\end{tabular}
+	\hspace{40pt}
 		\begin{tabular}{llll}
@@
 		\end{tabular}
+	\end{center}
 
@@
 		\begin{figure}
-			\includegraphics[width=1\textwidth]{figures/process-tree}
+			\includegraphics[width=1\textwidth]{\figures process-tree}
 			\caption{A process tree generated by pm4py using parameters: Min 15, Mode 30, Max 45, sequence 0.75, parallel 0.25. }
@@
 				\centering
-				\includegraphics[width=\textwidth]{figures/noise-first}
+				\includegraphics[width=\textwidth]{\figures noise-first}
 				\caption{Average of first noise experiment (Varying trace percentage).}
@@
 				\centering
-				\includegraphics[width=\textwidth]{figures/noise-second}
+				\includegraphics[width=\textwidth]{\figures noise-second}
 				\caption{Average of second noise experiment (Varying amount of noise applied to trace).}
@@
 				\centering
-				\includegraphics[width=\textwidth]{figures/fitness}
+				\includegraphics[width=\textwidth]{\figures fitness}
 				\caption{Fitness}
@@
 				\centering
-				\includegraphics[width=\textwidth]{figures/precision}
+				\includegraphics[width=\textwidth]{\figures precision}
 				\caption{Precision}
@@
 			\item Overall, noise behaves as expected
-			\item Again quantitative analyses can not be made from this data!
-			\item Very often the NLP and reference methods agree on perfect fitness or precision
-			\item For imperfect values the methods also seem to move in a similar direction, though further research is probably needed.
+			\item Again, quantitative analyses can not be made from this data!
+			\item Very often, the NLP and reference methods agree on perfect fitness or precision
+			\item For imperfect values, the methods also seem to move in a similar direction, though further research is needed.
 		\end{itemize}
@@
 		\begin{figure}
-			\includegraphics[width=1\textwidth]{figures/scaling}
+			\includegraphics[width=1\linewidth, height=0.6\paperheight, keepaspectratio]{\figures scaling}
 			\caption{Runtimes for all three methods for varying sizes of logs and dictionaries.}
@@
 
+	\begin{frame}
+		\frametitle{Replicability}
+		\begin{itemize}
+			 \pro<1-> Code  is available and well-organized
+			 \pro<2-> Implementation and experiments are seperated, should allow for relatively easy reuse of their embedding solution
+			 \con<3-> Experiment scripts only run experiment for one configuration.
+Reproducing their results requires manually entering all parameter combinations used (e.g.
+log and vocabulary size for the scalability experiment) and noting down results.
+			 \con<4-> Results outputted as plain text. This makes further processing of results tedious (and more error prone), since they need to be manually copied.
+			 \con<5-> No code included to create the figures displayed in the paper.
+			 \con<6-> As far as I can tell Alignment fitness and precision, Behavioural fitness and ECT precision were not calculated in the discovery experiment script.
+		\end{itemize}
+	\end{frame}
+
 	\section{Internet of Things}

### 2022-01-14 paper.tex
additions
Slides

@@
 The \emph{trace2vec} method could be more interesting since it gives a framework to directly compare traces.
-If we look at any trace we would assume that the longer a prefix we take and determine the embedding of the more similar it is to the trace itself, i.e.
-it convergence in some sense to the embedding of the complete trace.
+If we look at any trace we would assume that the longer a prefix we take and determine the embedding of, the more similar it is to the trace itself, i.e.
+it converges in some sense to the embedding of the complete trace.
 An improvement on the naïve method above could be to just check all prefixes of the $k$ nearest neighbors to any trace.

### 2022-01-14 slides/slides.tex
Slides

@@
+% !TeX spellcheck = en_US
 \documentclass{beamer}
@@
 		\frametitle{Motivation}
+		%\begin{center}	
+		%\end{center}
 		\begin{itemize}
@@
 		\end{block}
-		\alert{Theoretical exploration in previous paper, here implementation and evaluation was the main concern}
+		\alert{Theoretical exploration in previous paper \cite{KBWe18}, here \cite{PBWe20} implementation and evaluation was the main concern}
 	\end{frame}
@@
 		\begin{enumerate}
-			\item \textbf{Word Mover's distance} How much "work" is needed to transform one distribution of dirt on piles into another. Both distance between piles and amount of dirt on piles matter.
-			\item \textbf{Iterative Constraint Transfers} WMD has cubic complexity in the dictionary size, which makes it unattractive.
+			\item \textbf{Word Mover's distance}\cite{KSKW15} How much "work" is needed to transform one distribution of dirt on piles into another.
+Both distance between piles and amount of dirt on piles matter.
+			\item \textbf{Iterative Constraint Transfers}\cite{AtMi18} WMD has cubic complexity in the dictionary size, which makes it unattractive.
 ICT is a linear time approximation of WMD obtained by relaxing one of the constraints of the LP.
-			\item \textbf{\emph{trace2vec}} Analogously to \emph{doc2vec}, train an embedding of bags of activities called \emph{trace2vec}.
+			\item \textbf{\emph{trace2vec}}\cite{KBWe18} Analogously to \emph{doc2vec}, train an embedding of bags of activities called \emph{trace2vec}.
 Use cosine similarity to directly compare traces in the trace embedding space.
@@
 			\item Noise: Applying noise to a varying amount of traces/ varying amount of noise applied to same amount of traces. Investigate how the methods react. Do they deteriorate smoothly?
-			\item Discovery: Discover model using different miners, determine fitness and precision using the three proposed methods as well as alignments, behavioural fitness and ETC precision.
+			\item Discovery: Discover model using different miners, determine fitness and precision using the three proposed methods as well as alignment fitness and precision \cite{Aals16}, behavioural fitness \cite{GMVB09} and ETC precision \cite{MuCa10}.
 			\item Scaling: Vary log and dictionary sizes (number of activities). Compare runtimes \alert{Sadly no runtimes of traditional methods were included.}
@@
 			\item For imperfect values, the methods also seem to move in a similar direction, though further research is needed.
+			\item Validation techniques should not be seen as normative, since both of these also significantly disagree for some models. 
 		\end{itemize}
@@
 		\begin{itemize}
-			\item unoptimized ICT already rivalling WMD, very likely attractive alternative.
+			\item Note that WMD was calculated using a library with NumPy efficiency, whereas ICT was implemented in pure python. Yet unoptimized ICT already rivals WMD, very likely an attractive alternative.
 			\item ICT scales well, \emph{trace2vec} stays the same with dictionary size
@@
 			 \pro<1-> Code  is available and well-organized
-			 \pro<2-> Implementation and experiments are seperated, should allow for relatively easy reuse of their embedding solution
+			 \pro<2-> Implementation and experiments are separated, should allow for relatively easy reuse of their embedding solution
 			 \con<3-> Experiment scripts only run experiment for one configuration.
@@
 		\end{itemize}
+	\alert<7->{I would have liked to perform a performance experiment comparing these embedding-based methods to the reference methods.
+Due to the incompleteness of the provided code this was not possible in a reasonable timeframe for the seminar.}
 	\end{frame}
 
-	\section{Internet of Things}
+	\section{Application for Internet of Things}
 	\begin{frame}
@@
 		\begin{itemize}
-			\item Better performance, and especially better scaling w.r.t. number of activities and trace length.
+			\item Good scaling w.r.t number of activities could be necessary in scenarios with real time requirements and large amounts of data.
 			\item Learned embeddings could be shared between devices, moving work out of the evaluation to a preceding training step.
-			\item Embeddings have other advantages, no more binary activity equality, could allow for more fine grained conformance.
+			\item Streaming capabilities are a bigger priority in an IoT context.
+Difficult to do without explicit end-of-trace knowledge, at least prefix-conformance approach from \cite{ZBK*19} should be easily replicable.
+Whether embeddings could lead to better approaches constitutes a whole work in itself.
 			\item Possibly much more complex tasks. E.g. an analogy to predictive text, i.e. predicting the next event given a sequence of observed events.
@@
 
+\begin{frame}
+	\frametitle{Embeddings for BPM}
+	The possibilities when moving from generic objects (traces) to vector space embeddings should not be understated.
+
+	\begin{itemize}
+		\item Other methods essentially utilize binary activity equality and relatively simple models for trace comparison. Embeddings provide much more fine grained relationships between embedded objects.
+		\item This opens up a plethora of techniques that reach far beyond conformance checking.
+		\item Especially automatic grouping of similar activities, as is achieved by an embedding could be potentially very useful.
+	\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+	\frametitle{Conclusion \& Future Work}
+	\begin{itemize}
+		\item In general very interesting initial results were obtained that warrant further research
+		\item The performed experiment are not sufficient to reliably ascertain how well embedding-based methods perform in real world scenarios. Experiments with real logs should follow.
+		\item The metrics used at the moment are not proper fitness/precision metrics (Not in $[0,1]$).
+		\item WMD and ICT do not take activity order into account, \emph{trace2vec} only does so during training
+		\item Given the work it also seems feasible to move on to more complicated NLP techniques.
+The authors especially mention $n$-grams, Embeddings from Language Models, Global Vectors for Word Representation, and Recurrent Neural Networks.
+	\end{itemize}
+
+\begin{frame}[allowframebreaks]
+	\frametitle{References}
+	\bibliographystyle{../template/splncs04}
+	\bibliography{../literature/bibliography}
+\end{frame}
+\end{frame}
+
 \end{document}

### 2022-01-14 slides/slides.tex
Some changes

@@
 \setbeamertemplate{title page}[rwth][figures/title_small]{}
+\setbeamertemplate{bibliography item}{\insertbiblabel}
 \begin{frame}[plain]
@@
 			\=Chair of Process and Data Science \=\\%[0.4em]
-%			\={Supervisors}:~~~\=\firstsupervisor\\
+			\={Seminar:}~~~\=Business Processes and the Internet of Things\\
 %			\>                 \>\secondsupervisor\\[0.4em]
@@
 		\begin{enumerate}
-			\item \textbf{Word Mover's distance}\cite{KSKW15} How much "work" is needed to transform one distribution of dirt on piles into another.
+			\item \textbf{Word Mover's distance} \cite{KSKW15} How much "work" is needed to transform one distribution of dirt on piles into another.
 Both distance between piles and amount of dirt on piles matter.
-			\item \textbf{Iterative Constraint Transfers}\cite{AtMi18} WMD has cubic complexity in the dictionary size, which makes it unattractive.
+			\item \textbf{Iterative Constraint Transfers} \cite{AtMi18} WMD has cubic complexity in the dictionary size, which makes it unattractive.
 ICT is a linear time approximation of WMD obtained by relaxing one of the constraints of the LP.
-			\item \textbf{\emph{trace2vec}}\cite{KBWe18} Analogously to \emph{doc2vec}, train an embedding of bags of activities called \emph{trace2vec}.
+			\item \textbf{\emph{trace2vec}} \cite{KBWe18} Analogously to \emph{doc2vec}, train an embedding of bags of activities called \emph{trace2vec}.
 Use cosine similarity to directly compare traces in the trace embedding space.
@@
 		\end{itemize}
-	\alert<7->{I would have liked to perform a performance experiment comparing these embedding-based methods to the reference methods.
-Due to the incompleteness of the provided code this was not possible in a reasonable timeframe for the seminar.}
+	\temporal<7->{}{\alert{I would have liked to perform a performance experiment comparing these embedding-based methods to the reference methods.
+Due to the incompleteness of the provided code this was not possible in a reasonable timeframe for the seminar.}}{}
 	\end{frame}
@@
 	\end{itemize}
+\end{frame}
 
+\section*{References}
 \begin{frame}[allowframebreaks]
-	\frametitle{References}
+%	\frametitle{References}
 	\bibliographystyle{../template/splncs04}
@@
 \end{frame}
-\end{frame}
 

### 2022-01-17 slides/slides.tex
Integrated some comments

@@
 		\begin{itemize}
-			\item Traditional approaches (replay and alignments) are able to measure conformance, but have some meaningful disadvantages (inaccurate diagnostics through phenomena like token flooding, high complexity) as well.
-			\item At least conceptually, Natural Language Processing and Business Process management share some important characteristics.
+			\item Traditional approaches (replay and alignments) are able to measure conformance, but have some meaningful disadvantages (e.g.
+inaccurate diagnostics through phenomena like token flooding, high computational complexity).
+			\item Conceptually, Natural Language Processing and Business Process management share some important characteristics.
 Both deal with sequences (sentences/traces) of words/activities and aim to define similarity measures between those.
@@
 
-	\section{Structure of Embedding based conformance checking}
+	\section{Structure of Embedding based Conformance Checking}
 \begin{frame}
-	\frametitle{Proposed approach}
+	\frametitle{Conformance Checking using Activity and Trace Embeddings}
 	\begin{enumerate}
@@
 		\item Using a (dis)similarity metric pairwise compare all traces in real and model log.
-		\item The best dissimilarity between a real trace and all model traces is a measure for fitness, the best similarity between a model trace and all real traces is a measure for precision.
+		\item As a result obtain a dissimilarity matrix
 	\end{enumerate}
+\begin{block}{Definition of Fitness and Precision}
+	A trace that is fit should be replayable in the model. If the model log contains a trace with perfect similarity, then the trace is replayable.
+
+	Thus, the best similarity between a real trace and all model traces is a measure for fitness. Conversely, the best similarity between a model trace and all real traces is a measure for precision.
+\end{block}
 \end{frame}
@@
 	\begin{frame}
-		\frametitle{Diagram}
+		\frametitle{Graphical Representation of Approach}
 		\begin{figure}
@@
 			\item Discovery: Discover model using different miners, determine fitness and precision using the three proposed methods as well as alignment fitness and precision \cite{Aals16}, behavioural fitness \cite{GMVB09} and ETC precision \cite{MuCa10}.
-			\item Scaling: Vary log and dictionary sizes (number of activities). Compare runtimes \alert{Sadly no runtimes of traditional methods were included.}
+			\item Scaling: Vary log and dictionary sizes (number of activities). Compare runtimes \alert{No runtimes of traditional methods were included.}
 		\end{enumerate}
@@
 	\begin{frame}
-		\frametitle{Noise}
+		\frametitle{Noise Experiment}
 		\begin{figure}
@@
 	\begin{frame}
-		\frametitle{Discovery}
+		\frametitle{Discovery Experiment}
 		\begin{figure}
@@
 	\begin{frame}
-		\frametitle{Results from Noise \& Discovery}
+		\frametitle{Results from Noise \& Discovery Experiments}
 		\begin{itemize}
@@
 	\begin{frame}
-		\frametitle{Scaling}
+		\frametitle{Scaling Experiment}
 		\begin{figure}
@@
 	\begin{frame}
-		\frametitle{Scaling}
+		\frametitle{Results from Scaling Experiment}
 		\begin{itemize}
@@
 	\begin{frame}
-		\frametitle{Replicability}
+		\frametitle{Scientific Replicability of Experiment Results}
+		\begin{block}<1->{Source Code}
+				 Code\footnote{https://github.com/jaripeeperkorn/Conformance-checking-using-activity-and-trace-embeddings} for both experiments and implementation is available.
+As such, it seemed useful to evaluate how well the results are reproducible using that code.
+		\end{block}
 		\begin{itemize}
-			 \pro<1-> Code  is available and well-organized
+%			 \pro<1-> Code for experiments  is available and well-organized
 			 \pro<2-> Implementation and experiments are separated, should allow for relatively easy reuse of their embedding solution
@@
 log and vocabulary size for the scalability experiment) and noting down results.
-			 \con<4-> Results outputted as plain text. This makes further processing of results tedious (and more error prone), since they need to be manually copied.
+			 \con<4-> Results outputted as plain text in Jupyter Notebook. This makes further processing of results tedious (and more error prone), since they need to be manually copied.
 			 \con<5-> No code included to create the figures displayed in the paper.
-			 \con<6-> As far as I can tell Alignment fitness and precision, Behavioural fitness and ECT precision were not calculated in the discovery experiment script.
+			 \con<6-> Alignment fitness and precision, Behavioral fitness and ECT precision are not calculated in the discovery experiment script.
 		\end{itemize}
-	\temporal<7->{}{\alert{I would have liked to perform a performance experiment comparing these embedding-based methods to the reference methods.
-Due to the incompleteness of the provided code this was not possible in a reasonable timeframe for the seminar.}}{}
+	\temporal<7->{}{\alert{Another performance experiment comparing these embedding-based methods to the reference methods would be desirable.
+Since Alignment, Behavioral fitness and ECT calculations were not present in the discovery script, this was not possible to do in a reasonable time frame for the seminar.}}{}
 	\end{frame}
 
-	\section{Application for Internet of Things}
+	\section{Application in the Internet of Things}
 	\begin{frame}
 		\frametitle{Internet of Things}
+		\begin{block}<1->{Performance and Scaling}
 			\begin{itemize}
@@
 				\item Learned embeddings could be shared between devices, moving work out of the evaluation to a preceding training step.
+			\end{itemize}
+		\end{block}
+
+	\begin{block}<2->{Online Process Mining}
+		\begin{itemize}
 			\item Streaming capabilities are a bigger priority in an IoT context.
@@
 Whether embeddings could lead to better approaches constitutes a whole work in itself.
+			\item More automated, embeddings could be retrained/improved regularly based on new observed data.  
+		\end{itemize}
+	\end{block}
+
+\begin{block}<3->{Utilization of more complex NLP techniques}
+	\begin{itemize}
 		\item Possibly much more complex tasks. E.g. an analogy to predictive text, i.e. predicting the next event given a sequence of observed events.
 	\end{itemize}
+\end{block}
 	\end{frame}
@@
 		\item WMD and ICT do not take activity order into account, \emph{trace2vec} only does so during training
-		\item Given the work it also seems feasible to move on to more complicated NLP techniques.
-The authors especially mention $n$-grams, Embeddings from Language Models, Global Vectors for Word Representation, and Recurrent Neural Networks.
+		\item Given the work it also seems feasible to move on to more complicated NLP techniques:
+		\begin{itemize}
+			\item $n$-grams
+			\item Embeddings from Language Models
+			\item Global Vectors for Word Representation
+			\item Recurrent Neural Networks
+		\end{itemize}
 	\end{itemize}

### 2022-01-17 slides/slides.tex
Final changes for slides

@@
 \usepackage{subcaption}
+\usepackage[autostyle]{csquotes}
 
 \usetheme{rwth}
+\MakeOuterQuote{"}
 %\title{Conformance Checking Using Embeddings and its Applicability in the Internet of Things}
@@
 \newcommand{\con}{\item[\color{red}\boldmath{$-$}\color{black}]}
+\newcommand{\green}{\color{green}#1\color{black}}
 
@@
 		\begin{itemize}
-			\item Traditional approaches (replay and alignments) are able to measure conformance, but have some meaningful disadvantages (e.g.
-inaccurate diagnostics through phenomena like token flooding, high computational complexity).
-			\item Conceptually, Natural Language Processing and Business Process management share some important characteristics.
+			\item Traditional approaches (replay and alignments) are able to measure conformance, but have meaningful disadvantages:
+			\begin{itemize}
+				\item replay based approaches suffer form inaccurate diagnostics through phenomena like token flooding
+				\item alignments suffer from high computational complexity
+			\end{itemize}
+			\item[$\Rightarrow$] There is interest in finding alternatives to traditional approaches
+			\item<2-> Conceptually, Natural Language Processing and Business Process management share some important characteristics.
 Both deal with sequences (sentences/traces) of words/activities and aim to define similarity measures between those.
 		\end{itemize}
-		\begin{block}{Research Question:}
+		\begin{block}<2->{Research Question:}
 			Are adaptations of NLP techniques feasible solutions for problems in the BPM field, specifically for the problem of conformance checking?
 		\end{block}
-		\alert{Theoretical exploration in previous paper \cite{KBWe18}, here \cite{PBWe20} implementation and evaluation was the main concern}
+		\temporal<3->{}{\alert{Theoretical exploration in previous paper \cite{KBWe18}, here \cite{PBWe20} implementation and evaluation was the main concern}}{}
+	\end{frame}
+
+\begin{frame}
+	\frametitle{Embeddings Introduced in \cite{KBWe18}}
+	\begin{itemize}
+		\item \emph{act2vec}: Analogous to \emph{word2vec} (Does not use activity attributes currently)\temporal<2->{}{\green{Base building block, simple, robust}}{}
+		\item \emph{trace2vec}: Utilizes \emph{act2vec} and adds a paragraph vector, analogous to \emph{doc2vec} \temporal<2->{}{\green{Useful for direct trace comparison}}{}
+		\item<-3> \emph{log2vec}: Extends \emph{trace2vec} by including an averaging operation, to create an embedding for the whole log \temporal<2->{}{\alert{Too coarse}}{}
+		\item<-3> \emph{model2vec}: Embedding of the graph structure of a model by performing random walks \temporal<2->{}{\alert{Complex, not very robust, not useful for log/model comparisons}}{}
+	\end{itemize}
 \end{frame}
@@
 		\item Train activity embeddings (\emph{act2vec}) based on real and model log
-		\item Any trace is a sequence of activities. Given an embedding (dis)similarity metrics can be defined
+		%\item Any trace is a sequence of activities. Given an embedding (dis)similarity metrics can be defined
 		\item Using a (dis)similarity metric pairwise compare all traces in real and model log.
-		\item As a result obtain a dissimilarity matrix
 	\end{enumerate}
@@
 			\includegraphics[width=1\linewidth, height=0.6\paperheight, keepaspectratio]{\figures structure}
-			\caption{The general structure of the approach}
+			\caption{The General Structure of the Approach}
 			\label{fig:structure}
@@
 	\begin{frame}
-		\frametitle{Used dissimilarity functions}
+		\frametitle{Used Dissimilarity Functions}
 		\begin{enumerate}
@@
 		\end{enumerate}
+	\end{frame}
+\begin{frame}
+	\frametitle{How to get the Logs?}
+	\begin{figure}
+		\includegraphics[width=1\textwidth]{\figures process-tree}
+		\caption{A process tree generated by pm4py using parameters: Min 15, Mode 30, Max 45, sequence 0.75, parallel 0.25. }
+		\label{fig:process-tree}
+	\end{figure}
 \end{frame}
@@
 	\end{frame}
-	\begin{frame}
-		\frametitle{Example tree}
-		\begin{figure}
-			\includegraphics[width=1\textwidth]{\figures process-tree}
-			\caption{A process tree generated by pm4py using parameters: Min 15, Mode 30, Max 45, sequence 0.75, parallel 0.25. }
-			\label{fig:process-tree}
-		\end{figure}
-	\end{frame}
 
@@
 		\frametitle{Noise Experiment}
+		The goal of the noise experiments was to investigate whether the methods are well-behaved and conform to the expectations.
 		\begin{figure}
@@
 		\frametitle{Discovery Experiment}
+		In the Discovery experiment the embedding-based methods are evaluated against reference methods using different trees and discovery algorithms.
 		\begin{figure}
@@
 		\frametitle{Scaling Experiment}
+		The goal of the scaling experiment was to determine how the methods scale regarding vocabulary and log size
 		\begin{figure}
@@
 log and vocabulary size for the scalability experiment) and noting down results.
-			 \con<4-> Results outputted as plain text in Jupyter Notebook. This makes further processing of results tedious (and more error prone), since they need to be manually copied.
+			 \con<4-> Output format
+			 \begin{itemize}
+			 	\item<4-> Results outputted as plain text in Jupyter Notebook, that needs to be manually copied
+			 	\item<4-> This makes further processing of results tedious and more error prone
+			 	\item<4-> Suggestion: Instead collect results in dataframe and save as csv
+			 \end{itemize}
 			 \con<5-> No code included to create the figures displayed in the paper.
@@
 		\end{itemize}
-	\temporal<7->{}{\alert{Another performance experiment comparing these embedding-based methods to the reference methods would be desirable.
+	\begin{alertblock}<7->{block title}<action specification>
+		Another performance experiment comparing these embedding-based methods to the reference methods would be desirable.
+Since Alignment, Behavioral fitness and ECT calculations were not present in the discovery script, this was not possible to do in a reasonable time frame for the seminar.
+	\end{alertblock}
+%	\temporal<7->{}{\alert{Another performance experiment comparing these embedding-based methods to the reference methods would be desirable.
 Since Alignment, Behavioral fitness and ECT calculations were not present in the discovery script, this was not possible to do in a reasonable time frame for the seminar.}}{}
@@
 
+\begin{frame}{}
+	\centering \Large
+	\emph{Thank you for your attention}
+
+	\emph{Questions?}
+\end{frame}
+
 \end{document}

### 2022-01-26 paper.tex
Included some Peer Review comments

@@
 The terminology used here is oriented around the definitions in \cite{Aals16}, as it seems to be the most polished overview of the field at the moment.}.
-Process mining  \cite{Aals16} is concerned with the automatic and algorithmic processing of event data.
+Process Mining  \cite{Aals16} is concerned with the automatic and algorithmic processing of event data.
 In its easiest form, an event is a piece of data, that consists of a timestamp, an identifier to group events belonging to the same execution, and a body containing further arbitrary values.
@@
 Most importantly it makes it possible to define notions of distance and/or (dis-)similarity needed for machine learning and data analysis tasks.
+
+There are many different approaches to obtaining embeddings, most notably are the Continuous bag of Word and Skip-gram models which can in some sense be viewed as dual to each other.
+Both of these use neural networks in their modern conception.
+The goal of the CBOW architecture is to predict a possible word from a context.
+To this end a shifting window is applied on training text, to produce bags of words.
+Then one word is removed from this bag and the network is trained to produce said word from the others.
+
+The goal of the skip-gram approach is the opposite: Here the context should be predicted from a single word.
+As such the training is also reversed in an appropriate manner.
+
+Once the training is complete a neural network has been obtained, that is able to predict word from context or vice versa.
+The trick now lies in not actually using the whole network and instead utilize the weights trained for the hidden layer.
+this hidden layer is much smaller than either the input and output layers, whose sizes are determined by the vocabulary size, and serves as a dense representation of words.
+In that sense embeddings are very similar to autoencoders, with similar goals, the main difference is that words are not trained against themselves but against the surrounding context.
 
@@
 	\end{subfigure}
+\caption{Results from noise experiment (from \cite{PBWe20} Fig. 4 \& 5)}
+\label{fig:noise}
 \end{figure}
@@
 %However since the used methods are somewhat involved and since it can be hard to exactly tell what a system is doing for a lot of learning-based methods, whether the algorithms are well-behaved or not should be verified.
+
+Fo all noise experiment three random tree using the configurations mentioned above were created, from which the "noiseless" logs were produced.
+Then two different kind of noise were applied to these logs, and the average distance between traces in the "noiseless" and "noisy" variant was compared.
+These results can be found in \cref{fig:noise}.
 

### 2022-01-26 slides/slides.tex

@@
 \usepackage[autostyle]{csquotes}  
+%\usepackage[
+%backend=biber,
+%style=authoryear,
+%citestyle=authoryear 
+%]{biblatex}
+%
+%\addbibresource{../literature/bibliography.bib}
 
@@
 \newcommand{\con}{\item[\color{red}\boldmath{$-$}\color{black}]}
-\newcommand{\green}{\color{green}#1\color{black}}
+\newcommand{\green}[1]{\color{green}\textbf{#1}\color{black}}
 
@@
 	\begin{itemize}
-		\item \emph{act2vec}: Analogous to \emph{word2vec} (Does not use activity attributes currently)\temporal<2->{}{\green{Base building block, simple, robust}}{}
-		\item \emph{trace2vec}: Utilizes \emph{act2vec} and adds a paragraph vector, analogous to \emph{doc2vec} \temporal<2->{}{\green{Useful for direct trace comparison}}{}
-		\item<-3> \emph{log2vec}: Extends \emph{trace2vec} by including an averaging operation, to create an embedding for the whole log \temporal<2->{}{\alert{Too coarse}}{}
-		\item<-3> \emph{model2vec}: Embedding of the graph structure of a model by performing random walks \temporal<2->{}{\alert{Complex, not very robust, not useful for log/model comparisons}}{}
+		\item<-3> \emph{act2vec}:  \temporal<2->{Analogous to \emph{word2vec} (Does not use activity attributes currently)}{\green{Base building block, simple, robust}}{}
+		\item<-3> \emph{trace2vec}:  \temporal<2->{Utilizes \emph{act2vec} and adds a paragraph vector, analogous to \emph{doc2vec}}{\green{Useful for direct trace comparison}}{}
+		\item<-2> \emph{log2vec}:  \temporal<2->{Extends \emph{trace2vec} by including an averaging operation, to create an embedding for the whole log}{\alert{Too coarse}}{}
+		\item<-2> \emph{model2vec}:  \temporal<2->{Embedding of the graph structure of a model by performing random walks}{\alert{Complex, not very robust, not useful for log/model comparisons}}{}
 	\end{itemize}
@@
 		\frametitle{Conformance Checking using Activity and Trace Embeddings}
+		\begin{columns}
+			\column{0.5\textwidth}
 			\begin{enumerate}
 				\item Given a model play it out to obtain a so called model log
-		\item Train activity embeddings (\emph{act2vec}) based on real and model log
+				\item Train activity embeddings (\emph{act2vec}) based on real and model logs
 				%\item Any trace is a sequence of activities. Given an embedding (dis)similarity metrics can be defined
@@
 			\begin{block}{Definition of Fitness and Precision}
-	A trace that is fit should be replayable in the model. If the model log contains a trace with perfect similarity, then the trace is replayable.
-
-	Thus, the best similarity between a real trace and all model traces is a measure for fitness. Conversely, the best similarity between a model trace and all real traces is a measure for precision.
+				Then the best similarity between a real trace and all model traces is a measure for fitness. Conversely, the best similarity between a model trace and all real traces is a measure for precision.
 			\end{block}
-\end{frame}
-
-	\begin{frame}
-		\frametitle{Graphical Representation of Approach}
+		\column{0.4\textwidth}
 		\begin{figure}
@@
 		\end{figure}
+	\end{columns}
 	\end{frame}
@@
 		\frametitle{Used Dissimilarity Functions}
+\begin{columns}[t]
+	\column{.7\textwidth}
 		\begin{enumerate}
@@
 	\alert{The obtained metrics are not proper fitness metrics, i.e. they do not fall within the interval $[0,1]$. As such, quantitative analyses are not really possible at this point.}
+		\column{.3\textwidth}
+	\begin{figure}
+		\includegraphics[width=1\linewidth, keepaspectratio]{figures/emd}
+	\end{figure}
+\end{columns}
 	\end{frame}
@@
 		\end{enumerate}
+
 	\end{frame}
@@
 			\centering
-			\begin{subfigure}[b]{0.49\textwidth}
+			\begin{subfigure}[b]{0.45\textwidth}
 				\centering
@@
 			\hfill
-			\begin{subfigure}[b]{0.49\textwidth}
+			\begin{subfigure}[b]{0.45\textwidth}
 				\centering
@@
 		\begin{figure}
-			\includegraphics[width=1\linewidth, height=0.6\paperheight, keepaspectratio]{\figures scaling}
+			\includegraphics[width=1\linewidth, height=0.55\paperheight, keepaspectratio]{\figures scaling}
 			\caption{Runtimes for all three methods for varying sizes of logs and dictionaries.}
@@
 			 \con<6-> Alignment fitness and precision, Behavioral fitness and ECT precision are not calculated in the discovery experiment script.
+			 \item<7->\color{red}Another performance experiment comparing these embedding-based methods to the reference methods would be desirable.
+Since Alignment, Behavioral fitness and ECT calculations were not present in the discovery script, this was not possible to do in a reasonable time frame for the seminar.\color{black}
 		\end{itemize}
@@
 
+\section{Conclusion and Outlook}
 \begin{frame}
 	\frametitle{Embeddings for BPM}
-	The possibilities when moving from generic objects (traces) to vector space embeddings should not be understated.
+	\begin{exampleblock}{Do not lose sight of the more general benefits!}
+		While this paper dealt mostly with embeddings for conformance checking the possibilities when moving from generic objects (traces) to vector space embeddings should not be understated and are emphatically not limited to conformance checking.
+	\end{exampleblock}
 
@@
 		\item This opens up a plethora of techniques that reach far beyond conformance checking.
-		\item Especially automatic grouping of similar activities, as is achieved by an embedding could be potentially very useful.
+		\item Especially automatic clustering of similar activities, as is achieved by an embedding could be potentially very useful.
 	\end{itemize}
@@
 %	\frametitle{References}
-	\bibliographystyle{../template/splncs04}
+	\bibliographystyle{apalike}
+%	\bibliographystyle{authoryear}
 	\bibliography{../literature/bibliography}
+%	\printbibliography
 \end{frame}
@@
 \begin{frame}{}
-	\centering \Large
-	\emph{Thank you for your attention}
+	\centering \Huge
+	\emph{Thank you for your attention!}
 

### 2022-01-27 paper.tex
Deleted some parts to shorten paper

@@
 The uses of such an approach can generally be divided into two relatively distinct subcategories, depending on whether the event log or the process model are seen as normative.
-If the process model is considered normative, conformance checking allows for the detection of deviations, i.e. observed traces that are not possible according to the model.
-From such information a number of useful analyses can follow, e.g. where do deviations happen, which resources are involved in deviations, and how exactly these traces deviate from the model.
-It should be pointed out that the word "deviation" is negatively connotated in English, however, for the purpose of process intelligence it should be viewed as a neutral category. 
+If the process model is considered normative, conformance checking allows for the detection of deviations.
+From such information a number of useful analyses can follow, e.g. where, how and when deviations happen.
+%It should be pointed out that the word "deviation" is negatively connotated in English, however, for the purpose of process intelligence it should be viewed as a neutral category. 
 For example, an analysis may reveal that people often skip a step in the process, which actually improves the overall performance of the process, based on which refinements to the process model could be made.
@@
 
-In the second case, the log is seen as normative and the model is considered either imperfect or unknown.
-The most important representative application of this perspective is process discovery, or more specifically the evaluation of discovery algorithms.
-In the case of process discovery, a process model has to be constructed from an event log.
-Obviously, not all process models are able to describe a process equally well.
-So when developing or using a process discovery algorithm the question of how well the discovered process models describe the log often arises.
+%In the second case, the log is seen as normative and the model is considered either imperfect or unknown.
+%The most important representative application of this perspective is process discovery, or more specifically the evaluation of discovery algorithms.
+%In the case of process discovery, a process model has to be constructed from an event log.
+%Obviously, not all process models are able to describe a process equally well.
+%So when developing or using a process discovery algorithm the question of how well the discovered process models describe the log often arises.
 
@@
 \begin{figure}
-	\includegraphics[width=1\textwidth]{figures/structure}
+	\centering
+	\includegraphics[width=.8\textwidth]{figures/structure}
 	\caption{The general structure of the approach}
@@
 		\includegraphics[width=\textwidth]{figures/noise-first}
-		\caption{Average of first noise experiment (Varying trace percentage) Raw data can be found in \cite{PBWe20} Table 4}
+		\caption{Average of first noise experiment (Varying trace percentage) }
 		\label{fig:noise-first}
@@
 	\end{subfigure}
-\caption{Results from noise experiment (from \cite{PBWe20} Fig. 4 \& 5)}
+\caption{Results from noise experiment (from \cite{PBWe20} Fig. 4 \& 5). Raw data can be found in \cite{PBWe20} Table 4}
 \label{fig:noise}

### 2022-01-28 paper.tex
-
Some details for embeddings

--- 2022-01-26 paper.tex
@@
 Instead of formulating the problem in terms of model-to-log comparison, one can formulate it as a comparison problem of a real log to a model log.
-Such a reformulation of the problem is possible since all (reasonably defined) models are able to generate sample traces, and can therefore produce a model log.
-Then the whole problem is re-framed as log-to-log comparisons, i.e. determining similarities between objects of the same type, for which a broad range of techniques already exist.
+Such a reformulation of the problem is possible since all (reasonably defined) models are able to generate sample traces.
+Then the key part is determining similarities between objects of the same type, for which a broad range of techniques already exist.
 This has the additional advantage that it is model-independent since no limitations apart from the ability to generate traces are put on the type of model.
@@
 First, a model log is produced from the model by using appropriate replay semantics for the model.
-Then, given these two logs, one real and one produced by replaying the model, it is possible to train the \emph{act2vec} \cite{KBWe18} embedding.
-Based on these embeddings a dissimilarity function needs to be defined to compare different traces, however, the \emph{act2vec} embedding only yields distance measurements between activities and not between traces.
+Then, given these two logs, it is possible to train the \emph{act2vec} \cite{KBWe18} embedding\footnote{Note that only the activity labels were used to train the embedding here.
+It is possible to include further attributes, but this is more complicated}.
+Then a dissimilarity function needs to be defined, to compare to bags of \emph{act2vec} embeddings to each other.
+%Based on these embeddings a dissimilarity function needs to be defined to compare different traces, however, the \emph{act2vec} embedding only yields distance measurements between activities and not between traces.
 Here the differences between the three techniques come into play.
@@
 The last one, \emph{trace2vec}, further needs to train a trace embedding based on activity embeddings, and can then perform direct comparisons in the trace embedding space.
-All three methods however lead to a reasonable dissimilarity metric between traces.
 Using one of these metrics a dissimilarity matrix can be built up describing the pairwise dissimilarities between the real log and the model log.
@@
 These activity embeddings then allow for the comparison of two traces by comparing their individual activities in the embedding space.
+Both the \emph{act2vec} and \emph{trace2vec} approaches utilized a relatively small vector size of 16, to train the embeddings.
 Every trace then constitutes a distribution over the embeddings of the activities contained in it, so given an appropriate distance metric for probability distributions such as the Earth Mover's Distance, it is possible to determine the distance (or conversely similarity) between two traces.

### 2022-01-28 paper.tex

--- 2022-01-27 paper.tex
@@
 		\While{$l < k$}
-		\State $r \gets \min(p_i,q_{s(l)}))$ \Comment{Edge constraint, move as much as possible but no more than allowed}
+		\State $r \gets \min(p_i,q_{s(l)}))$ \Comment{Edge constraint}
 		\State $p_i \gets p_i - r$ \Comment{Move weight}
